### 2008-09-15 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

\documentclass[a4paper, 11pt]{article}
\begin{document}
\section{Requirements}
\subsection{Transactions}
We have a set of Threads $T$ each representing a transaction.The code for a 
Transaction is like below:

\hspace{12mm}	Thread.doIt(new Callable)()\{

\hspace{12mm}		// code for transaction

\hspace{12mm}	\}

This is adopted from dstm and can and may be changed. Within this block which 
represents a member of set $T$. The functions beginTransction and endTransaction are implicitly called by the system without the intervention of the programmer.However, the programmer can read and write from TransactionalFile Objects within the blocks of a member of $T$. To provide consisteny the read and write from ordinary Java object files should be prohibited, otherwise the semantics of transactions would not be preserved. Hence, the sequence of operations provided to the programmer within a member of $T$ is the set \{TransactionalFile.Read(), TransactionalFile.Write()i, TransactionalFile.Seek()\}. However, always a beginTransaction() and commitTransaction() (if the transaction does not abort prior to this point) are performed too. \\

The flow of program should be in a manner that we could have an arbitrary serial order of the members of $T$ (e.g. $T_5,T_6,T_1$,...) or any other order. The serial order should be in such a way that for any given two members of the set $T$, either the effect of all opertaions of \{ TransactionalFile.Read, TransactionalFileWrite, TransactionalFile.Seek()\} within $T_i$ should be visible to $T_j$ or none should be visible. In the first case we would say the $T_i$ precedes $T_j$ and in the seconds case $T_j$ preceds $T_i$ and $T_i$ can observe all the effects made by the operations in $T_j$. \\

\subsection{Defenitions}

Def 1- 1-An operation in $T_i$ is said to have "changed" or "affected" some data structure in correspondece to all members of $OP_{T- T_i}$ , when it reflects the changes in the filesystem in such a way that the modification is durable and irreversible. A transaction with such an operation $T_i$ in its operation set is said to have changed the data 2- An operation in $T_i$ is said to have "changed or affeced the data in correspondence to all the operations in $OP_{T_i}$ as soon as the operation is encountered \\

Def 2- An operation in $T_i$ is said to have "used" the data when it has read some data and has done some actions that is potentially irreversible. hence if the data in question was to change, $op$ would have different results. A transaction with such an operation in its operations set is said to have used that data. Any data read and used within a transaction at its commit instant does not count as using. "Use" can just be attributed to the operations actually reading data before commit instant. \\

Def 3- A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "changes" in the filesystem or equivalently makes it changes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$ . An operation $\in OP_{T_i}$ is said to commit if and only if $T_i$ commits. Commit instant are not splittable, hence it appears to other transactions that all changes are refleted in the file system together.\\

Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ should be able to see the changes made by $op_i$ unless data has been changed by a more recent precedessor  \\

Def 5- Succeds relationship is defined similarly.  \\

Def 6- If operation $a$ both precedes and succeds operation $b$ since they do not share any resources so the changes can be made visible, $a$ both precedes and succeds $b$. \\

Def 7- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$,  then $T_i$ \emph {can} $\rightarrow T_j$) \hspace{8mm} (this defines precedes relationship for members of $T$) \\

Def 8- An operation $op \in OP_{T_i}$ should be able to see the "changes" 1- made by $OP_{T_commited}$ and 2-$oper \in OP_{T_i}$ that in natural order of transaction occur before $op$

\subsection{Rules}
If we denote $\rightarrow$ as the relation precedes between operations and $OP_{T_i}$ as the set of all operation within $T_i$ from the set \{BeginTransaction, TransactionaFile.Read, TransactionalFile.Write, EndTransactioni\} we would have: \\

Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\

proof: Follows from defenition. \\

Rule 2) If an operation $a \in OP{T_i}$ has multiple prcedecors (denoted as $OP_{precedesors}$) that their changes overlap each other, then if all of them are from sets other than $OP{T_i}$, $a$ sees the "changes" made by the $op_i \in OP_{predecesors}$ such that $op_i$ has the greatest "commit instant"  . Otherwise, $a$ sees the most recent precedesor in $OP{T_i}$. \\

proof: the first part follows from Def 4 , second derives from Def 4 and second part of Def 1.\\

Rule 3- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  op{T_k}$ if $op_i \rightarrow op_k$ and $op_k \rightarrow op_j$ then $op_i \rightarrow op_j$ \\

proof: Follows from the defenition of $\rightarrow$ \\

Rule 4- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\

proof: Follows from Rule 2 and Def 7. \\

Rule 5- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $T_j$ should not \emph ONLY precede any members of $T_{commited}$ (hence they should succed)\\

proof: $T_i$ denotes the last commited member of $T_{commited}$. Lets assume on the contrary $T_j$ only precedes $T_i$. This means according to def 7, all operations in $OP_i$ sees the effects made by those in $OP_j$. \\

If an operation $op_{i_1}$ in $OP_i$, affects some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption. On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$. If no operations in $OP_i$ affects another in $OP_j$, then the set of all opeartions in $OP_i$ both precede and succed those in $OP_j$, and hence the contraray to the assumption. In this case, the transaction are conceptually interchangable. In either case, $T_j$ either "succeds" or "succeds and precedes" $T_i$. Either way it succeds the other. \\

The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$. Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$. Same reasoning is applied for all the members of $T_{commited}$. \\

Rule 6- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_i$  should not \emph ONLY precede $op_{all}$ (hence it should at least succed)\\

Follows immediately from rule 4 and def 7.

\subsection{TransactionalFile Opeartions}
TransactioalFiles can be either created inside or outside $T$. The TransactionalFile object ensures transactional access no matter where it is created and accessed. Meaning the first time $T_i$ \emph {uses} $tf_j$ the flow of the program should look like no other piece of code (i.e Transactional and non-transactional) outside $T_i$ will \emph {modify} $tf_j$ before $OP(endtransaction)_{T_i}$. Otherwise, $T_i$ has to abort. \\

A Transactionalfile can be shared among any subset of the members of $T$. If shared, the offset is shared between these too.

\section{Implications for the System}
Now, if $T_i$ and $T_j$ do not either modify the data the other one uses, according to Rule 4 both can commit. This means even if $T_i$ accesses $tr_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit. \\

Below we will give a list of principles with the proofs on the operations and how they affect the data. We would using this table then establish the rules our system would go by. Before going to this, it should be noted that according to rule 6 even if all but one operations in a set suucced all operations in the other, still the transaction can not commit. therefore it takes only one operation to make the transaction dependent (it should succced others but can not since one of the operations in its set already preceded an operation in an already commited transaction). Formally, if there is an operation $b \in OP_{T_j}$ and an operation $a \in OP_{T_j}$ such that $b$ does not succed $a$ (or equivalently only precedes $a$) then $T_j$ can not succed $T_i$. In the rules below $T_i$ is not commited yet and $T$ denotes the set of all commited or active transactions. \\

Assumption : The reads within transaction do actually occur when they are encountered. However, no change to the file system is done before commit instant as said before (writes, changing the offset and etc.)\\

Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.

Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.//

proof: If the data is not valid anymore it means the data has changed since $t_{i-1}$. This implies at least one operation $b$ has chaged the data since the use. $b$ is either a succesor in the same transaction or a different one. According to Def 1 and Def 3, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem. Hence $b$ belongs to a different transaction namely $T_j$. Since $T_j$ should have already commited, according to Rule 6 all operation in $OP_{T_i}$ should succed those in $OP_{T_j}$, however, we know there is at least an operation $a$ that does not succced $b$ (since it has not seen the "changes" made by $b$). Hence, $T_i$ can not commit.\\

Principle 2) 1-A seek operation in $OP_{T_i}$ does not make $T_i$ dependent on any data and hence does not count as "using" ("use" as defined in Def 1).\\

The seek operations seeks to an offste within the file descriptor regardless of the changes made by opretaions in all transaction, hence the result would always be the same so according to Def 2 it does not count as using.\\

Principle 3) 1- A read operation in $OP_{T_i}$ "uses" contents read and makes $T_i$ dependent on the file contents read.\\

proof: Due to assumtion 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different. According to Def 2 it uses the data\\

Principle 4) 1- A write operation in $OP_{T_i}$ does not make $T_i$ dependent on file contents.\\

proof: The result of a write would always be the same contents thus, according to Def 2 does not count as using.\\

Assumption: Each operation has an offset status assioated with it. We call this operation.offsetstatus\\

Assumption: An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant. An operation with absolute offset means the value is absolute and does not depend on any other operation OR the operation only specifies a specific value for the offset for the next operation (i.e. seek). An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transactions. \\

Principle 5: an operation with defeinte offset status assosiated with it is the only one "using" the offset value.\\

proof: For speculative and absolute it comes form the defeniton that they do not count as using, since one is determined at commit instant and hence read at the same time, and the other is always the same value. However, with defenite, if some other transaction changes the offset of the file descriptor, then the result of the operation would have been possibly different. According to Def 2 it uses the offset data.\\

Def: We define a function $f$ that takes as input an operation (i.e. seek, read, write) and gives as the output the offsetstatus assosiated with that operation. In speaking, $f$ determines the offsetstatus assoiated with an operation given that it is the ONLY operation in the operation set of the transaction. \\

1- $f$(Seek) = Absolute

proof: seek operation does not invlove reading offset value hence, according to assumptions it is considered as absoulute.\\

2-$f$(Read) = Defenite

proof: Since according to Principle 3, read is actually done before the commit instant and hence can not be relocated in the commit instant. According to Principle 1 and 5 the offset the read is done from should not be affected by other members of $T$ before this transaction gets to its commit instant. This means not the only offset can not be relocated, but a check should be done at the commit instant for its validity.\\

3-$f$(Write) = Speculative

proof: If write is the only operation, then since according to Principle 4 the write does not use any file contents before commit instant, hence the ofsset value can be determined at commit instant from the most recently commited offset value by then. Then the write is done on the offset. This preserves the semantics since the commit instant is atomic by defenition and Rule 6 and 5 are preserved, as the write operation is getting the most recent data(offset) and hence would see all the changes made to it by commited transactions so far and hence this write operation would succed all the operations in other commited transaction. Consequently this transaction can succed those.\\

Requirements: To determine an operation should use Absolute, Define or Speculative offset type (the first and third would be used in commit instant) respective to other operatins in the set, the requirements below should be provided:\\

Req 1- 1-Any operation follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Absolute, has offsetstatus = Absolute itself. 2-Any operation that applying $f$ to it would yield in Absolute, has offsettype = absolute \\

proof: 1-Lets assume $op$ is the first operation with offsettype = Absolute in the set of operatopns. The immediate operation ($op_{imm}$) after $op$ uses the absolute offset specified by $op$ or the absolute offset advanced by a certain number in case of read or write. $op_{imm}$ either advances this value or specifies another absolute value, in either case the offset type for $op_{imm}$ would be absolute. The same reasoning could be done for all the follwing operations.\\

2- Since such an operation is seek and seek regardless of all other operation (in and out of transaction) sets the offset and hence is always absolute.\\

Req 2- 1- Any operations $op$ that applying $f$ on it would yield in Definite, has offsettype = Defenite unless speified otherwise by Req 1  2-Any operation immediately follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Defenite, has offsetstatus = Defenite itself. unless specified otherwise by Req 1\\

proof: 1- if $f$ makes the output Defenite it means this operation should "use" offset value at that time unless some previous instruction has set the offset to specific value independent of other transactions and thus changing the offset value would not have any effect on the outcome of $op$ as the value $op$ should be carried on from would be independent. Operation having such an effect is the one with Absolute offsettype.\\

2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.

Req 3: Any operation with offsetstaus = Defenite, should change the offsetstatus for prveious operations with a value of Speculative, to Defenite.\\

If $op.offsettype = Definte$ means no previous operations are Absolute (Req 1). So it just could be a mixture of Speculative and Defenite. Lets assume $op_{Def}$ as the first operation after a $op_{spec}$ a Speculative one (Rq 2 ensure after A Defenite there is no Speculative).  $op_{Def}$ makes the offset bound to a specific value and $op_{Def} succeds $op{Spec}$ so it should be able to see the changes made by $op{Spec} this neccesitaes that $op{Spec}$ be done at a specific offset such that when advanced as the effect of operation, it gives the offset chosen by $op{Def}$, otherwise $op{Def}$ does not see the effects of $op{Spec}$ which is in contradiction to presumtions. Hence, $op_{Spec}.offsettype$ should be converted to Defenite.\\

Req 4: Any operation $op$ which applying $f$ on it yields in Speculative has offsettype=Speculative unless specified otherwise by previous requirements.\\

proof: If we denote $OP_{prev}.offsettype$ as the offsettypes for the prviously encountered operations, considering all requirements this means all (if any) the members of $OP_{prev}$ should be Speculative for $op$ to be able to be Speculative. In this case the offset passed to $op$ is Speculative and if $op$ is Speculative as considered alone then it would carry on the actions in the passed-in Speculative offset.\\

Def: We define a function $g(offsetstat_1, offsettat_2, ..., offsetstat_{n-1}, operation)$ that takes an input  $n-1$ number of $op.offsetstatus$ plus an operation and gives as the output $n$ number of $op.offsetstatus$. The $g$ functions provides the requirements mentioned above. Follwing rules determine the output, the rules are ordererd according to their priority:\\

1- if $f(operation) = Absolute$, $g(offsetstat_1, ..., {offsetstat_{n-1}}, operation) = ({offsetstat_1}, ..., {offsetstat_{n-1}}, Absolute)$ leaving all offsetstats intact.\\

2- if $f(operation) = Defenite$:\\

\hspace{ 8mm}
	2.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}$\} such that offset = Absolute,  $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ... ,Absolute)$ leaving all offsestats intact.\\

\hspace{ 8mm}
	2.2- else $\forall offsetstat \in (offsetstat_0, ..., offsetstat_{n-1})$ if offsetstat = Speculative, change its value to Defenite in the output of $g$, plus appending a Defenite to the output (for instane $g(speculative, speculative, read) = (defenite, defeinte, definte)$)\\

3- if $f(operation) = Speculative$:\\

\hspace{ 8mm}
	3.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offset = Absolute, $g(offsetstat_1, ... offsetstat_{n-1}, operation) = (offsetstat_1, ... Absolute)$ leaving all offsestats intact.\\

\hspace{ 8mm}
	3.2- else if $\exists offsetstat \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offsetstat = {Defenite},  $g(offsetstat_1, ...,  offsetstat_{n-1}, operation) = (offsetstat_1 ,..., offsetstat_{n-1}, Defenite)$\\

\hspace{ 8mm}
	3.3- else $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ..., offsetstat_{n-1}, Speculative)$\\

1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4.

%$f: \{op_0.offsetstatus,op_1.offsetstatus,...,op_{n-1}.offsetstatus\} \rightarrow \{op_0.offsetstatus, op_1.offsettatus,...,op_{n-1}.offsetstatus,op_m.offsetstatus, \}

%2- Since due to assumption 1, the read should be actually done, it has to be done from a real offset, and since the commited offset at the commit instant is unknown in adavance, the currenlty most recent commited offset is chosen. This makes the read and hence transaction dependent on the offset value read.

%2- Since all the following read and writes at least succed this seek operation, they should be able to see the changes made by it unless some other operation in between changes the data in question (offset). Lets first assume the operation ($op$) following the seek. If $op$ is a read or write, then it would carry on reading or writing the data from the absolute offset so it would advance the aboslute offset resulting in another absolute offset and hence no "use" of the actual offset would be applicable. If the following is a seek, then the resultant offset would be another absolute offste. Same reasoning could be done for all the succeding operations and hence the offset would be still absolute. To prove only seek can make the offset absolute it should have been made absolute by read or write, however as we'll see in Principles 2 and 3 they can not yield in an absolute offset. Hence, an absolute offset indicates there has been a seek.\\
%According to priciple 1 the offset chosen should be validated at the the commit instant.\\
\section{Implementation Overview}

%proof: A write operation writes to the most recently commited offset (unless imposed otherwise by a seek or a prior read or a following read as shown above) of the file descriptor.  According to Def 2, it does not "use" any data. Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known. 
Now we will describe the components of our system and demosntrate how the algorithm

to be continued

%\begin{tabular}{c|c|c|}
\end{document}

### 2008-09-15 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ should be able to see the changes made by $op_i$ unless data has been changed by a more recent precedessor  \\
+Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ sees the changes made by $op_i$ unless data has been changed by a more recent precedessor.
+Furthermore  \\
 
@@
 
-Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.
+Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.\\
 
-Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.//
+Principle 0: An operation should not see any modifications other than those made by precedessors (either in the same transaction or others)\\
+
+proof: Obviously such modifications are not valid and are probably part of a faulty operation.\\
+
+Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.\\
 
@@
 This implies at least one operation $b$ has chaged the data since the use.
-$b$ is either a succesor in the same transaction or a different one.
+$b$ is either a succesor (since the changes were not seen) in the same transaction or a different one.
 According to Def 1 and Def 3, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem.
@@
 
-Assumption: Each operation has an offset status assioated with it. We call this operation.offsetstatus\\
+Assumption: Each operation has a offset status assioated with it. We call this operation.offsetstatus. Each operation has a data satus assosiated with it namely operation.datastatus\\
 
@@
 seek).
-An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transactions.
-\\
+An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transaction and not being valid at commit instant\\
+
+Assumption: Based on previous assumptions read.datastatus = Defenite and others are Speculative, hence they do not use the "file contents"
 
@@
 
-2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.
+2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.\\
 
@@
 In this case the offset passed to $op$ is Speculative and if $op$ is Speculative as considered alone then it would carry on the actions in the passed-in Speculative offset.\\
+
+Req 5: An operation with datastatus = Defenite, converts all the speculative offsttypes of the previous operations to Defenite. This requirement is always enforced.\\
+
+proof: Since if datastatus = Defenite, this mean the operation is "using" or "reading" some file contents- an irreversible action- and as this operation should be able to see the modifications made by all preceding operations, if these are speculative, at commit instant they may "relocate" their modifications, this means eitehr $op$ may not see some changes made by precedessors or may see some changes not made by any precedessors (since the speculatively changes were used by $op$ however these did not get reflected in the actual file system since they were relocated at commit instant).
+Either way contradicts the defenitions and principles (Def 8 and Principle 0).\\
+
+Note: Req 5 suggest if datatype = Definite this causes all the previous operation with Speculative as offsettype to be changed to Defenite.
 
@@
 
-1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4.
+4- After doing the above check if datastatus = Defenite, then change all offsettypes in the input that are Speculative to Defenite in the output.
+
+1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4. 4 also ensures Req 5.
 
@@
 Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known.
-Now we will describe the components of our system and demosntrate how the algorithm
+Now we will describe the components of our system and demosntrate how the algorithm conforms to the function just described, and how all the rules principles are gurantedd.
 

### 2008-09-15 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 \section{Implications for the System}
+
+\subsection{General Principles}
 Now, if $T_i$ and $T_j$ do not either modify the data the other one uses, according to Rule 4 both can commit.
@@
 
-proof: Due to assumtion 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different.
+proof: Due to assumption 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different.
 According to Def 2 it uses the data\\
@@
 proof: The result of a write would always be the same contents thus, according to Def 2 does not count as using.\\
+
+\subsection{A Model for Offset and Data Dependeny for Operations}
 

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
+A Transaction consists of a sequence of operations.
+Thus, a transaction can be represented as the \{$OP_1$, $OP_2$, ..., $OP_n$\}.
 The flow of program should be in a manner that we could have an arbitrary serial order of the members of $T$ (e.g.
 $T_5,T_6,T_1$,...) or any other order.
-The serial order should be in such a way that for any given two members of the set $T$, either the effect of all opertaions of \{ TransactionalFile.Read, TransactionalFileWrite, TransactionalFile.Seek()\} within $T_i$ should be visible to $T_j$ or none should be visible.
+The serial order should be in such a way that for any given two members of the set $T$, it looks all the operations of one occur before all the operation of the other.
 In the first case we would say the $T_i$ precedes $T_j$ and in the seconds case $T_j$ preceds $T_i$ and $T_i$ can observe all the effects made by the operations in $T_j$.
@@
 
-Def 1- 1-An operation in $T_i$ is said to have "changed" or "affected" some data structure in correspondece to all members of $OP_{T- T_i}$ , when it reflects the changes in the filesystem in such a way that the modification is durable and irreversible.
+Def 1- \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length)\}.
+We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
+
+%Def 1- 1-An operation in $T_i$ is said to have "changed" or "affected" some data structure in correspondece to all members of $OP_{T- T_i}$ , when it reflects the changes in the filesystem in such a way that the modification is durable and irreversible.
 A transaction with such an operation $T_i$ in its operation set is said to have changed the data 2- An operation in $T_i$ is said to have "changed or affeced the data in correspondence to all the operations in $OP_{T_i}$ as soon as the operation is encountered \\
 
-Def 2- An operation in $T_i$ is said to have "used" the data when it has read some data and has done some actions that is potentially irreversible.
+Def 2- \emph{Operations Sharing Resources} 1- A readoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
+2- A readdata and writedata operations are said to be sharing resources if they both operate on the same inode AND the range of (offset, offset + length) within one overlaps with that of the other.\\
+
+Def 3- A read operation can only see the writes made by write operations sharing reources.\\
+
+Def 4- \emph{Commit Instant}: A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" mabe by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$ .
+An operation $\in OP_{T_i}$ is said to commit if and only if $T_i$ commits.
+Commit instant are not splittable, hence it appears to other transactions that all writes are refleted in the file system together.\\
+
+Def 5- \emph{No See In Future}: Assume $T_i$ is an uncomiited transaction and $T_{commited}$ indicates the set of commited transaction.
+A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by write operation $b$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
+
+\hspace{7mm} 1- $a \in OP_{T_j}$ ($j \neq i$)  such that $T_j \in T_{commited}$ \\
+
+\hspace{7mm} 2- $a \in OP_{T_i}$ and $a$ happens before $b$ in the natural order of the transaction. Formally, $a$ has a lower position than that of $b$ in $OP_{T_i}$ = \{$OP_1$, ..., $OP_n$\} \\
+
+Def 7- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$.
+Otherwise, $b \rightarrow a$.
+\\
+
+Corrolary- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations.
+Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$.
+\\
+
+proof: Consider case 1 that all precedessors are from sets of operations other than that of $a$'s, according to Def 4 all these prcedessors belong to comitted transactions.
+Assume $T_i$ is accessing data at $t_i$, $t_i$ is neccasarily gretaer than all members of \{$committime_{T_1}, ..., commitime_{T_{i-1}}$\},and hence the writes to $r_i$ made by these commited transaction, have accroding to Def 1 been already reflected in the file system.
+Since, $T_{i-1}$ has the greatest commit instant its changes have overriiden that of previously commited transactions and thus, $a$ reading $r_i$ from file system sees these changes.\\
+
+In case 2 that there are operations preceding $a$ in $OP_{T_i}$, according to defenition of transaction $r_i$ should be read from the writes made by write operations in $T_i$, and as the last of such write operation overrides the written data to $r_i$ by other operations, $a$ gets to see the most recent precedessor in $T_i$.\\
+
+Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence elationship is not etemined between two transactions by Def 6.
+1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
+2-If two operation belong to the same transaction, then the one that occurs earlier in natural order of transaction precedes the other.
+3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
+4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ or it is $op_i \rightarrow op_j$.
+5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\
+
+Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if there is a precedence relationship between $op_{T_i}$ and $op_{T_i}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+
+%Def 2- An operation in $T_i$ is said to have "used" the data when it has read some data and has done some actions that is potentially irreversible.
 hence if the data in question was to change, $op$ would have different results.
@@
 
-Def 3- A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "changes" in the filesystem or equivalently makes it changes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$ .
-An operation $\in OP_{T_i}$ is said to commit if and only if $T_i$ commits.
-Commit instant are not splittable, hence it appears to other transactions that all changes are refleted in the file system together.\\
-
-Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ sees the changes made by $op_i$ unless data has been changed by a more recent precedessor.
+%Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ sees the changes made by $op_i$ unless data has been changed by a more recent precedessor.
 Furthermore  \\
 
-Def 5- Succeds relationship is defined similarly.  \\
+%Def 5- Succeds relationship is defined similarly.  \\
 
-Def 6- If operation $a$ both precedes and succeds operation $b$ since they do not share any resources so the changes can be made visible, $a$ both precedes and succeds $b$. \\
+%Def 5- \emph{Precedence Relationship for Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, 1- if $b$ see the writes made by the $a$ to $r_i$ and their relationship conforms to Def 4, then $a$ precedes $b$ ($a \rightarrow b$) 2- if $b$ does not see the changes written by $a$, however their relatioship conforms to Def 4,   $r_i$ has been changed by operation $c$ such that $t_{a-commit-instant}<t_{c-commint-instant}$ and $b$ sees the write made by $c$, then $a \rightarrow b$.
+3- If $b$ does not see the changes made by $a$ and $r_i$ has been changed by operation $c$ such that 3- Otherwise $b$ precedes $a$.
+Precedence is only defined for a read and write operation sharing resources.\\
 
-Def 7- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$,  then $T_i$ \emph {can} $\rightarrow T_j$) \hspace{8mm} (this defines precedes relationship for members of $T$) \\
-
-Def 8- An operation $op \in OP_{T_i}$ should be able to see the "changes" 1- made by $OP_{T_commited}$ and 2-$oper \in OP_{T_i}$ that in natural order of transaction occur before $op$
+%Def 6- If operation $a$ both precedes and succeds operation $b$ since they do not share any resources so the changes can be made visible, $a$ both precedes and succeds $b$. \\
 
 \subsection{Rules}
-If we denote $\rightarrow$ as the relation precedes between operations and $OP_{T_i}$ as the set of all operation within $T_i$ from the set \{BeginTransaction, TransactionaFile.Read, TransactionalFile.Write, EndTransactioni\} we would have: \\
+%If we denote $\rightarrow$ as the relation precedes between operations and $OP_{T_i}$ as the set of all operation within $T_i$ from the set \{BeginTransaction, TransactionaFile.Read, TransactionalFile.Write, EndTransactioni\} we would have: \\
 
-Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\
+i%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\
 
-proof: Follows from defenition. \\
+%proof: Follows from defenition. \\
 
-Rule 2) If an operation $a \in OP{T_i}$ has multiple prcedecors (denoted as $OP_{precedesors}$) that their changes overlap each other, then if all of them are from sets other than $OP{T_i}$, $a$ sees the "changes" made by the $op_i \in OP_{predecesors}$ such that $op_i$ has the greatest "commit instant"  .
+%Rule 2) If an operation $a \in OP{T_i}$ has multiple prcedecors (denoted as $OP_{precedesors}$) that their changes overlap each other, then if all of them are from sets other than $OP{T_i}$, $a$ sees the "changes" made by the $op_i \in OP_{predecesors}$ such that $op_i$ has the greatest "commit instant"  .
 Otherwise, $a$ sees the most recent precedesor in $OP{T_i}$.
@@
 
-proof: the first part follows from Def 4 , second derives from Def 4 and second part of Def 1.\\
+%proof: the first part follows from Def 4 , second derives from Def 4 and second part of Def 1.\\
 
-Rule 3- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  op{T_k}$ if $op_i \rightarrow op_k$ and $op_k \rightarrow op_j$ then $op_i \rightarrow op_j$ \\
+Rule 3- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if there is a precedence relationship between $op_i$ and $op_k$ sand $op_i \rightarrow op_k$, and if there is a relationship between $op_k$ and $op_j$ and $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
 

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence elationship is not etemined between two transactions by Def 6.
+Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence relationship is not detemined between two operations by Def 6.
 1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
@@
 3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
-4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ or it is $op_i \rightarrow op_j$.
+4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ OR it is $op_i \rightarrow op_j$.
 5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\
 
-Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if there is a precedence relationship between $op_{T_i}$ and $op_{T_i}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+
+Def 10- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established.\\
+
+Corrolary: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}
+
+proof: Follows imeediately from Def 9 and Def 10.
 

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

--- 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
@@
 
+Def 6- \emph{Precedence Relationship for Read-Write Operations}:
+
 Def 7- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$.
 Otherwise, $b \rightarrow a$.
-\\
+For other pairs of operations or read-writes that do not share resources $a \rightarrow b$ and $b \rightarrow a$.\\
 
@@
 
-Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence elationship is not etemined between two transactions by Def 6.
+%Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence relationship is not detemined between two operations by Def 6.
 1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
@@
 3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
-4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ or it is $op_i \rightarrow op_j$.
+4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ OR it is $op_i \rightarrow op_j$.
 5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\
 
-Def 9- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if there is a precedence relationship between $op_{T_i}$ and $op_{T_i}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+Def 8- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+
+Def 9- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established.\\
+
+Corrolary: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}
+
+proof: Follows imeediately from Def 8 and Def 9.
 
@@
 
-Rule 3- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if there is a precedence relationship between $op_i$ and $op_k$ sand $op_i \rightarrow op_k$, and if there is a relationship between $op_k$ and $op_j$ and $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
+%Rule 1- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if there is a precedence relationship between $op_i$ and $op_k$ sand $op_i \rightarrow op_k$, and if there is a relationship between $op_k$ and $op_j$ and $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
 
@@
 
-Rule 4- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
+Rule 2- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
 
-proof: Follows from Rule 2 and Def 7. \\
+proof: Since Def 9 ensures all operations in $OP_{T_i}$ precede those in $OP_{T_j}$. \\
 
-Rule 5- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $T_j$ should not \emph ONLY precede any members of $T_{commited}$ (hence they should succed)\\
+Rule 5- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\
 
-proof: $T_i$ denotes the last commited member of $T_{commited}$.
-Lets assume on the contrary $T_j$ only precedes $T_i$.
-This means according to def 7, all operations in $OP_i$ sees the effects made by those in $OP_j$.
-\\
+proof: $T_i$ denotes the last commited member of $T_{commited}$. Lets assume on the contrary $T_i$ does not precede $T_j$ and hence $T_j \rightarrow T_i$.\\
 
-If an operation $op_{i_1}$ in $OP_i$, affects some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption.
+If there is not a pair of (read, write) or (write, read), sharing resource $r_n$ in the two transaction, then $T_i \rightarrow T_j$ according to Def 7 and Def 9.\\
+
+If there are such operations, 1-At least an operation $a$ reads from $r_n$ in $OP_i$ sees the writes made by a write operation on $r_n$($b$) in $OP_j$, however since $T_j$ is just about to commit and acording to Def 4, writes are not reflected till commit instant, hence $a$ could not have read the writes made by $b$ and consequently $a$ does not precede $b$ contradicting the assumption $T_j \rightarrow T_i$ .
+OR 2- An operation $a$ in $T_i$ writes to resource $r_i$ and operation $b$ in $T_j$ reads resource $b$, according to Def 5 and Def 5 $a$ precedes $b$ and $b$ does not precede $a$, hence contradicting the assumption that $T_j \rightarrow T_i$.\\
+
+If
+If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption.
 On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$.

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Def 6- \emph{Precedence Relationship for Read-Write Operations}:
-
-Def 7- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$.
+Def 6- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$.
 Otherwise, $b \rightarrow a$.
@@
 
-Corrolary- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations.
+Corrolary 1- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations.
 Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$.
@@
 
-Def 8- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+Def 7- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
 
-Def 9- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established.\\
+Def 8- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the behavior of the program.\\
 
-Corrolary: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}
+Corrolary 2: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}
 
-proof: Follows imeediately from Def 8 and Def 9.
+proof: Follows imeediately from Def 8 and Def 9. This is later proven formally.i\\
 
@@
 
-i%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\
+%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\
 
@@
 
-proof: Follows from the defenition of $\rightarrow$ \\
+%proof: Follows from the defenition of $\rightarrow$ \\
 
-Rule 2- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
+Rule 1- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
 
@@
 
-Rule 5- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\
+Rule 2- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\
 
@@
 
-If
-If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption.
+The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
+Now according to rule 3, since $T_{i-1}$ precedes $T_i$ and $T_i$ precedes $T_{j}$, hence $T_{i-1}$ precedes $T_{j}$.
+Same reasoning is applied for all the members of $T_{commited}$.
+\\
+
+%If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption.
 On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$.
@@
 
-The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
-Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$.
-Same reasoning is applied for all the members of $T_{commited}$.
-\\
+Rule 3- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_{all}$  should precede $op_{i}$.\\
 
-Rule 6- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_i$  should not \emph ONLY precede $op_{all}$ (hence it should at least succed)\\
-
-Follows immediately from rule 4 and def 7.
+Follows immediately from Rule 2 and Def 7.
 

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-\subsection{General Principles}
-Now, if $T_i$ and $T_j$ do not either modify the data the other one uses, according to Rule 4 both can commit.
-This means even if $T_i$ accesses $tr_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit.
+\subsection{General Implications}
+Now, if $T_i$ and $T_j$ do not either write the data the other one reads, according to Rule 2 and 3 both can commit.
+This means even if $T_i$ accesses $r_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit.
 \\
@@
 We would using this table then establish the rules our system would go by.
-Before going to this, it should be noted that according to rule 6 even if all but one operations in a set suucced all operations in the other, still the transaction can not commit.
-therefore it takes only one operation to make the transaction dependent (it should succced others but can not since one of the operations in its set already preceded an operation in an already commited transaction).
-Formally, if there is an operation $b \in OP_{T_j}$ and an operation $a \in OP_{T_j}$ such that $b$ does not succed $a$ (or equivalently only precedes $a$) then $T_j$ can not succed $T_i$.
+Before going to this, it should be noted that according to rule 3 even if all but one operations in a set precede all operations in the other, still the transaction can not commit.
+Therefore it takes only one operation to make the transaction dependent (all the committed transaction should precede this transaction but can not since one of the operations in the committed transaction does not precede an operation in this transaction).
+Formally, if there is an operation $b \in OP_{T_j}$ and an operation $a \in OP_{T_i}$ such that $a$ does not precede $b$ then $T_i$ can not precede $T_j$.
 In the rules below $T_i$ is not commited yet and $T$ denotes the set of all commited or active transactions.
@@
 
-Assumption : The reads within transaction do actually occur when they are encountered.
+%Assumption : The reads within transaction do actually occur when they are encountered.
 However, no change to the file system is done before commit instant as said before (writes, changing the offset and etc.)\\
 
-Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.\\
+%Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.\\
 
-Principle 0: An operation should not see any modifications other than those made by precedessors (either in the same transaction or others)\\
+%Principle 0: An operation should not see any modifications other than those made by precedessors (either in the same transaction or others)\\
 
@@
 
-Principle 1) If an operation $a$ that "uses" some data (reads the data at some $t < t_{commit}$(the commit instant)), it should be ensured that the data is still valid in the actual file system at $t_{commit}$ (commit instant) or $T_i$ has to abort.\\
+Principle 1) If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
 
-proof: If the data is not valid anymore it means the data has changed since $t_{i-1}$.
-This implies at least one operation $b$ has chaged the data since the use.
-$b$ is either a succesor (since the changes were not seen) in the same transaction or a different one.
-According to Def 1 and Def 3, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem.
-Hence $b$ belongs to a different transaction namely $T_j$.
-Since $T_j$ should have already commited, according to Rule 6 all operation in $OP_{T_i}$ should succed those in $OP_{T_j}$, however, we know there is at least an operation $a$ that does not succced $b$ (since it has not seen the "changes" made by $b$).
+proof: If the data is not valid anymore it means the data $r_n$ has been written since $t_{i-1}$.
+This implies at least one operation $b$ has written the data since the use and $b$ does not precede $a$ and $a$ precedes $b$.
+$b$ is either an operation in the same transaction or a different one.
+According to Def 4, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem so it is still valid at commit instant.
+Hence, $b$ belongs to a different transaction namely $T_j$.
+Since $T_j$ should have already commited, according to Rule 3 all operation in $OP_{T_j}$ should precede those in $OP_{T_i}$, however, we know there is at least an operation $b$ that does not precede $a$ (since $a$ has not seen the "writes" made to $r_n$ by $b$).
 Hence, $T_i$ can not commit.\\
 
-Principle 2) 1-A seek operation in $OP_{T_i}$ does not make $T_i$ dependent on any data and hence does not count as "using" ("use" as defined in Def 1).\\
+%Principle 2) 1-A seek operation in $OP_{T_i}$ does not make $T_i$ dependent on any data and hence does not count as "using" ("use" as defined in Def 1).\\
 
-The seek operations seeks to an offste within the file descriptor regardless of the changes made by opretaions in all transaction, hence the result would always be the same so according to Def 2 it does not count as using.\\
+%The seek operations seeks to an offste within the file descriptor regardless of the changes made by opretaions in all transaction, hence the result would always be the same so according to Def 2 it does not count as using.\\
 
-Principle 3) 1- A read operation in $OP_{T_i}$ "uses" contents read and makes $T_i$ dependent on the file contents read.\\
+%rinciple 3) 1- A read operation in $OP_{T_i}$ "uses" contents read and makes $T_i$ dependent on the file contents read.\\
 
-proof: Due to assumption 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different.
+%proof: Due to assumption 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different.
 According to Def 2 it uses the data\\
 
-Principle 4) 1- A write operation in $OP_{T_i}$ does not make $T_i$ dependent on file contents.\\
+%Principle 4) 1- A write operation in $OP_{T_i}$ does not make $T_i$ dependent on file contents.\\
 
-proof: The result of a write would always be the same contents thus, according to Def 2 does not count as using.\\
+%proof: The result of a write would always be the same contents thus, according to Def 2 does not count as using.\\
 

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Below we will give a list of principles with the proofs on the operations and how they affect the data.
-We would using this table then establish the rules our system would go by.
-Before going to this, it should be noted that according to rule 3 even if all but one operations in a set precede all operations in the other, still the transaction can not commit.
+It should be noted that according to Rule 3 even if all but one of the transactions in the set of committed transaction precede $T_i$ which is about to commit, , still the transaction can not commit.
 Therefore it takes only one operation to make the transaction dependent (all the committed transaction should precede this transaction but can not since one of the operations in the committed transaction does not precede an operation in this transaction).
@@
 
-Assumption: Each operation has a offset status assioated with it. We call this operation.offsetstatus. Each operation has a data satus assosiated with it namely operation.datastatus\\
+%Assumption: Each operation has a offset status assioated with it. We call this operation.offsetstatus. Each operation has a data satus assosiated with it namely operation.datastatus\\
 
-Assumption:  An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant.
+%Assumption:  An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant.
 An operation with absolute offset means the value is absolute and does not depend on any other operation OR the operation only specifies a specific value for the offset for the next operation (i.e.
@@
 
-Assumption: Based on previous assumptions read.datastatus = Defenite and others are Speculative, hence they do not use the "file contents"
+%Assumption: Based on previous assumptions read.datastatus = Defenite and others are Speculative, hence they do not use the "file contents"
 
-Principle 5: an operation with defeinte offset status assosiated with it is the only one "using" the offset value.\\
+%Principle 5: an operation with defeinte offset status assosiated with it is the only one "using" the offset value.\\
 
-proof: For speculative and absolute it comes form the defeniton that they do not count as using, since one is determined at commit instant and hence read at the same time, and the other is always the same value.
+%proof: For speculative and absolute it comes form the defeniton that they do not count as using, since one is determined at commit instant and hence read at the same time, and the other is always the same value.
 However, with defenite, if some other transaction changes the offset of the file descriptor, then the result of the operation would have been possibly different.
@@
 
-Def: We define a function $f$ that takes as input an operation (i.e.
+%Def: We define a function $f$ that takes as input an operation (i.e.
 seek, read, write) and gives as the output the offsetstatus assosiated with that operation.
@@
 
-1- $f$(Seek) = Absolute
+%1- $f$(Seek) = Absolute
 
-proof: seek operation does not invlove reading offset value hence, according to assumptions it is considered as absoulute.\\
+%proof: seek operation does not invlove reading offset value hence, according to assumptions it is considered as absoulute.\\
 
-2-$f$(Read) = Defenite
+%2-$f$(Read) = Defenite
 
-proof: Since according to Principle 3, read is actually done before the commit instant and hence can not be relocated in the commit instant.
+%proof: Since according to Principle 3, read is actually done before the commit instant and hence can not be relocated in the commit instant.
 According to Principle 1 and 5 the offset the read is done from should not be affected by other members of $T$ before this transaction gets to its commit instant.
@@
 
-3-$f$(Write) = Speculative
+%3-$f$(Write) = Speculative
 
-proof: If write is the only operation, then since according to Principle 4 the write does not use any file contents before commit instant, hence the ofsset value can be determined at commit instant from the most recently commited offset value by then.
+%proof: If write is the only operation, then since according to Principle 4 the write does not use any file contents before commit instant, hence the ofsset value can be determined at commit instant from the most recently commited offset value by then.
 Then the write is done on the offset.
@@
 
-Requirements: To determine an operation should use Absolute, Define or Speculative offset type (the first and third would be used in commit instant) respective to other operatins in the set, the requirements below should be provided:\\
+%Requirements: To determine an operation should use Absolute, Define or Speculative offset type (the first and third would be used in commit instant) respective to other operatins in the set, the requirements below should be provided:\\
 
-Req 1- 1-Any operation follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Absolute, has offsetstatus = Absolute itself.
+%Req 1- 1-Any operation follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Absolute, has offsetstatus = Absolute itself.
 2-Any operation that applying $f$ to it would yield in Absolute, has offsettype = absolute \\
 
-proof: 1-Lets assume $op$ is the first operation with offsettype = Absolute in the set of operatopns.
+%proof: 1-Lets assume $op$ is the first operation with offsettype = Absolute in the set of operatopns.
 The immediate operation ($op_{imm}$) after $op$ uses the absolute offset specified by $op$ or the absolute offset advanced by a certain number in case of read or write.
@@
 
-2- Since such an operation is seek and seek regardless of all other operation (in and out of transaction) sets the offset and hence is always absolute.\\
+%2- Since such an operation is seek and seek regardless of all other operation (in and out of transaction) sets the offset and hence is always absolute.\\
 
-Req 2- 1- Any operations $op$ that applying $f$ on it would yield in Definite, has offsettype = Defenite unless speified otherwise by Req 1  2-Any operation immediately follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Defenite, has offsetstatus = Defenite itself.
+%Req 2- 1- Any operations $op$ that applying $f$ on it would yield in Definite, has offsettype = Defenite unless speified otherwise by Req 1  2-Any operation immediately follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Defenite, has offsetstatus = Defenite itself.
 unless specified otherwise by Req 1\\
 
-proof: 1- if $f$ makes the output Defenite it means this operation should "use" offset value at that time unless some previous instruction has set the offset to specific value independent of other transactions and thus changing the offset value would not have any effect on the outcome of $op$ as the value $op$ should be carried on from would be independent.
+%proof: 1- if $f$ makes the output Defenite it means this operation should "use" offset value at that time unless some previous instruction has set the offset to specific value independent of other transactions and thus changing the offset value would not have any effect on the outcome of $op$ as the value $op$ should be carried on from would be independent.
 Operation having such an effect is the one with Absolute offsettype.\\
 
-2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.\\
+%2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.\\
 
-Req 3: Any operation with offsetstaus = Defenite, should change the offsetstatus for prveious operations with a value of Speculative, to Defenite.\\
+%Req 3: Any operation with offsetstaus = Defenite, should change the offsetstatus for prveious operations with a value of Speculative, to Defenite.\\
 
-If $op.offsettype = Definte$ means no previous operations are Absolute (Req 1).
+%If $op.offsettype = Definte$ means no previous operations are Absolute (Req 1).
 So it just could be a mixture of Speculative and Defenite.
@@
 
-Req 4: Any operation $op$ which applying $f$ on it yields in Speculative has offsettype=Speculative unless specified otherwise by previous requirements.\\
+%Req 4: Any operation $op$ which applying $f$ on it yields in Speculative has offsettype=Speculative unless specified otherwise by previous requirements.\\
 
-proof: If we denote $OP_{prev}.offsettype$ as the offsettypes for the prviously encountered operations, considering all requirements this means all (if any) the members of $OP_{prev}$ should be Speculative for $op$ to be able to be Speculative.
+%proof: If we denote $OP_{prev}.offsettype$ as the offsettypes for the prviously encountered operations, considering all requirements this means all (if any) the members of $OP_{prev}$ should be Speculative for $op$ to be able to be Speculative.
 In this case the offset passed to $op$ is Speculative and if $op$ is Speculative as considered alone then it would carry on the actions in the passed-in Speculative offset.\\
 
-Req 5: An operation with datastatus = Defenite, converts all the speculative offsttypes of the previous operations to Defenite. This requirement is always enforced.\\
+%Req 5: An operation with datastatus = Defenite, converts all the speculative offsttypes of the previous operations to Defenite. This requirement is always enforced.\\
 

### 2008-09-17 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java
helpful progress reporting

@@ -397,6 +397,8 @@ public class OwnershipAnalysis {
       FlatNode fn = (FlatNode) flatNodesToVisit.iterator().next();
       flatNodesToVisit.remove(fn);
 
+      //System.out.println( "  "+fn );
+
       // perform this node's contributions to the ownership
       // graph on a new copy, then compare it to the old graph
       // at this node to see if anything was updated.
@@ -418,6 +420,12 @@ public class OwnershipAnalysis {
                            fn,
                            returnNodesToCombineForCompleteOwnershipGraph,
                            og);
+
+
+
+      //debugSnapshot(og,fn);
+
+
 
       // if the results of the new graph are different from
       // the current graph at this node, replace the graph
@@ -603,14 +611,20 @@ public class OwnershipAnalysis {
 
   // insert a call to debugSnapshot() somewhere in the analysis to get
   // successive captures of the analysis state
-  int debugCounter = 0;
-  int numIterationsIn = 80000;
-  int numIterationsToCapture = 53;
+  int debugCounter        = 0;
+  int numStartCountReport = 66000;
+  int freqCountReport     = 50;
+  int iterStartCapture    = 70000;
+  int numIterToCapture    = 100;
   void debugSnapshot( OwnershipGraph og, FlatNode fn ) {
     ++debugCounter;
-    if( debugCounter > numIterationsIn ) {
-      System.out.println( "   @@@ capturing debug "+(debugCounter-numIterationsIn)+" @@@" );
-      String graphName = String.format("snap%04d",debugCounter-numIterationsIn);
+    if( debugCounter > numStartCountReport &&
+	debugCounter % freqCountReport == 0 ) {
+      System.out.println( "    @@@ debug counter = "+debugCounter );
+    }
+    if( debugCounter > iterStartCapture ) {
+      System.out.println( "    @@@ capturing debug "+(debugCounter-iterStartCapture)+" @@@" );
+      String graphName = String.format("snap%04d",debugCounter-iterStartCapture);
       if( fn != null ) {
 	graphName = graphName+fn;
       }
@@ -621,7 +635,7 @@ public class OwnershipAnalysis {
 	System.exit( 0 );	
       }
     }
-    if( debugCounter == numIterationsIn + numIterationsToCapture ) {
+    if( debugCounter == iterStartCapture + numIterToCapture ) {
       System.out.println( "Stopping analysis after debug captures." );
       System.exit( 0 );
     }

### 2008-09-17 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -1013,7 +1013,9 @@ public class OwnershipGraph {
 	ReferenceEdge edge = edgeItr.next();
 	D_i = D_i.union(edge.getBeta() );
       }
+
       D_i = D_i.exhaustiveArityCombinations();
+
       paramIndex2rewriteD.put(paramIndex, D_i);
     }
 
@@ -1106,7 +1108,6 @@ public class OwnershipGraph {
 	}
       }
 
-
       // update reachable edges
       Iterator<ReferenceEdge> edgeReachableItr = edgesReachable.iterator();
       while( edgeReachableItr.hasNext() ) {
@@ -1124,7 +1125,6 @@ public class OwnershipGraph {
 
 	edgesWithNewBeta.add(edgeReachable);
       }
-
 
       // update upstream edges
       Hashtable<ReferenceEdge, ChangeTupleSet> edgeUpstreamPlannedChanges
@@ -1163,7 +1163,6 @@ public class OwnershipGraph {
     while( edgeItr.hasNext() ) {
       edgeItr.next().applyBetaNew();
     }
-
 
 
     // verify the existence of allocation sites and their
@@ -1334,7 +1333,6 @@ public class OwnershipGraph {
     }
 
 
-
     // return value may need to be assigned in caller
     if( fc.getReturnTemp() != null ) {
 
@@ -1396,7 +1394,6 @@ public class OwnershipGraph {
 	}
       }
     }
-
 
 
     // merge the shadow nodes of allocation sites back down to normal capacity

### 2008-09-17 Robust/src/Analysis/OwnershipAnalysis/ReachabilitySet.java

@@ -255,6 +255,10 @@ public class ReachabilitySet extends Canonical {
 
     int numDimensions = this.possibleReachabilities.size();
 
+    if( numDimensions > 10 ) {
+      System.out.println( "exhaustiveArityCombinations numDimensions = "+numDimensions );
+    }
+
     // add an extra digit to detect termination
     int[] digits = new int[numDimensions+1];
 
@@ -284,6 +288,20 @@ public class ReachabilitySet extends Canonical {
       // increment
       for( int i = 0; i < numDimensions+1; ++i ) {
 	digits[i]++;
+
+
+	if( i == 11 ) {
+	  System.out.print( "x " );
+	}
+
+	if( i == 15 ) {
+	  System.out.print( "@ " );
+	}
+
+	if( i == 17 ) {
+	  System.out.print( "# " );
+	}
+
 	if( digits[i] > maxArity ) {
 	  // this axis reached its max, so roll it back to min and increment next higher digit
 	  digits[i] = minArity;

### 2008-09-17 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Rule 2- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then all members of $T_{commited}$ should precede $T_j$ (hence they should succed)\\
+Rule 2-  \emph{Committed transaction Should Precede the About to Commit Transaction}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if all members of $T_{commited}$ precede $T_j$ (hence they should succed)\\
 
@@
 
-If there are such operations, 1-At least an operation $a$ reads from $r_n$ in $OP_i$ sees the writes made by a write operation on $r_n$($b$) in $OP_j$, however since $T_j$ is just about to commit and acording to Def 4, writes are not reflected till commit instant, hence $a$ could not have read the writes made by $b$ and consequently $a$ does not precede $b$ contradicting the assumption $T_j \rightarrow T_i$ .
-OR 2- An operation $a$ in $T_i$ writes to resource $r_i$ and operation $b$ in $T_j$ reads resource $b$, according to Def 5 and Def 5 $a$ precedes $b$ and $b$ does not precede $a$, hence contradicting the assumption that $T_j \rightarrow T_i$.\\
+If there are such operations, 1-At least an operation $a$ reads from $r_n$ in $OP_i$ sees the writes made by a write operation on $r_n$($b$) in $OP_j$, however since $T_j$ has commited after $T_i$ and writes are not reflected till commit instant, hence $a$ could not have read the writes made by $b$ and consequently $a$ does not precede $b$ contradicting the assumption $T_j \rightarrow T_i$ .
+OR 2- An operation $a$ in $T_i$ writes to resource $r_i$ and operation $b$ in $T_j$ reads resource $r_i$, according to Def 5 $a$ precedes $b$ and $b$ does not precede $a$, hence contradicting the assumption that $T_j \rightarrow T_i$.\\
 
@@
 
-Rule 3- If $T_j$ "commits" at instant $t_j$, and $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$ then $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, then $op_{all}$  should precede $op_{i}$.\\
+Rule 3-\emph{Operation in the Committed Transactions Precede Those in The Transaction About to Commit}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denoting the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, $op_{all}$  should precede $op_{i}$.\\
 
-Follows immediately from Rule 2 and Def 7.
+proof: Follows immediately from Rul2 and Def 7.
+
+Rule 4- \emph{If All committed Transactions Precede A Transaction About to Commit, It Commits}: $T_i$ commits if at its commit instant, $\forall T_j \in T_ccommitted T_j \rightarrow T_i$.
+
+proof: If $\forall T_j \in T_committed T_j \rightarrow T_i$, a total ordering can be established corresponding the precedence relationship and all writes made by committed transaction have been seen by reads in $T_i$, hence according to Def 8, a consistent sequence of transactions would be provided.
 
@@
 
-Principle 1) If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
+Principle 1) \emph{Reads Should be Validated At Commit Instant}: If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
 
@@
 Hence, $T_i$ can not commit.\\
+
+The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
+Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$.
+Same reasoning is applied for all the members of $T_{commited}$.
+\\
+
+Principle 2: emph{If Reads Are Valid At Commit Instant, the Transaction Commits}: If by applying Principle 1 for $T_i$ it is ensured that $\forall r_i \in R{T_i}$ (all data read by $T_i$) is still valid at commit instant, then $\forall T_j \in T_{committed} T_j \rightarrow T_j$ and hence according to Rule 4 $T_i$ commits.\\
+
+proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.\\
 
@@
 
-\subsection{A Model for Offset and Data Dependeny for Operations}
+%\subsection{A Model for Offset and Data Dependeny for Operations}
 
@@
 
-proof: Since if datastatus = Defenite, this mean the operation is "using" or "reading" some file contents- an irreversible action- and as this operation should be able to see the modifications made by all preceding operations, if these are speculative, at commit instant they may "relocate" their modifications, this means eitehr $op$ may not see some changes made by precedessors or may see some changes not made by any precedessors (since the speculatively changes were used by $op$ however these did not get reflected in the actual file system since they were relocated at commit instant).
+%proof: Since if datastatus = Defenite, this mean the operation is "using" or "reading" some file contents- an irreversible action- and as this operation should be able to see the modifications made by all preceding operations, if these are speculative, at commit instant they may "relocate" their modifications, this means eitehr $op$ may not see some changes made by precedessors or may see some changes not made by any precedessors (since the speculatively changes were used by $op$ however these did not get reflected in the actual file system since they were relocated at commit instant).
 Either way contradicts the defenitions and principles (Def 8 and Principle 0).\\
 
-Note: Req 5 suggest if datatype = Definite this causes all the previous operation with Speculative as offsettype to be changed to Defenite.
+%Note: Req 5 suggest if datatype = Definite this causes all the previous operation with Speculative as offsettype to be changed to Defenite.
 
-Def: We define a function $g(offsetstat_1, offsettat_2, ..., offsetstat_{n-1}, operation)$ that takes an input  $n-1$ number of $op.offsetstatus$ plus an operation and gives as the output $n$ number of $op.offsetstatus$.
+%Def: We define a function $g(offsetstat_1, offsettat_2, ..., offsetstat_{n-1}, operation)$ that takes an input  $n-1$ number of $op.offsetstatus$ plus an operation and gives as the output $n$ number of $op.offsetstatus$.
 The $g$ functions provides the requirements mentioned above.
@@
 
-1- if $f(operation) = Absolute$, $g(offsetstat_1, ..., {offsetstat_{n-1}}, operation) = ({offsetstat_1}, ..., {offsetstat_{n-1}}, Absolute)$ leaving all offsetstats intact.\\
+%1- if $f(operation) = Absolute$, $g(offsetstat_1, ..., {offsetstat_{n-1}}, operation) = ({offsetstat_1}, ..., {offsetstat_{n-1}}, Absolute)$ leaving all offsetstats intact.\\
 
-2- if $f(operation) = Defenite$:\\
+%2- if $f(operation) = Defenite$:\\
 
-\hspace{ 8mm}
-	2.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}$\} such that offset = Absolute,  $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ...
+%\hspace{ 8mm}
+%	2.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}$\} such that offset = Absolute,  $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ...
 ,Absolute)$ leaving all offsestats intact.\\
 
-\hspace{ 8mm}
-	2.2- else $\forall offsetstat \in (offsetstat_0, ..., offsetstat_{n-1})$ if offsetstat = Speculative, change its value to Defenite in the output of $g$, plus appending a Defenite to the output (for instane $g(speculative, speculative, read) = (defenite, defeinte, definte)$)\\
+%\hspace{ 8mm}
+%	2.2- else $\forall offsetstat \in (offsetstat_0, ..., offsetstat_{n-1})$ if offsetstat = Speculative, change its value to Defenite in the output of $g$, plus appending a Defenite to the output (for instane $g(speculative, speculative, read) = (defenite, defeinte, definte)$)\\
 
-3- if $f(operation) = Speculative$:\\
+%3- if $f(operation) = Speculative$:\\
 
-\hspace{ 8mm}
-	3.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offset = Absolute, $g(offsetstat_1, ...
+%\hspace{ 8mm}
+%	3.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offset = Absolute, $g(offsetstat_1, ...
 offsetstat_{n-1}, operation) = (offsetstat_1, ...
@@
 
-\hspace{ 8mm}
-	3.2- else if $\exists offsetstat \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offsetstat = {Defenite},  $g(offsetstat_1, ...,  offsetstat_{n-1}, operation) = (offsetstat_1 ,..., offsetstat_{n-1}, Defenite)$\\
+%\hspace{ 8mm}
+%	3.2- else if $\exists offsetstat \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offsetstat = {Defenite},  $g(offsetstat_1, ...,  offsetstat_{n-1}, operation) = (offsetstat_1 ,..., offsetstat_{n-1}, Defenite)$\\
 
-\hspace{ 8mm}
-	3.3- else $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ..., offsetstat_{n-1}, Speculative)$\\
+%\hspace{ 8mm}
+%	3.3- else $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ..., offsetstat_{n-1}, Speculative)$\\
 
-4- After doing the above check if datastatus = Defenite, then change all offsettypes in the input that are Speculative to Defenite in the output.
+%4- After doing the above check if datastatus = Defenite, then change all offsettypes in the input that are Speculative to Defenite in the output.
 
-1, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4. 4 also ensures Req 5.
+%51, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4. 4 also ensures Req 5.
 

### 2008-09-18 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 A Transaction consists of a sequence of operations.
-Thus, a transaction can be represented as the \{$OP_1$, $OP_2$, ..., $OP_n$\}.
+Thus, a transaction can be represented as the \{$op_1$, $op_2$, ..., $op_n$\}.
 The flow of program should be in a manner that we could have an arbitrary serial order of the members of $T$ (e.g.
@@
 The serial order should be in such a way that for any given two members of the set $T$, it looks all the operations of one occur before all the operation of the other.
-In the first case we would say the $T_i$ precedes $T_j$ and in the seconds case $T_j$ preceds $T_i$ and $T_i$ can observe all the effects made by the operations in $T_j$.
+%In the first case we would say the $T_i$ precedes $T_j$ and in the seconds case $T_j$ preceds $T_i$ and $T_i$ can observe all the effects made by the operations in $T_j$.
 \\
@@
 
-Def 1- \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length)\}.
+Def 1- \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), getoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
 We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
-
-%Def 1- 1-An operation in $T_i$ is said to have "changed" or "affected" some data structure in correspondece to all members of $OP_{T- T_i}$ , when it reflects the changes in the filesystem in such a way that the modification is durable and irreversible.
-A transaction with such an operation $T_i$ in its operation set is said to have changed the data 2- An operation in $T_i$ is said to have "changed or affeced the data in correspondence to all the operations in $OP_{T_i}$ as soon as the operation is encountered \\
 
@@
 
-Def 4- \emph{Commit Instant}: A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" mabe by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$ .
+Def 4- \emph{Commit Instant and Commit Operation}: A transaction commits when it invokes the "commit" operation.
+A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" mabe by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$.
+After a transaction invokes commit operation, the transactin ends and no more operation by transaction is done.
 An operation $\in OP_{T_i}$ is said to commit if and only if $T_i$ commits.
@@
 
-Def 5- \emph{No See In Future}: Assume $T_i$ is an uncomiited transaction and $T_{commited}$ indicates the set of commited transaction.
-A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by write operation $b$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
+Def 5- \emph{Precedence Relationship}: If $OP_{executed} = \{op_0, op_1, ..., op_n\}$ represnts the operations executed so far(from all transactions running), and the indices represnt the order of operations executed so far in an ascending manner, we define $op_i \rightarrow op_j$ (precedes) if and only if $i<j$.\\
+
+Def 6- \emph{Visbility of Writes}: Assume $T_i$ is an uncommitted transaction and $T_{commited}$ indicates the set of commited transaction (those which have invoked the "commit" operation).
+A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by precedent write operation $a$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
 
@@
 
-\hspace{7mm} 2- $a \in OP_{T_i}$ and $a$ happens before $b$ in the natural order of the transaction. Formally, $a$ has a lower position than that of $b$ in $OP_{T_i}$ = \{$OP_1$, ..., $OP_n$\} \\
+\hspace{7mm} 2- $a \in OP_{T_i}$ and $a$ happens before $b$ in the natural order of the transaction. Formally, $a \rightarrow b$\\
 
-Def 6- \emph{Precedence Relationship for Read-Write Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, $a$ precedes $b$ ($a \rightarrow b$) if complying with Def 5, $b$ is allowed to see the writes to $r_i$ made by $a$.
-Otherwise, $b \rightarrow a$.
-For other pairs of operations or read-writes that do not share resources $a \rightarrow b$ and $b \rightarrow a$.\\
+Corrolary 1- \emph{No See in The Fututre}: If $ \exists op_i \in WRITEOP_{T_i}$ and $\exists op_j \in READOP{T_j}$ such that $i \neq j$ and $op_i \rightarrow op_j$ then if $op_j \rightarrow commit-operation_{T_i}$, writes made by $op_j$ are not seen by $op_i$.i\\
 
-Corrolary 1- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$, in case $a$ has multiple precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" between all transaction with such operations.
+proof: Follows immediately from Def 5 and Def 6.\\
+
+Corrolary 2- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$ at $t_i$.
+In case $a$ has multiple writer precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" less than $t_i$ between all transaction with such operations .
 Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$.
@@
 
-proof: Consider case 1 that all precedessors are from sets of operations other than that of $a$'s, according to Def 4 all these prcedessors belong to comitted transactions.
-Assume $T_i$ is accessing data at $t_i$, $t_i$ is neccasarily gretaer than all members of \{$committime_{T_1}, ..., commitime_{T_{i-1}}$\},and hence the writes to $r_i$ made by these commited transaction, have accroding to Def 1 been already reflected in the file system.
-Since, $T_{i-1}$ has the greatest commit instant its changes have overriiden that of previously commited transactions and thus, $a$ reading $r_i$ from file system sees these changes.\\
+axiom: Assume $a$ is accessing data at $t_i$, according to Def 6, only writes by those transactions that have already committed would be visble.
+Hence, $t_i$ is neccasarily gretaer than all members of \{$committime_{T_1}, ..., commitime_{T_{i-1}}$\},and hence the writes to $r_i$ made by these commited transaction, have accroding to Def 4 been already reflected in the file system.
+Since, $T_{i-1}$ has the greatest commit instant its changes have overriden that of previously commited transactions and thus, $a$ reading $r_i$ from file system sees these changes.\\
 
-In case 2 that there are operations preceding $a$ in $OP_{T_i}$, according to defenition of transaction $r_i$ should be read from the writes made by write operations in $T_i$, and as the last of such write operation overrides the written data to $r_i$ by other operations, $a$ gets to see the most recent precedessor in $T_i$.\\
-
-%Def 8- \emph{Precedence Relationship for Other Types of Operations}:  Follwoing rules are ONLY enforced if precedence relationship is not detemined between two operations by Def 6.
-1-If $T_i$ and $T_j$ are two transactions both committed with commit instant of $T_j$ being greater than commit instant of $T_i$ then $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
-2-If two operation belong to the same transaction, then the one that occurs earlier in natural order of transaction precedes the other.
-3- If $T_i$ is committed and $T_j$ is not, $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$.
-4- If neither $T_i$ has commited nor $T_j$, then  $\forall op_i \in OP_{T_i}, \forall op_j \in OP_{T_j} op_i \rightarrow op_j$, if there is either not a precedence relationship between $op_i$ and $op_j$ OR it is $op_i \rightarrow op_j$.
-5- Otherwise, it means some operations in $T_i$ precede some of thos in $T_j$ and the other way around, for thos pairs not having such relationship it is assigned arbitrarily.\\
+In case 2 that there are writer operations writng $r_i$ and preceding $a$ in $OP_{T_i}$, according to defenition of transaction, $r_i$ should be read from the writes made by write operations in $T_i$, and as the last of such write operation overrides the written data to $r_i$ by other operations, $a$ gets to see the most recent precedessor in $T_i$.\\
 
@@
 
-Def 8- A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the behavior of the program.\\
+Def 8- \emph{Correctness}: A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
+Behavior for an operation means the data it has read.
+Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence.\\
 
-Corrolary 2: \emph{Upon Commit All Mebers of $T_{commit}$ Should Precede $T_i$}
+Note: Def 7 and Def 8 indicate that if operations can be commuted in a given sequnce of $OP_{executed} = \{op_{T_1}(0), op_{T_4}(0), ...
+op_{T_1}(n)\}$ such that a total ordering of transactions (e.g \{$OP_{T_1}, OP_{T_2}, ..., OP_{T_n}) $\} can be obtained then the execution is consistent and correct.
+The eligiblity to commute is subject to conforming to Corrolary 1 \& 2.\\
 
-proof: Follows imeediately from Def 8 and Def 9. This is later proven formally.i\\
+Def 9- \emph{Relocation Operations in A Sequence}: In a sequence of operations $OP = \{op_1, op_2, ...,op_n\}$, any operation can relocate its position in the sequence unless as a result of this change, the behavior of a read operation changes (it reads different data).\\
 
-%Def 2- An operation in $T_i$ is said to have "used" the data when it has read some data and has done some actions that is potentially irreversible.
-hence if the data in question was to change, $op$ would have different results.
-A transaction with such an operation in its operations set is said to have used that data.
-Any data read and used within a transaction at its commit instant does not count as using.
-"Use" can just be attributed to the operations actually reading data before commit instant.
-\\
+Note: \emph{No Exchange for Operations Belonging to The Same Transaction}: If $op_i \in OP_{T_i}$ and $op_{i+1} \in OP_{T_i}$, we never exchange $op_i$ and $op_{i+1}$, since even if this exchange does not change any operations behavior, there is still no point in doing this as the aim is to put all operations belonging to the same transaction together, the internal order among these is not any of our concern, and the precedence relationship among these as indicated by the execution should be maintained.\\
 
-%Def 4-  $\forall op_i \in OP_{T_i}$, $\forall op_j in OP{T_i}$, $op_i$ precedes $op_j$ if and only if $op_j$ does not use the data changed by $op_i$ OR if it does, then $op_j$ sees the changes made by $op_i$ unless data has been changed by a more recent precedessor.
-Furthermore  \\
+%Def 9- A pair of operations are said to be conflictant if they form a pair of (read, write) or (write, read) acting on the same resource $r_n$.
 
-%Def 5- Succeds relationship is defined similarly.  \\
+%Corrolary 3: \emph{For $T_i$ to Commit All Members of $T_{commit}$ Should Precede $T_i$}
 
-%Def 5- \emph{Precedence Relationship for Operations}: Assume $b$ is a read operation and $a$ is a write operation, and $a$ and $b$ share resource $r_i$, 1- if $b$ see the writes made by the $a$ to $r_i$ and their relationship conforms to Def 4, then $a$ precedes $b$ ($a \rightarrow b$) 2- if $b$ does not see the changes written by $a$, however their relatioship conforms to Def 4,   $r_i$ has been changed by operation $c$ such that $t_{a-commit-instant}<t_{c-commint-instant}$ and $b$ sees the write made by $c$, then $a \rightarrow b$.
-3- If $b$ does not see the changes made by $a$ and $r_i$ has been changed by operation $c$ such that 3- Otherwise $b$ precedes $a$.
-Precedence is only defined for a read and write operation sharing resources.\\
-
-%Def 6- If operation $a$ both precedes and succeds operation $b$ since they do not share any resources so the changes can be made visible, $a$ both precedes and succeds $b$. \\
+%proof: Follows immediately from Def 7 and Def 8. This is later proven formally.\\
 
 \subsection{Rules}
-%If we denote $\rightarrow$ as the relation precedes between operations and $OP_{T_i}$ as the set of all operation within $T_i$ from the set \{BeginTransaction, TransactionaFile.Read, TransactionalFile.Write, EndTransactioni\} we would have: \\
 
-%Rule 1- for any pair of operations (transactions) $a$ and $b$ their relationship is taken from the set \{$\rightarrow$, $\leftarrow$, $\leftarrow$ and $\rightarrow$\} \\
+Rule 1- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if $op_i \rightarrow op_k$ and  $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
 
-%proof: Follows from defenition. \\
+proof: Follows from the defenition of $\rightarrow$ \\
 
-%Rule 2) If an operation $a \in OP{T_i}$ has multiple prcedecors (denoted as $OP_{precedesors}$) that their changes overlap each other, then if all of them are from sets other than $OP{T_i}$, $a$ sees the "changes" made by the $op_i \in OP_{predecesors}$ such that $op_i$ has the greatest "commit instant"  .
-Otherwise, $a$ sees the most recent precedesor in $OP{T_i}$.
-\\
+Rule 2- If $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
 
-%proof: the first part follows from Def 4 , second derives from Def 4 and second part of Def 1.\\
+proof: Follws from Rule 1 and Def 7. \\
 
-%Rule 1- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if there is a precedence relationship between $op_i$ and $op_k$ sand $op_i \rightarrow op_k$, and if there is a relationship between $op_k$ and $op_j$ and $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
+Rule 3- \emph{Exchnaging Position of Consecutive Operations}: Formally having the sequence of operations $OP = \{op_1,...,op_i,op_{i+1},...,op_n\}$, if $op_i \in OP_{T_n}$ and $op_{i+1} \in OP{T_m}$ such that $ n\neq m$, $op_i$ and $op_{i+1}$ can exchange positions if and only if none of the follwing conditions apply:\\
 
-%proof: Follows from the defenition of $\rightarrow$ \\
+\hspace{8mm} 1- If $op_i = {commit}$ and $op_{i+1} = {read}$ and $op_{i+1}$ reads $r_k$, then if there is at least another operation in $T_n$ that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
 
-Rule 1- if $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
+\hspace{8mm} 2- If $op_{i+1} = {commit}$ and $op_{i} = {read}$ and $op_{i}$ reads $r_k$, then if there is at least another operation in $T_m$ that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
 
-proof: Since Def 9 ensures all operations in $OP_{T_i}$ precede those in $OP_{T_j}$. \\
+proof: According to Def 9, none of the operatios in the sequence should change behavior as the result of this exchange, however in this argument only $op_i$ and $op_{i+1}$ may change behavior as those are the only operations that their postions in the sequence is changed.
+However, since behavior is only defined for read operations, one of these without losing generality lets say $op_i$ should be a read operation on agiven resource $r_k$.\\
 
-Rule 2-  \emph{Committed transaction Should Precede the About to Commit Transaction}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denotes the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if all members of $T_{commited}$ precede $T_j$ (hence they should succed)\\
+Now changing the $(op_i, op_{i+1})$ to $(op_{i+1}, op_i)$ changes the behavior of $op_i$ if and inly if $op_{i+1}$ writes $r_k$ at the file system (all the previous precedessors are still the same, only $op{i+1}$ has been added).
+This means by defenition the $op_{i+1}$ should be a commit operation.
+And, if $op_{i+1}$ is a commit operation for $T_m$, and there is at least one write operation in $T_m$ writing to $r_k$, then according to Corrolary 2, $op_i$ should see the most recent results and hence sees these changes.
+These changes could not have been seen in the first case $(op_i, op_{i+1})$ due to Corrolary 1 (No See in The Futture).\\
+
+Rule 4 -\emph{Relocating the Position of an Operation Within the Sequence}: Given a sequence of operations $OP = \{op_1, ..., op_i, op_{i+1}, ..., op_j, op_{j+1}, ..., op_n\}$, $op_j$ can be put into the standing $i<j$ within the sequence (resulting in $OP = \{op_1, ..., op_i,op_j,op_{i+1},..., op_{j+1},...,op_n\}$) if and only if $\forall op \in \{op_{i+1}, ..., op_{j-1}\}$, $op$ and $op_j$ belong to different transactions and the pair $(op_j, op)$ or $(op,op_j)$ is not a pair subject to one of the conditions in Rule 3.
+The same holds true for $i>j$.\\
+
+proof: We use induction to prove if assumptions above hold true $op_j$ can be relocated to $i = j-n$.
+Assume the same $OP$ as before.
+If $n = 1$ then since according to assumption the pair $(op_j, op_{j-1})$ is not subject to the conditions in Rule 3, these two can be easily exchanged.
+Now, lets assume the $op_j$ can be relocated to $j-n-1$, now we prove it for $n$.
+After relocation to $j-n-1$, $op_{i+1}$ immediately precedes $op_j$, as according to assumption and Rule 3 $op_j$ and $op_{i+1}$ can exchange positions.
+After this exchange, $op_j$ has been relocated by $n$ and to $i$ and $op_i$ now immediately precedes $op_j$.\\
+
+The same argument can be used for $i > j$.\\
+
+%proof: If the sequence of operations $OP$ is a consistent one, exchanging the position of $a$ and $b$ does not violate this property as no difference in the bahvior of neither $op_i$ nor $op_{i+1}$ is made.
+If ($op_i, op_{i+1}) is changed to ($op_{i+1}, op_i) they would still both read the same data (if they are reads), since there is no other operation in the middle and Corrolary 2 says the read from $r_n$ reads the most commited write to $r-n$ and as no writes are reflected before the commit operation for that transaction is invoked, and none of these operations is a write, consequently exchanging their positions does not change the data read by them and hence the behavior.\\
+Rule 3-  \emph{Committed transaction Should Precede the About to Commit Transaction}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denoting the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if a sequence preseving the behavior of the program can be found that in it all members of $T_{commited}$ precede $T_j$.\\
 
@@
 
-proof: Follows immediately from Rul2 and Def 7.
+proof: Follows immediately from Rul2 and Def 7.\\
 

### 2008-09-18 Robust/src/IR/TypeDescriptor.java
added a test for immutable

@@ -221,6 +221,10 @@ public class TypeDescriptor extends Descriptor {
     return type==TAG;
   }
 
+  public boolean isImmutable() {
+    return isPrimitive() || isString();
+  }
+
   public TypeDescriptor(NameDescriptor name) {
     super(name.toString());
     this.type=CLASS;

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java
test for immutable instead of primitive to decide if a field cannot create an alias

@@ -347,7 +347,6 @@ public class OwnershipAnalysis {
       OwnershipGraph og = analyzeFlatMethod(d, fm);
       OwnershipGraph ogPrev = mapDescriptorToCompleteOwnershipGraph.get(d);
       if( !og.equals(ogPrev) ) {
-
 	setGraphForDescriptor(d, og);
 
 	// only methods have dependents, tasks cannot
@@ -452,7 +451,8 @@ public class OwnershipAnalysis {
       assert mapFlatNodeToOwnershipGraph.containsKey(frn);
       OwnershipGraph ogr = mapFlatNodeToOwnershipGraph.get(frn);
       completeGraph.merge(ogr);
-    }
+    }   
+
     return completeGraph;
   }
 
@@ -518,7 +518,7 @@ public class OwnershipAnalysis {
       lhs = ffn.getDst();
       rhs = ffn.getSrc();
       fld = ffn.getField();
-      if( !fld.getType().isPrimitive() ) {
+      if( !fld.getType().isImmutable() ) {
 	og.assignTempXEqualToTempYFieldF(lhs, rhs, fld);
       }
       break;
@@ -528,14 +528,16 @@ public class OwnershipAnalysis {
       lhs = fsfn.getDst();
       fld = fsfn.getField();
       rhs = fsfn.getSrc();
-      og.assignTempXFieldFEqualToTempY(lhs, fld, rhs);
+      if( !fld.getType().isImmutable() ) {
+	og.assignTempXFieldFEqualToTempY(lhs, fld, rhs);
+      }
       break;
 
     case FKind.FlatElementNode:
       FlatElementNode fen = (FlatElementNode) fn;
       lhs = fen.getDst();
       rhs = fen.getSrc();
-      if( !lhs.getType().isPrimitive() ) {
+      if( !lhs.getType().isImmutable() ) {
 	og.assignTempXEqualToTempYFieldF(lhs, rhs, fdElement);
       }
       break;
@@ -544,7 +546,7 @@ public class OwnershipAnalysis {
       FlatSetElementNode fsen = (FlatSetElementNode) fn;
       lhs = fsen.getDst();
       rhs = fsen.getSrc();
-      if( !rhs.getType().isPrimitive() ) {
+      if( !rhs.getType().isImmutable() ) {
 	og.assignTempXFieldFEqualToTempY(lhs, fdElement, rhs);
       }
       break;
@@ -552,9 +554,10 @@ public class OwnershipAnalysis {
     case FKind.FlatNew:
[…]

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -1334,9 +1334,10 @@ public class OwnershipGraph {
 
 
     // return value may need to be assigned in caller
-    if( fc.getReturnTemp() != null ) {
+    TempDescriptor returnTemp = fc.getReturnTemp();
+    if( returnTemp != null && !returnTemp.getType().isImmutable() ) {
 
-      LabelNode lnLhsCaller = getLabelNodeFromTemp(fc.getReturnTemp() );
+      LabelNode lnLhsCaller = getLabelNodeFromTemp(returnTemp);
       clearReferenceEdgesFrom(lnLhsCaller, null, true);
 
       LabelNode lnReturnCallee = ogCallee.getLabelNodeFromTemp(tdReturn);

### 2008-09-18 Robust/src/Tests/OwnershipAnalysisTest/test01/test01.java

@@ -44,7 +44,8 @@ public class Voo {
 public class Baw {
   int y;
   Foo f;
-  
+  String s;
+
   public Baw() {}
   
   public void doTheBaw( Voo v ) { v = new Voo(); }
@@ -391,6 +392,23 @@ task showPrunedEdgesInMethodCall( Foo a{ f } ) {
   c.f.b = new Baw();
   
   Zool.FooToBaw( c, b );
+
+  taskexit( a{ !f } );
+}
+
+task showStringIsImmutable( Foo a{ f } ) {
+
+  Baw x = new Baw();
+  Baw y = new Baw();
+
+  Foo f = new Foo();
+  String s = new String();
+
+  x.f = f;
+  y.f = f;
+
+  x.s = s;
+  y.s = s;
 
   taskexit( a{ !f } );
 }

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/AllocationSite.java
exhaustive arity improves for benchmarks with ad=1

@@ -41,7 +41,7 @@ public class AllocationSite {
 
 
   public AllocationSite(int allocationDepth, TypeDescriptor type) {
-    assert allocationDepth >= 2;
+    assert allocationDepth >= 1;
 
     this.allocationDepth = allocationDepth;
     this.type            = type;

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -1011,7 +1011,7 @@ public class OwnershipGraph {
       Iterator<ReferenceEdge> edgeItr = argLabel_i.iteratorToReferencees();
       while( edgeItr.hasNext() ) {
 	ReferenceEdge edge = edgeItr.next();
-	D_i = D_i.union(edge.getBeta() );
+	D_i = D_i.union(edge.getBeta());
       }
 
       D_i = D_i.exhaustiveArityCombinations();

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/ReachabilitySet.java

@@ -46,6 +46,11 @@ public class ReachabilitySet extends Canonical {
     return possibleReachabilities.iterator();
   }
 
+  
+  public int size() {
+    return possibleReachabilities.size();
+  }
+
 
   public boolean contains(TokenTupleSet tts) {
     assert tts != null;
@@ -256,7 +261,8 @@ public class ReachabilitySet extends Canonical {
     int numDimensions = this.possibleReachabilities.size();
 
     if( numDimensions > 10 ) {
-      System.out.println( "exhaustiveArityCombinations numDimensions = "+numDimensions );
+      System.out.println( "    exhaustiveArityCombinations numDimensions = "+numDimensions );
+      System.out.println( this );
     }
 
     // add an extra digit to detect termination
@@ -291,15 +297,15 @@ public class ReachabilitySet extends Canonical {
 
 
 	if( i == 11 ) {
-	  System.out.print( "x " );
+	  System.out.print( "x" );
 	}
 
 	if( i == 15 ) {
-	  System.out.print( "@ " );
+	  System.out.print( "@" );
 	}
 
 	if( i == 17 ) {
-	  System.out.print( "# " );
+	  System.out.print( "#" );
 	}
 
 	if( digits[i] > maxArity ) {
@@ -311,6 +317,10 @@ public class ReachabilitySet extends Canonical {
 	  break;
 	}
       }
+    }
+
+    if( numDimensions > 10 ) {
+      System.out.println( "" );
     }
 
     return rsOut.makeCanonical();

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/AllocationSite.java
pull in class files that already exist in library

@@ -27,7 +27,7 @@ public class AllocationSite {
   protected int allocationDepth;
   protected Vector<Integer> ithOldest;
   protected Integer summary;
-  protected TypeDescriptor type;
+  protected FlatNew flatNew;
 
   public static final int AGE_notInThisSite = 100;
   public static final int AGE_in_I          = 101;
@@ -40,11 +40,11 @@ public class AllocationSite {
   public static final int SHADOWAGE_summary       = -103;
 
 
-  public AllocationSite(int allocationDepth, TypeDescriptor type) {
+  public AllocationSite(int allocationDepth, FlatNew flatNew) {
     assert allocationDepth >= 1;
 
     this.allocationDepth = allocationDepth;
-    this.type            = type;
+    this.flatNew         = flatNew;
 
     ithOldest = new Vector<Integer>(allocationDepth);
     id        = generateUniqueAllocationSiteID();
@@ -103,8 +103,12 @@ public class AllocationSite {
     return -summary;
   }
 
+  public FlatNew getFlatNew() {
+    return flatNew;
+  }
+
   public TypeDescriptor getType() {
-    return type;
+    return flatNew.getType();
   }
 
   public int getAgeCategory(Integer id) {
@@ -169,6 +173,6 @@ public class AllocationSite {
   }
 
   public String toStringVerbose() {
-    return "allocSite" + id + " "+type.toPrettyString();
+    return "allocSite" + id + " "+flatNew.getType().toPrettyString();
   }
 }

### 2008-09-18 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java

@@ -106,7 +106,7 @@ public class OwnershipAnalysis {
 	  AllocationSite as = (AllocationSite) allocItr.next();
 	  if( createsPotentialAliases(td, i, as) ) {
 	    foundSomeAlias = true;
-	    bw.write("Potential alias between parameter "+i+" and "+as+".\n");
+	    bw.write("Potential alias between parameter "+i+" and "+as.getFlatNew()+".\n");
 	  }
 	}
       }
@@ -126,7 +126,7 @@ public class OwnershipAnalysis {
 	  if( !outerChecked.contains(as2) &&
 	      createsPotentialAliases(td, as1, as2) ) {
 	    foundSomeAlias = true;
-	    bw.write("Potential alias between "+as1+" and "+as2+".\n");
+	    bw.write("Potential alias between "+as1.getFlatNew()+" and "+as2.getFlatNew()+".\n");
 	  }
 	}
 
@@ -686,7 +686,7 @@ public class OwnershipAnalysis {
   private AllocationSite getAllocationSiteFromFlatNewPRIVATE(FlatNew fn) {
 
     if( !mapFlatNewToAllocationSite.containsKey(fn) ) {
-      AllocationSite as = new AllocationSite(allocationDepth, fn.getType() );
+      AllocationSite as = new AllocationSite(allocationDepth, fn );
 
       // the newest nodes are single objects
       for( int i = 0; i < allocationDepth; ++i ) {

### 2008-09-18 Robust/src/Main/Main.java

@@ -174,6 +174,12 @@ public class Main {
     readSourceFile(state, ClassLibraryPrefix+"gnu/Random.java");
     readSourceFile(state, ClassLibraryPrefix+"Vector.java");
     readSourceFile(state, ClassLibraryPrefix+"Enumeration.java");
+    readSourceFile(state, ClassLibraryPrefix+"Dictionary.java");
+    readSourceFile(state, ClassLibraryPrefix+"Writer.java");
+    readSourceFile(state, ClassLibraryPrefix+"BufferedWriter.java");
+    readSourceFile(state, ClassLibraryPrefix+"OutputStreamWriter.java");
+    readSourceFile(state, ClassLibraryPrefix+"FileWriter.java");
+    readSourceFile(state, ClassLibraryPrefix+"Date.java");
 
     if (state.TASK) {
       readSourceFile(state, ClassLibraryPrefix+"Object.java");

### 2008-09-19 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-Def 1- \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), getoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
+\textbf{Def 1-} \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), getoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
 We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
 
-Def 2- \emph{Operations Sharing Resources} 1- A readoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
+\textbf{Def 2-} \emph{Operations Sharing Resources} 1- A readoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
 2- A readdata and writedata operations are said to be sharing resources if they both operate on the same inode AND the range of (offset, offset + length) within one overlaps with that of the other.\\
 
-Def 3- A read operation can only see the writes made by write operations sharing reources.\\
+\textbf{Def 3-} A read operation can only see the writes made by write operations sharing reources.\\
 
-Def 4- \emph{Commit Instant and Commit Operation}: A transaction commits when it invokes the "commit" operation.
+\textbf{Def 4-} \emph{Commit Instant and Commit Operation}: A transaction commits when it invokes the "commit" operation.
 A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" mabe by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$.
@@
 
-Def 5- \emph{Precedence Relationship}: If $OP_{executed} = \{op_0, op_1, ..., op_n\}$ represnts the operations executed so far(from all transactions running), and the indices represnt the order of operations executed so far in an ascending manner, we define $op_i \rightarrow op_j$ (precedes) if and only if $i<j$.\\
+\textbf{Def 5-} \emph{Precedence Relationship}: If $OP_{executed} = \{op_0, op_1, ..., op_n\}$ represnts the operations executed so far(from all transactions running), and the indices represnt the order of operations executed so far in an ascending manner, we define $op_i \rightarrow op_j$ (precedes) if and only if $i<j$.\\
 
-Def 6- \emph{Visbility of Writes}: Assume $T_i$ is an uncommitted transaction and $T_{commited}$ indicates the set of commited transaction (those which have invoked the "commit" operation).
+\textbf{Def 6-} \emph{Visbility of Writes}: Assume $T_i$ is an uncommitted transaction and $T_{commited}$ indicates the set of commited transaction (those which have invoked the "commit" operation).
 A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by precedent write operation $a$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
@@
 
-Corrolary 1- \emph{No See in The Fututre}: If $ \exists op_i \in WRITEOP_{T_i}$ and $\exists op_j \in READOP{T_j}$ such that $i \neq j$ and $op_i \rightarrow op_j$ then if $op_j \rightarrow commit-operation_{T_i}$, writes made by $op_j$ are not seen by $op_i$.i\\
+\textbf{Corrolary 1-} \emph{No See in The Fututre}: If $ \exists op_i \in WRITEOP_{T_i}$ and $\exists op_j \in READOP{T_j}$ such that $i \neq j$ and $op_i \rightarrow op_j$ then if $op_j \rightarrow commit-operation_{T_i}$, writes made by $op_j$ are not seen by $op_i$.i\\
 
@@
 
-Corrolary 2- \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$ at $t_i$.
+\textbf{Corrolary 2-} \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$ at $t_i$.
 In case $a$ has multiple writer precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" less than $t_i$ between all transaction with such operations .
@@
 
-Def 7- $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+\textbf{Def 7-} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
 
-Def 8- \emph{Correctness}: A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
+\textbf{Def 8-} \emph{Correctness}: A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
 Behavior for an operation means the data it has read.
@@
 
-Note: Def 7 and Def 8 indicate that if operations can be commuted in a given sequnce of $OP_{executed} = \{op_{T_1}(0), op_{T_4}(0), ...
+\textbf{Note 1:} Def 7 and Def 8 indicate that if operations can be commuted in a given sequnce of $OP_{executed} = \{op_{T_1}(0), op_{T_4}(0), ...
 op_{T_1}(n)\}$ such that a total ordering of transactions (e.g \{$OP_{T_1}, OP_{T_2}, ..., OP_{T_n}) $\} can be obtained then the execution is consistent and correct.
@@
 
-Def 9- \emph{Relocation Operations in A Sequence}: In a sequence of operations $OP = \{op_1, op_2, ...,op_n\}$, any operation can relocate its position in the sequence unless as a result of this change, the behavior of a read operation changes (it reads different data).\\
+\textbf{Def 9-} \emph{Relocation Operations in A Sequence}: In a sequence of operations $OP = \{op_1, op_2, ...,op_n\}$, any operation can relocate its position in the sequence unless as a result of this change, the behavior of a read operation changes (it reads different data).\\
 
-Note: \emph{No Exchange for Operations Belonging to The Same Transaction}: If $op_i \in OP_{T_i}$ and $op_{i+1} \in OP_{T_i}$, we never exchange $op_i$ and $op_{i+1}$, since even if this exchange does not change any operations behavior, there is still no point in doing this as the aim is to put all operations belonging to the same transaction together, the internal order among these is not any of our concern, and the precedence relationship among these as indicated by the execution should be maintained.\\
+\textbf{Note 2:} \emph{No Commute for Operations Belonging to The Same Transaction}: If $op_i \in OP_{T_i}$ and $op_{i+1} \in OP_{T_i}$, we never commute $op_i$ and $op_{i+1}$, since even if this exchange does not change any operations behavior, there is still no point in doing this as the aim is to put all operations belonging to the same transaction together, the internal order among these is not any of our concern, and the precedence relationship among these as indicated by the execution should be maintained.\\
+
+\textbf{Note 3:} \emph{Precedence Relationship Between Commit Operations Should Be Preserved}: As a rquirement we want to have the notion that transaction are executed in the serial order imposed by their commit operations.
+Hence, commit operations can not be commuted.\\
+
+All the rules explained later are based on the assumptions made in Note 2 \& 3, hence these two types of commution are ruled out by default.\\
 
@@
 
-Rule 1- $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if $op_i \rightarrow op_k$ and  $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
+\textbf{Rule 1-} $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if $op_i \rightarrow op_k$ and  $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
 
@@
 
-Rule 2- If $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
+\textbf{Rule 2-} If $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
 
@@
 
-Rule 3- \emph{Exchnaging Position of Consecutive Operations}: Formally having the sequence of operations $OP = \{op_1,...,op_i,op_{i+1},...,op_n\}$, if $op_i \in OP_{T_n}$ and $op_{i+1} \in OP{T_m}$ such that $ n\neq m$, $op_i$ and $op_{i+1}$ can exchange positions if and only if none of the follwing conditions apply:\\
+\textbf{Rule 3-} \emph{Exchnaging Position of Consecutive Operations}: Formally having the sequence of operations $OP = \{op_1,...,op_i,op_{i+1},...,op_n\}$, if $op_i \in OP_{T_n}$ and $op_{i+1} \in OP{T_m}$ such that $ n\neq m$, $op_i$ and $op_{i+1}$ can exchange positions if and only if none of the follwing conditions apply:\\
 
-\hspace{8mm} 1- If $op_i = {commit}$ and $op_{i+1} = {read}$ and $op_{i+1}$ reads $r_k$, then if there is at least another operation in $T_n$ that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
+\hspace{8mm} 1- If $op_i = {commit}$ and $op_{i+1} = {read}$ and $op_{i+1}$ reads $r_k$, and $\not \exists op_k$ in $OP_{T_m}$ such that writes to $r_k$, and if there  $exists op_l \in OP_{T_n}$ such that writes the data $r_k$, then $op_i$ and $op_{i+1}$ can not exchange positions.\\
 
-\hspace{8mm} 2- If $op_{i+1} = {commit}$ and $op_{i} = {read}$ and $op_{i}$ reads $r_k$, then if there is at least another operation in $T_m$ that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
+\hspace{8mm} 2- If $op_{i+1} = {commit}$ and $op_{i} = {read}$ and $op_{i}$ reads $r_k$ and $\not \exists op_k$ in $OP_{T_n}$ such that writes to $r_k$, and if there $exists op_l \in OP_{T_m}$ such that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
 
@@
 
-Now changing the $(op_i, op_{i+1})$ to $(op_{i+1}, op_i)$ changes the behavior of $op_i$ if and inly if $op_{i+1}$ writes $r_k$ at the file system (all the previous precedessors are still the same, only $op{i+1}$ has been added).
+Now changing the $(op_i, op_{i+1})$ to $(op_{i+1}, op_i)$ changes the behavior of $op_i$ if and only if $op_{i+1}$ writes $r_k$ at the file system (all the previous precedessors are still the same, only $op{i+1}$ has been added).
 This means by defenition the $op_{i+1}$ should be a commit operation.
-And, if $op_{i+1}$ is a commit operation for $T_m$, and there is at least one write operation in $T_m$ writing to $r_k$, then according to Corrolary 2, $op_i$ should see the most recent results and hence sees these changes.
-These changes could not have been seen in the first case $(op_i, op_{i+1})$ due to Corrolary 1 (No See in The Futture).\\
+And, if $op_{i+1}$ is a commit operation for $T_m$, and there is at least one write operation in $T_m$ writing to $r_k$, then according to Corrolary $op_i$ should see the most recent results and hence if there is no precedessor for $op_i$ in $T_n$ itself that writes to $r_k$, then $op_i$ sees the changes made by the write operarion in $T_m$.
+These changes could not have been seen in the first case $(op_i, op_{i+1})$ due to Corrolary 1 (No See in The Future).\\
 
-Rule 4 -\emph{Relocating the Position of an Operation Within the Sequence}: Given a sequence of operations $OP = \{op_1, ..., op_i, op_{i+1}, ..., op_j, op_{j+1}, ..., op_n\}$, $op_j$ can be put into the standing $i<j$ within the sequence (resulting in $OP = \{op_1, ..., op_i,op_j,op_{i+1},..., op_{j+1},...,op_n\}$) if and only if $\forall op \in \{op_{i+1}, ..., op_{j-1}\}$, $op$ and $op_j$ belong to different transactions and the pair $(op_j, op)$ or $(op,op_j)$ is not a pair subject to one of the conditions in Rule 3.
+\textbf{Rule 4} -\emph{Relocating the Position of an Operation Within the Sequence}: Given a sequence of operations $OP = \{op_1, ..., op_i, op_{i+1}, ..., op_j, op_{j+1}, ..., op_n\}$, $op_j$ can be put into the standing $i<j$ within the sequence (resulting in $OP = \{op_1, ..., op_i,op_j,op_{i+1},..., op_{j+1},...,op_n\}$) if and only if $\forall op \in \{op_{i+1}, ..., op_{j-1}\}$, $op$ and $op_j$ belong to different transactions and the pair $(op_j, op)$ or $(op,op_j)$ is not a pair subject to one of the conditions in Rule 3.
 The same holds true for $i>j$.\\
@@
 
-The same argument can be used for $i > j$.\\
+Now we prove the other side of the argument, that if $op_j$ can be relocated in $i$, $\forall op \in \{op_{i+1}, ..., op{j-1}\}, (op_j, op)$ is not a pair subject to the condition in Rule 3.
+Lets assume there is $op$ in $T_i$ such that $(op, op_{j})$ is a $({read r_n}, {commit})$  and the commit invlolves making a write in $T_j$ to $r_n$ durable and a precedessor writer that writes to $r_n$ does not exists for $op$ in $OP_{T_i}$ , now if $op_j$ is relocated to position $i$, $op_j$ would precede $op$ and hence $op$ would see the writes by the operation in $T_j$ (defenition of commit Def 4 \& Corrolary  2) and hence the behavior of $op$ would change as it does not read the same data as before (the data read before could not have been the same thing due to Corrolary 1).
+If the pair of $(op, op_j)$ is $({commit}, {read r_n})$ the same reasoning would do.\\
 
-%proof: If the sequence of operations $OP$ is a consistent one, exchanging the position of $a$ and $b$ does not violate this property as no difference in the bahvior of neither $op_i$ nor $op_{i+1}$ is made.
-If ($op_i, op_{i+1}) is changed to ($op_{i+1}, op_i) they would still both read the same data (if they are reads), since there is no other operation in the middle and Corrolary 2 says the read from $r_n$ reads the most commited write to $r-n$ and as no writes are reflected before the commit operation for that transaction is invoked, and none of these operations is a write, consequently exchanging their positions does not change the data read by them and hence the behavior.\\
-Rule 3-  \emph{Committed transaction Should Precede the About to Commit Transaction}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denoting the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if a sequence preseving the behavior of the program can be found that in it all members of $T_{commited}$ precede $T_j$.\\
+The whole argument can be used to prove the Rule for $i > j$ as well.\\
 
-proof: $T_i$ denotes the last commited member of $T_{commited}$. Lets assume on the contrary $T_i$ does not precede $T_j$ and hence $T_j \rightarrow T_i$.\\
+\textbf{Rule 5-}\emph{Operation in the Set of Execeuted Operations Belongin to Committed Transactions Should Be Able To Precede Those in The Transaction About to Commit}: $OP_{executed} = \{op_1,..., op_n\}$ represents the set of executed operations before instant $t_j$ and $T_{committed}$ represents the set of committed transactions committed successfully before $t_j$.
+If $T_j$ invokes ${commit}$ operation at instant $t_j$ - then $T_j$ commits at instant $t_j$ if and only if operations in $OP$ can be commuted in a way such that $\forall op_i \in OP_{T{committed}}$, $\forall op_j \in OP_{T_j}$, $op_i \rightarrow op_j$.\\
 
-If there is not a pair of (read, write) or (write, read), sharing resource $r_n$ in the two transaction, then $T_i \rightarrow T_j$ according to Def 7 and Def 9.\\
+proof: If all those operations can be commuted tp precede those in $T_j$ we could have $OP_{executed} = \{op_1,...,OP{T_j}\}$.
+This by defenition of transaction means $T_j$ can commit (it is executed in its whole entierty).\\
 
-If there are such operations, 1-At least an operation $a$ reads from $r_n$ in $OP_i$ sees the writes made by a write operation on $r_n$($b$) in $OP_j$, however since $T_j$ has commited after $T_i$ and writes are not reflected till commit instant, hence $a$ could not have read the writes made by $b$ and consequently $a$ does not precede $b$ contradicting the assumption $T_j \rightarrow T_i$ .
-OR 2- An operation $a$ in $T_i$ writes to resource $r_i$ and operation $b$ in $T_j$ reads resource $r_i$, according to Def 5 $a$ precedes $b$ and $b$ does not precede $a$, hence contradicting the assumption that $T_j \rightarrow T_i$.\\
-
-The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
-Now according to rule 3, since $T_{i-1}$ precedes $T_i$ and $T_i$ precedes $T_{j}$, hence $T_{i-1}$ precedes $T_{j}$.
-Same reasoning is applied for all the members of $T_{commited}$.
-\\
-
-%If an operation $op_{i_1}$ in $OP_i$, writes some data used by an operation $op_{j_i}$ in $OP_j$, then $op_{j_1}$ can not precede $op_{i_1}$ since then it could not have seen the changes by it, however def 3 says it does, this is in contrats to the assumption.
-On the other hand, if $op_{j_1}$ affects some data used by $op{i_1}$, then since $op{i_1}$ has not seen the change, $op{j_1}$ can not precede $op{i_1}$.
-If no operations in $OP_i$ affects another in $OP_j$, then the set of all opeartions in $OP_i$ both precede and succed those in $OP_j$, and hence the contraray to the assumption.
-In this case, the transaction are conceptually interchangable.
-In either case, $T_j$ either "succeds" or "succeds and precedes" $T_i$.
-Either way it succeds the other.
-\\
-
-Rule 3-\emph{Operation in the Committed Transactions Precede Those in The Transaction About to Commit}: $T_j$ "commits" at instant $t_j$ - $T_{commited}$ denoting the set of all commited transactions at $t_i$ such that $t_j > t_i$- only if $\forall op_i \in OP_{T_i}$, $\forall op_{all} \in$ the union of $OP_j$, such that $OP_j$ is the set of operations  for every $T_j \in T_{commited}$, $op_{all}$  should precede $op_{i}$.\\
-
-proof: Follows immediately from Rul2 and Def 7.\\
-
-Rule 4- \emph{If All committed Transactions Precede A Transaction About to Commit, It Commits}: $T_i$ commits if at its commit instant, $\forall T_j \in T_ccommitted T_j \rightarrow T_i$.
-
-proof: If $\forall T_j \in T_committed T_j \rightarrow T_i$, a total ordering can be established corresponding the precedence relationship and all writes made by committed transaction have been seen by reads in $T_i$, hence according to Def 8, a consistent sequence of transactions would be provided.
+Now we have to prove $T_j$ commits only if $\forall T_i \in T_{committed} T_i \rightarrow T_j$.
+Now we'll show that if all committed operations can not precede operation of $T_j$ the $T_j$ can not commit.
+$OP = \{op_{T_j}(1), ..., op{T_j}(m)} represent the operations in $T_j$ excluding the ${commit}$ in the order they have occured in $OP_{executed}$.
+Assume \{op_{T_j}(k),...op{T_j}(m)\} can be relocated in $OP_{executed}$ in the standing \{n-(m-k), ...,n-1) but op_{T_j}(k-1) can not.
+This means first of all op_{T_j}(k-1) is a ${read}$ operation reading $r_n$(each transaction has only one ${commit$} operation).
+Furthermore, this implies there is a ${commit}$ operation by some transactione $T_i$ between $op{T_j}(k-1)$ and commit operation by $T_j$ and $ \exists op in OP{T_i}$ such that writes $r_n$ and $\not \exists op_i \in OP{T_j}$ such that $op_i \rightarrow op_{T_i}(k-1)$.
+On the other hand since there is a ${commit}$ by $T_i$ in the middle, the commit by $T_J$ can not be commuted in a way so $OP$ precedes it without any operation belonging to other transaction in the middle (two ${commits}$ can not commute).
+Hence we can not have a sequence where all operations belonging to $T_j$ are located next to each other, this contradicts the defenition of transaction, hence the transaction can not commit.
 

### 2008-09-23 Robust/Transactions/Notes/draft.tex
*** empty log message ***

\documentclass[a4paper, 11pt]{article}
\usepackage[pdftex]{graphicx}
\begin{document}
\section{Correctness}

{Correctness}: A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program. Behavior for an operation means the data it has read or wants to write. Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence. However writs always writes the same value no matter what. Hence the behavior of a write operation is not alterable.\\

\textbf{Def 1-} \emph{Set of Primitve Operations}: Operations are taken from the set \{forcereadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.\\

\textbf{Def 2-} \emph{Set of User-Level Operations}: User-Level Operations are taken from the set \{Read(fildescriptor), GetFilePointer(filedescriptor), Write(filedescriptor), Seek(filedescriptor), EndTransaction\}.\\

\textbf{Note 1-} \emph{Assignment Operations Need Not Be Shown In $OP_{excecuted}$}: Operations like offset = offset + length and other assignment operations in $OP_{T_i}$ need not be shown in the actual sequence of operations namely $OP_{executed}$ that consists of operations executed by different transaction so far, the reason is simply all such operations are local to the transaction and do not affect any other transaction's state and hence do not restrict the commution of other operations in any manner.\\

\textbf{Note 2} \emph{ForcedReadOffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\

\section{FileDescriptor Offset State per Transaction}:

Each filedescriptor has an assosiated offset with it, within each transaction this offset can be in 4 different states, these states indicate the dependency the transaction has on the value of this offset:\\

1- \textbf{No Access}: This is the default state for all filedescriptors in a transaction and is changed as soon as there is an acsess to the the descriptor within the transaction (any of the use-level operations are invoked).\\

2- \textbf{None}: Meaning there is no dependency for any operation in this transaction on the value of the offset assosiated with this descriptor regarding other transactions.\\ %This stems from the fact that the offset has been assigned an absolute value in this transaction and no operation reads on the value the offset had before this transaction accessed it.\\

3- \textbf{Write Dependency}: This kind of dependency means there is at least one operation in $OP_{T_i}$ having an unknown offset(essentially a write operation) value as argument. The value of this unknown offset will be determined at commit instant. \\

4- \textbf{Read Dependency}: This kind of dependency means there is at least one operation acting on an offset value for fd, where the value for fd has been determined by a previously commited transaction.\\

The state machine below depicts the behavior of the user level operations regarding how the offset corresponding to that transaction changes: \\

\includegraphics[scale = 0.3]{hello.png}\\

\textbf{Explanation}: Whenever the offset status for the transaction goes to "Read Dependence", a "forcedreadoffset(fd)" operation is issued immdeiately preceding the operation that caused this transformation. The forced-radoofset(fd) is only issued if there is not a forcedofset(fd) in the $OP_{T_i}$ already.\\

\textbf{Axiom For Diagram:} If the first access to a filedescriptor is a $Seek(fd)$, then the following operation on $fd$ gets the offset value from the assignment made by the $Seek(fd)$ and adavances the offset. Hence, the follwoing operations get this offset and the offset value the filedescriptor had had before this transaction accesses fd is never refrenced (thats why it is an absorbing state). This conforms to the defnition of "None" state.\\

If $Read(fd.inode, offset, length)$ or $GetFilePointer(fd)$ is the first access made by this transaction, the offset is read (since the data needs to be read at this instant), this offset should be the one committed by a previously committed transaction (as this is the first access to $fd$ in this transaction). Once the offset is read, it is always dependent on this value (hence an absorbing state). For all the following operations, the offset value is known. This conforms to the defenition that there is at least (the first read ever on fd by this transaction) one operation that acts on the offset value for fd and rules out the "Write Dependency" and "None" states.\\

If $Write(fd.inode, offset, length)$ is the first access made to fd by this transaction, then the offset to write to, can be decided at commit instant since the Write functions means start writing at the most recent committed fd.offset, hence offset realization can be postponed till commit instant. Any Writes or Seeks would still leave this dpendency, since operations after a Seek act on absoulte offset, and Writes preceding any Seek can all determine the offset at commit instant for the same reason as before.\\

However, if a Read on the same fd in the transaction is invoked there are two possiblities:\\

1- A Seek precedes this Read, hence the offset value is absolute and is not read, however the ranges that are supposed to be written by Writes preceding the Seek, may overlap with the range Read is willing to Read from, and according to Rules(Most Recent Changes Should Be Visible) if thats the case the Read should be able to see this data, this suggests the ranges that all the Writes are going to write to should be realized now and this requires settling down on a value for all file descriptors offsets for this inode at this instant. Based on these, the most recent commited offset value for all these descriptors should be assigned to the offsets for the Writes that for the first time accessed the descriptor. Other for writes prceding the Seek, get this value as being advance by prior writes.\\

2- No Seek precedes the Read, hence the offset value the Read has to read from is unknown, since preceding Writes to fd have all used unknown offsets, the offset value given to Read is an unknown once, however it has to be known, follwos that the offset value for the Write that for the first time accessed this fd should be decided upon and as shown before, the value should be the most recent commited offset value for fd. The offset value for this read or other writes, is the offset value obtained as being advamced by those operations.\\

The two same possiblities exist when a GetFilePointer operation is invoked on the same fd:\\

1- If a Seek precedes it, then the offset value becomes absolute and hence the getFilePointer could retreive the value assigned by Seek.\\

2- Otherwise, the offset value is still unknown, hence to be able to determine the offset value at this instant, the value obtained by reading the last commited offset value should be assigned to the offset value. for the first Write to $fd$.\\

%\textbf{Def 2-} \emph{Read and Write Operation}: 1- A Readdata is always a read operation. 2- ${readoffset(fd})\in OP_{T_i}$ is only a read operation, if it precedes a ${forceoffset(fd)} \in OP_{T_i}$. The reason is even though readoffset reads the offset, but the value does not matter unless specefied by ${forceoffset }$. 3- ${writeoffset}$ and ${writedata}$ are write operations.\\

%\textbf{Note 1-}: The runtime determines if and only if this is the first time the fd has been accessed by this transaction, then a $\{{offset} = {readoffset(fd)}\}$ is inserted in the sequence of operations. This ensures the offset is read for each filedescriptor once, and thats the first time it is accessed.\\

\section{User-Level Operations Structure}

The user-level operation cab be broken as follows:\\

1- Seek(fd): This operation sets the offset for filedescriptor. We define it as demonstarted below:\\

\hspace{8mm} Just an internal assignment in the transaction, $\{{fd.offset = value}\}$.\\

2- Write(fd):\\

\hspace{8mm} 1- $\{writedata(fd.inode, offset, length), fd.offset = fd.offset + length\}$\\

3- GetFilePointer(fd):\\

\hspace{8mm} \{\{$forcedreadoffset(fd)$ issued as demonstrated at the state diagram if any, it is issued when the state for fd in this transaction is not in "No Dependeny" or "Write Dependency 2"\}\}\\

4- Read(fd):\\

\hspace{8mm} $\forall filedescriptor fd_i$ where $fd_i.inode = fd.inode$ and the state for $fd_i$ in this transaction is not $No Dependency$, Read(fd) =$\{\{forcedreadoffset(fd_i)\}\}, {readdata(fd.inode, offset, length)}, offset = offset + length\}$\\

%\hspace{8mm}  1-  If ${read(fd)} \in OP_{T_i}$ and  $\exists forceoffset(fd) \in OP_{T_i}$ such that $forceoffset(fd) \rightarrow read(fd)$, then:\\

%\hspace{16mm} $\{{read(fd)}=readdata(fd.inode, offset, lenght), fd.offset = fd.offset + length\} $\\

%\hspace{8mm}  2-  If ${read(fd)} \in OP_{T_i}$ and  $ \not \exists forceoffset(fd) \in OP_{T_i}$ such that $forceoffset(fd) \rightarrow read(fd)$, then:\\

%\hspace{16mm} 1- If $\exists Seek(fd) \in USEROP_{T_i}$ such that $Seek(fd) \rightarrow read(fd)$ then:\\

%\hspace{16mm} $\forall fd_i \in filedescriptors-accessed-by-T_i$ if $\exists writedata(fd_i.inode, offset, length)$ where $fd_i.inode = fd.inode$ and ${write(fd_i, offset, lenght)} \rightarrow {read(fd)}$  and $\not \exists seek(fd_i)$ such that $seek(fd_i) \rightarrow write(fd_i)$ and $\not \exists forceoffset(fd_i)$ such that $forceoffset(fd_i) \rightarrow read(fd)$ then ${read(fd)} = \{ \{forceoffset(fd_i)\},readdata(fd.inode, offset, length), fd.offset = fd.offset + length\}$ \\

%\hspace{16mm} 2- Else:\\ $\forall fd_i \in filedescriptors-accessed-by-T_i$ excluding $fd$ itself, if $ \exists writedata(fd_i.inode, offset, length)$ where ${write(fd_i, offset, lenght)} \rightarrow {read(fd)}$  and $\not \exists seek(fd_i)$ such that $seek(fd_i) \rightarrow write(fd_i)$ and $\not \exists forceoffset(fd_i)$ such that $forceoffset(fd_i) \rightarrow read(fd)$ then ${read(fd)} = \{ \{forceoffset(fd_i)\},readdata(fd.inode, offset, length), fd.offset = fd.offset + length\}$ \\

5- EndTransaction:

\hspace{8mm} $\forall fd_i$ such that the state for $fd_i$ in this transaction is  not "No State",  $EndTransaction= \{\{{writeoffset(fd_i)}\}, commit\}$\\

Essentially for any fd that the correspondent state digaram in the transactions shows is in a state other than "No Access", a writeoffset(fd) is issued while committing.\\

\section{FileDescriptor Offset State per writedata Operation}

Any writedata operation within a transaction gets $fd$ and an offset as arguments. There writes are reflected in the commit instant, howeverthe offset to write to as we saw earlier for some writes i sdetermined at commit instant and for other is bound to a specefic value bfore commit instant. We should have a policy to be able to diffrenciate between these two. The 3 rules below odes this.\\

1- If the state for $fd$ a given FileDescriptor in a transaction is "Write Dependency 1" all writes by that transaction to that $fd$ will get the value of the offset to write to at commit instant (since in "Write Dependency 1" all writes are at unknown offsets) .\\\

2- If the state for $fd$ is "Read Dependency"  or "No Dependency" then all writes on $fd$ within this transaction should be done at offset detrmined for them when they were invoked (since all writes are to known offsets either determined by the transaction itself or a previously committed transaction).\\

3- Otherwise, if the state is "Write Dependency 2", then if the $writedata(fd.inode,...)$ operation precedes a $Seek(fd)$ then the offset is determined at commit instant (since all such writes are at unknown offset). Otherise, the writes shold be done at the offset decided upon earlier (the write after a Seek write the iffset detrmined by Seek and hence to a known offset).\\

We could also think of this as a state machine for each writedata operation. The state diagram is created for each operation when it is first invoked and is subject to two things:\\

1- If there $\exists Seek(fd) or forced-readoffset(fd)\in OP_{T_i}$ such that those precede the $writedata(fd.inode,....)$ then the initial state in the state diagram for this writedata is Absolute.\\

2- Otherwise the initial state is Unknown offsset.\\

\includegraphics[scale = 0.3]{hello2.png}\\

\end{document}

### 2008-09-23 Robust/Transactions/Notes/draft.tex
*** empty log message ***

@@
 
-\textbf{Def 1-} \emph{Set of Primitve Operations}: Operations are taken from the set \{forcereadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.\\
+\textbf{Def 1-} \emph{Set of Primitive Operations}: Operations are taken from the set \{force-readoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.\\
 
@@
 
-\textbf{Note 2} \emph{ForcedReadOffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
+\textbf{Note 2} \emph{Forced-Readoffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
 
@@
 
-Each filedescriptor has an assosiated offset with it, within each transaction this offset can be in 4 different states, these states indicate the dependency the transaction has on the value of this offset:\\
+Each filedescriptor has an associated offset with it, within each transaction this offset can be in 4 different states, these states indicate the dependency the transaction has on the value of this offset:\\
 
-1- \textbf{No Access}: This is the default state for all filedescriptors in a transaction and is changed as soon as there is an acsess to the the descriptor within the transaction (any of the use-level operations are invoked).\\
+1- \textbf{No Access}: This is the default state for all filedescriptors in a transaction and is changed as soon as there is an access to the the descriptor within the transaction (any of the use-level operations are invoked).\\
 
-2- \textbf{None}: Meaning there is no dependency for any operation in this transaction on the value of the offset assosiated with this descriptor regarding other transactions.\\ %This stems from the fact that the offset has been assigned an absolute value in this transaction and no operation reads on the value the offset had before this transaction accessed it.\\
+2- \textbf{None}: Meaning there is no dependency for any operation in this transaction on the value of the offset associated with this descriptor regarding other transactions.\\ %This stems from the fact that the offset has been assigned an absolute value in this transaction and no operation reads on the value the offset had before this transaction accessed it.\\
 
@@
 
-4- \textbf{Read Dependency}: This kind of dependency means there is at least one operation acting on an offset value for fd, where the value for fd has been determined by a previously commited transaction.\\
+4- \textbf{Read Dependency}: This kind of dependency means there is at least one operation acting on an offset value for fd, where the value for fd has been determined by a previously committed transaction.\\
 
@@
 
-\textbf{Explanation}: Whenever the offset status for the transaction goes to "Read Dependence", a "forcedreadoffset(fd)" operation is issued immdeiately preceding the operation that caused this transformation.
-The forced-radoofset(fd) is only issued if there is not a forcedofset(fd) in the $OP_{T_i}$ already.\\
+\textbf{Explanation}: Whenever the offset status for the transaction goes to "Read Dependence", a "forced-readoffset(fd)" operation is issued immediately preceding the operation that caused this transformation.
+The forced-radoofset(fd) is only issued if there is not a forced-readoffset(fd) in the $OP_{T_i}$ already.\\
 
-\textbf{Axiom For Diagram:} If the first access to a filedescriptor is a $Seek(fd)$, then the following operation on $fd$ gets the offset value from the assignment made by the $Seek(fd)$ and adavances the offset.
-Hence, the follwoing operations get this offset and the offset value the filedescriptor had had before this transaction accesses fd is never refrenced (thats why it is an absorbing state).
-This conforms to the defnition of "None" state.\\
+\textbf{Axiom For Diagram:} If the first access to a filedescriptor is a $Seek(fd)$, then the following operation on $fd$ gets the offset value from the assignment made by the $Seek(fd)$ and advances the offset.
+Hence, the following operations get this offset and the offset value the filedescriptor had had before this transaction accesses fd is never referenced (thats why it is an absorbing state).
+This conforms to the definition of "None" state.\\
 
@@
 For all the following operations, the offset value is known.
-This conforms to the defenition that there is at least (the first read ever on fd by this transaction) one operation that acts on the offset value for fd and rules out the "Write Dependency" and "None" states.\\
+This conforms to the definition that there is at least (the first read ever on fd by this transaction) one operation that acts on the offset value for fd and rules out the "Write Dependency" and "None" states.\\
 
 If $Write(fd.inode, offset, length)$ is the first access made to fd by this transaction, then the offset to write to, can be decided at commit instant since the Write functions means start writing at the most recent committed fd.offset, hence offset realization can be postponed till commit instant.
-Any Writes or Seeks would still leave this dpendency, since operations after a Seek act on absoulte offset, and Writes preceding any Seek can all determine the offset at commit instant for the same reason as before.\\
+Any Writes or Seeks would still leave this dependency, since operations after a Seek act on absolute offset, and Writes preceding any Seek can all determine the offset at commit instant for the same reason as before.\\
 
-However, if a Read on the same fd in the transaction is invoked there are two possiblities:\\
+However, if a Read on the same fd in the transaction is invoked there are two possibilities:\\
 
 1- A Seek precedes this Read, hence the offset value is absolute and is not read, however the ranges that are supposed to be written by Writes preceding the Seek, may overlap with the range Read is willing to Read from, and according to Rules(Most Recent Changes Should Be Visible) if thats the case the Read should be able to see this data, this suggests the ranges that all the Writes are going to write to should be realized now and this requires settling down on a value for all file descriptors offsets for this inode at this instant.
-Based on these, the most recent commited offset value for all these descriptors should be assigned to the offsets for the Writes that for the first time accessed the descriptor.
-Other for writes prceding the Seek, get this value as being advance by prior writes.\\
+Based on these, the most recent committed offset value for all these descriptors should be assigned to the offsets for the Writes that for the first time accessed the descriptor.
+Other for writes preceding the Seek, get this value as being advance by prior writes.\\
 
-2- No Seek precedes the Read, hence the offset value the Read has to read from is unknown, since preceding Writes to fd have all used unknown offsets, the offset value given to Read is an unknown once, however it has to be known, follwos that the offset value for the Write that for the first time accessed this fd should be decided upon and as shown before, the value should be the most recent commited offset value for fd.
-The offset value for this read or other writes, is the offset value obtained as being advamced by those operations.\\
+2- No Seek precedes the Read, hence the offset value the Read has to read from is unknown, since preceding Writes to fd have all used unknown offsets, the offset value given to Read is an unknown once, however it has to be known, follows that the offset value for the Write that for the first time accessed this fd should be decided upon and as shown before, the value should be the most recent committed offset value for fd.
+The offset value for this read or other writes, is the offset value obtained as being advanced by those operations.\\
 
-The two same possiblities exist when a GetFilePointer operation is invoked on the same fd:\\
+The two same possibilities exist when a GetFilePointer operation is invoked on the same fd:\\
 
-1- If a Seek precedes it, then the offset value becomes absolute and hence the getFilePointer could retreive the value assigned by Seek.\\
+1- If a Seek precedes it, then the offset value becomes absolute and hence the getFilePointer could retrieve the value assigned by Seek.\\
 
-2- Otherwise, the offset value is still unknown, hence to be able to determine the offset value at this instant, the value obtained by reading the last commited offset value should be assigned to the offset value.
+2- Otherwise, the offset value is still unknown, hence to be able to determine the offset value at this instant, the value obtained by reading the last committed offset value should be assigned to the offset value.
 for the first Write to $fd$.\\
@@
 
-\hspace{8mm} \{\{$forcedreadoffset(fd)$ issued as demonstrated at the state diagram if any, it is issued when the state for fd in this transaction is not in "No Dependeny" or "Write Dependency 2"\}\}\\
+\hspace{8mm} \{\{$forcedreadoffset(fd)$ issued as demonstrated at the state diagram if any, it is issued when the state for fd in this transaction is not in "No Dependency" or "Write Dependency 2"\}\}\\
 
@@
 
-Essentially for any fd that the correspondent state digaram in the transactions shows is in a state other than "No Access", a writeoffset(fd) is issued while committing.\\
+Essentially for any fd that the correspondent state diagram in the transactions shows is in a state other than "No Access", a writeoffset(fd) is issued while committing.\\
 
@@
 Any writedata operation within a transaction gets $fd$ and an offset as arguments.
-There writes are reflected in the commit instant, howeverthe offset to write to as we saw earlier for some writes i sdetermined at commit instant and for other is bound to a specefic value bfore commit instant.
+There writes are reflected in the commit instant, however the offset to write to as we saw earlier for some writes i s determined at commit instant and for other is bound to a specific value before commit instant.
 We should have a policy to be able to diffrenciate between these two.
@@
 
-1- If the state for $fd$ a given FileDescriptor in a transaction is "Write Dependency 1" all writes by that transaction to that $fd$ will get the value of the offset to write to at commit instant (since in "Write Dependency 1" all writes are at unknown offsets) .\\\
+1- If the state for $fd$ a given distinguish in a transaction is "Write Dependency 1" all writes by that transaction to that $fd$ will get the value of the offset to write to at commit instant (since in "Write Dependency 1" all writes are at unknown offsets) .\\\
 
-2- If the state for $fd$ is "Read Dependency"  or "No Dependency" then all writes on $fd$ within this transaction should be done at offset detrmined for them when they were invoked (since all writes are to known offsets either determined by the transaction itself or a previously committed transaction).\\
+2- If the state for $fd$ is "Read Dependency"  or "No Dependency" then all writes on $fd$ within this transaction should be done at offset determined for them when they were invoked (since all writes are to known offsets either determined by the transaction itself or a previously committed transaction).\\
 
 3- Otherwise, if the state is "Write Dependency 2", then if the $writedata(fd.inode,...)$ operation precedes a $Seek(fd)$ then the offset is determined at commit instant (since all such writes are at unknown offset).
-Otherise, the writes shold be done at the offset decided upon earlier (the write after a Seek write the iffset detrmined by Seek and hence to a known offset).\\
+Otherwise, the writes should be done at the offset decided upon earlier (the write after a Seek write the offset determined by Seek and hence to a known offset).\\
 
@@
 
-2- Otherwise the initial state is Unknown offsset.\\
+2- Otherwise the initial state is Unknown offset.\\
 
@@
 
+\section{Commuting Operations}
+
+As we saw earlier in Rule 4, any two operations can commute across each other unless they are subject to one of the two conditions in Rule 3.\\
+
+\textbf{Guideline 1}: \emph{Commuting forced-readoffset Operations}: A $forced-readoffset(fd) \in OP_{T_i}$ can go past a $commit_{T_j}$ if and only $\not \exists writeoffset(fd) in OP_{T_j}$.\\
+
+\textbf{Axiom}: It follows immediately from Rule 4 and conditions in Rule 3, that this $forced-readoffset(fd)$ can go pats the commit.
+What remains to be proven is  $ \not \exists writeoffset(fd) \in OP_{T_i}$ such that it precedes
+$forced-readoffset(fd)$, as this would mean even if $\exists writeoffset \in OP_{T_j}$ still the $forced-readoffset(fd)$ could commute with $commit_{T_j}$.\\
+
+This stems from the definition of EndTransaction operation, and the state diagram.
+A $forced-readoffset$ can be issued at any place in $OP_T{i}$ however it would always precede the $writeoffset(fd) \in OP_{T_i}$ since this is last operation in $OP_{T_i}$ before $commit$.\\
+
+\textbf{guideline 2}: \emph{Commuting readdata Operations}:% A $readdata(fd_i.inode,offset_i, lenght_i) \in OP_{T_i}$ can go past a $commit_{T_j}$ if and only if $\not \exists writedata(fd_j.inode, offset_j, length_j) in OP{T_j}$ such that fd_j.inode= fd_i.inode and the two ranges (offset_i, offset_i + length_i) and (offset_i, offset_j + length_j) have an intersection.\\
+
+%\textbf{Axiom}:\ This is
+
 \end{document}

### 2008-09-29 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java
Introduced ZEROORMORE arity, something appears to be broken so another change is coming

@@ -925,10 +925,10 @@ public class OwnershipGraph {
     Hashtable<Integer, TokenTuple> paramIndex2paramToken =
       new Hashtable<Integer, TokenTuple>();
 
-    Hashtable<TokenTuple, Integer> paramTokenStar2paramIndex =
+    Hashtable<TokenTuple, Integer> paramTokenPlus2paramIndex =
       new Hashtable<TokenTuple, Integer>();
 
-    Hashtable<Integer, TokenTuple> paramIndex2paramTokenStar =
+    Hashtable<Integer, TokenTuple> paramIndex2paramTokenPlus =
       new Hashtable<Integer, TokenTuple>();
 
     Hashtable<Integer, LabelNode> paramIndex2ln =
@@ -943,7 +943,7 @@ public class OwnershipGraph {
     Integer bogusID = new Integer(-1);
     Integer bogusIndex = new Integer(-1);
     TokenTuple bogusToken = new TokenTuple(bogusID, true, TokenTuple.ARITY_ONE);
-    TokenTuple bogusTokenStar = new TokenTuple(bogusID, true, TokenTuple.ARITY_MANY);
+    TokenTuple bogusTokenPlus = new TokenTuple(bogusID, true, TokenTuple.ARITY_ONEORMORE);
     ReachabilitySet rsIdentity =
       new ReachabilitySet(new TokenTupleSet(bogusToken).makeCanonical() ).makeCanonical();
 
@@ -951,8 +951,8 @@ public class OwnershipGraph {
     paramIndex2rewriteJ.put(bogusIndex, rsIdentity);
     paramToken2paramIndex.put(bogusToken, bogusIndex);
     paramIndex2paramToken.put(bogusIndex, bogusToken);
-    paramTokenStar2paramIndex.put(bogusTokenStar, bogusIndex);
-    paramIndex2paramTokenStar.put(bogusIndex, bogusTokenStar);
+    paramTokenPlus2paramIndex.put(bogusTokenPlus, bogusIndex);
+    paramIndex2paramTokenPlus.put(bogusIndex, bogusTokenPlus);
 
 
     for( int i = 0; i < fm.numParameters(); ++i ) {
@@ -991,11 +991,11 @@ public class OwnershipGraph {
       paramToken2paramIndex.put(p_i, paramIndex);
       paramIndex2paramToken.put(paramIndex, p_i);
 
-      TokenTuple p_i_star = new TokenTuple(hrnParam.getID(),
[…]

### 2008-09-29 Robust/src/Analysis/OwnershipAnalysis/ReachabilitySet.java

@@ -82,21 +82,6 @@ public class ReachabilitySet extends Canonical {
     return false;
   }
 
-  public ReachabilitySet increaseArity(Integer token) {
-    assert token != null;
-
-    HashSet<TokenTupleSet> possibleReachabilitiesNew = new HashSet<TokenTupleSet>();
-
-    Iterator itr = iterator();
-    while( itr.hasNext() ) {
-      TokenTupleSet tts = (TokenTupleSet) itr.next();
-      possibleReachabilitiesNew.add(tts.increaseArity(token) );
-    }
-
-    return new ReachabilitySet(possibleReachabilitiesNew).makeCanonical();
-  }
-
-
   public ReachabilitySet union(ReachabilitySet rsIn) {
     assert rsIn != null;
 
@@ -154,28 +139,28 @@ public class ReachabilitySet extends Canonical {
 
 	Iterator itrRelement = r.iterator();
 	while( itrRelement.hasNext() ) {
-	  TokenTuple e = (TokenTuple) itrRelement.next();
+	  TokenTuple ttR = (TokenTuple) itrRelement.next();
+	  TokenTuple ttO = o.containsToken( ttR.getToken() );
 
-	  if( o.containsToken(e.getToken() ) ) {
-	    theUnion = theUnion.union(new TokenTupleSet(e.increaseArity() ) ).makeCanonical();
+	  if( ttO != null ) {
+	    theUnion = theUnion.union( new TokenTupleSet( ttR.unionArity(ttO) ) ).makeCanonical();
 	  } else {
-	    theUnion = theUnion.union(new TokenTupleSet(e) ).makeCanonical();
+	    theUnion = theUnion.union( new TokenTupleSet( ttR                 ) ).makeCanonical();
 	  }
 	}
 
 	Iterator itrOelement = o.iterator();
 	while( itrOelement.hasNext() ) {
-	  TokenTuple e = (TokenTuple) itrOelement.next();
+	  TokenTuple ttO = (TokenTuple) itrOelement.next();
+	  TokenTuple ttR = theUnion.containsToken( ttO.getToken() );
 
-	  if( !theUnion.containsToken(e.getToken() ) ) {
-	    theUnion = theUnion.union(new TokenTupleSet(e) ).makeCanonical();
+	  if( ttR == null ) {
+	    theUnion = theUnion.union( new TokenTupleSet(ttO) ).makeCanonical();
 	  }
 	}
-
+	
 	if( !theUnion.isEmpty() ) {
-	  ctsOut = ctsOut.union(
[…]

### 2008-09-29 Robust/src/Analysis/OwnershipAnalysis/TokenTuple.java

@@ -14,34 +14,30 @@ import java.io.*;
 public class TokenTuple extends Canonical {
 
   private Integer token;
-  private boolean isNewSummary;
+  private boolean isMultiObject;
 
-
-  // only summary tokens should have ARITY_MANY?
-  // acutally, multiple-object regions can be arity-many
-  // so isNewSummary actually means "multi-object" in
-  // this class.  CHANGE THIS SOMETIME!
-  public static final int ARITY_ONE  = 1;
-  public static final int ARITY_MANY = 2;
+  public static final int ARITY_ZEROORMORE = 0;
+  public static final int ARITY_ONE        = 1;
+  public static final int ARITY_ONEORMORE  = 2;
   private int arity;
 
 
   public TokenTuple(HeapRegionNode hrn) {
     assert hrn != null;
 
-    token        = hrn.getID();
-    isNewSummary = hrn.isNewSummary();
-    arity        = ARITY_ONE;
+    token         = hrn.getID();
+    isMultiObject = !hrn.isSingleObject();
+    arity         = ARITY_ONE;
   }
 
   public TokenTuple(Integer token,
-                    boolean isNewSummary,
+                    boolean isMultiObject,
                     int arity) {
     assert token != null;
 
-    this.token        = token;
-    this.isNewSummary = isNewSummary;
-    this.arity        = arity;
+    this.token         = token;
+    this.isMultiObject = isMultiObject;
+    this.arity         = arity;
   }
 
 
@@ -53,18 +49,39 @@ public class TokenTuple extends Canonical {
   public Integer getToken() {
     return token;
   }
-  public int     getArity() {
+
+  public boolean isMultiObject() {
+    return isMultiObject;
+  }
+
+  public int getArity() {
     return arity;
   }
 
 
-  public TokenTuple increaseArity() {
-    if( isNewSummary ) {
-      return (TokenTuple) Canonical.makeCanonical(
-               new TokenTuple(token, isNewSummary, ARITY_MANY)
-               );
+  public TokenTuple unionArity( TokenTuple tt ) {
+    assert tt            != null;
+    assert token         == tt.token;
+    assert isMultiObject == tt.isMultiObject;
+
+    if( isMultiObject ) {
+      // for multiple objects only zero-or-mores combined are still zero-or-more
+      // when two tokens are present (absence of a token is arity=zero and is
[…]

### 2008-09-29 Robust/src/Analysis/OwnershipAnalysis/TokenTupleSet.java

@@ -58,54 +58,41 @@ public class TokenTupleSet extends Canonical {
     return ttsOut.makeCanonical();
   }
 
+
   public TokenTupleSet unionUpArity(TokenTupleSet ttsIn) {
     assert ttsIn != null;
     TokenTupleSet ttsOut = new TokenTupleSet();
 
     Iterator<TokenTuple> ttItr = this.iterator();
     while( ttItr.hasNext() ) {
-      TokenTuple tt = ttItr.next();
+      TokenTuple ttThis = ttItr.next();
+      TokenTuple ttIn   = ttsIn.containsToken( ttThis.getToken() );
 
-      if( ttsIn.containsToken(tt.getToken() ) ) {
-	ttsOut.tokenTuples.add(tt.increaseArity());
+      if( ttIn != null ) {
+	ttsOut.tokenTuples.add( ttThis.unionArity( ttIn ) );
       } else {
-	ttsOut.tokenTuples.add(tt);
+	ttsOut.tokenTuples.add( ttThis );
       }
     }
 
     ttItr = ttsIn.iterator();
     while( ttItr.hasNext() ) {
-      TokenTuple tt = ttItr.next();
+      TokenTuple ttIn   = ttItr.next();
+      TokenTuple ttThis = ttsOut.containsToken( ttIn.getToken() );
 
-      if( !ttsOut.containsToken(tt.getToken()) ) {
-	ttsOut.tokenTuples.add(tt);
+      if( ttThis == null ) {
+	ttsOut.tokenTuples.add( ttIn );
       }
     }
 
     return ttsOut.makeCanonical();
   }
 
+
   public TokenTupleSet add(TokenTuple tt) {
     assert tt != null;
     TokenTupleSet ttsOut = new TokenTupleSet(tt);
     return ttsOut.union(this);
-  }
-
-
-  // this should only be done with a multiple-object heap region's token!
-  public TokenTupleSet increaseArity(Integer token) {
-    assert token != null;
-    TokenTupleSet ttsOut = new TokenTupleSet(this);
-    TokenTuple tt
-    = new TokenTuple(token, true, TokenTuple.ARITY_ONE).makeCanonical();
-    if( ttsOut.tokenTuples.contains(tt) ) {
-      ttsOut.tokenTuples.remove(tt);
-      ttsOut.tokenTuples.add(
-        new TokenTuple(token, true, TokenTuple.ARITY_MANY).makeCanonical()
-        );
-    }
[…]

### 2008-09-29 Robust/Transactions/Notes/draft.tex
*** empty log message ***

@@
 
-\section{Commuting Operations}
+The final state for all $writedata$ operations is Absolute, since the write should be perfomed at a specefic offset eventually.
+However, depending on the prevuious circumstances the system would immediately prior to commit determine the offset or would have realized it earlier.\\
+
+\section{Guidelines for Implementaion}
 
@@
 
-\textbf{guideline 2}: \emph{Commuting readdata Operations}:% A $readdata(fd_i.inode,offset_i, lenght_i) \in OP_{T_i}$ can go past a $commit_{T_j}$ if and only if $\not \exists writedata(fd_j.inode, offset_j, length_j) in OP{T_j}$ such that fd_j.inode= fd_i.inode and the two ranges (offset_i, offset_i + length_i) and (offset_i, offset_j + length_j) have an intersection.\\
+\textbf{Guideline 2}: \emph{Commuting readdata Operations}: A $readdata(fd_i.inode,offset_i, lenght_i) \in OP_{T_i}$ can go past a $commit_{T_j}$ if and only if \\
 
-%\textbf{Axiom}:\ This is
+1- $\not \exists writedata(fd_j.inode, offset_j, length_j) in OP{T_j}$ such that $fd_j.inode= fd_i.inode$ and the two ranges $(offset_i, offset_i + length_i)$ and $(offset_i, offset_j + length_j)$ have an intersection.\\
+
+ OR\\
+
+2- $\exists$ a set of $writedata(fd_j.inode,offset_j, lenght_j) in OP_{T_i}$ such that for all of them $writedata \rightarrow readdata$ and $fd_i.inode = fd_j.inode$ and the range $(offset_i, offset_i + length)$ is a subrange for a combiantion of ranges for these $writedata$ operations.\\
+
+\textbf{Axiom}: This follows imeediately from Rule 4 (1 and 2 are concrete representations for conditions 1 and 2 in Rule 3).
+However, it should be noted that whenever a $readata$ operation wants to commute across a $commit$ operation $\in T_j$, if $ \exists writedata \in OP_{T_j}$, the offset for the $wtitedata$ operation is known at this instant (according to the state diagram demonstarted below and regardless of whether $i = j$ or not), hence it would be trivial to see whether these $writedata$ operations intersect (or include in case they are in the same transaction as the $readata$) with the $readdata$ or not.\\
+
+\textbf{Guideline 3:} \emph{Reads Should be Validated At Commit Instant}:
+If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
+
+\textbf{Axiom}: If the data is not valid anymore it means the data $r_n$ has been written since $t_{i-1}$.
+This implies at least one operation $b$ has written the data since the use and $b$ does not precede $a$ and $a$ precedes $b$.
+$b$ is either an operation in the same transaction or a different one.
+However, if $b$ is in the same transaction, then the data read is valid at commit instant by defenition.
+On the other hand, assume $b$ belongs to a different transaction namely $T_j$.
+Since $T_j$ should have already commited, according to Corrolary 2 all operation in $OP_{T_j}$ should precede those in $OP_{T_i}$, however, we know there is at least an operation $b$ that does not precede $a$ (since $a$ has not seen the "writes" made to $r_n$ by $b$).
+Hence, $T_i$ can not commit.\\
+
+\textbf{Guideline 4}: \emph{If Reads Are Valid At Commit Instant, the Transaction Commits}: If by applying Guideline 3 for $T_i$ it is ensured that $\forall r_i \in R{T_i}$ (all data read by $T_i$) is still valid at commit instant, then $\forall T_j \in T_{committed} T_j \rightarrow T_j$ and hence according to Rule 4 $T_i$ commits.\\
+
+proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.
+Rule 5 ensures such transaction would be able to commit.\\
 

### 2008-09-29 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 \begin{document}
-\section{Requirements}
+\section{Correctness}
 \subsection{Transactions}
@@
 
-\textbf{Def 1-} \emph{Set of Operations}: Operations are taken from the set \{readoffset(fildescriptor), getoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
+\textbf{Def 1-} \emph{Set of Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
 We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
 
-\textbf{Def 2-} \emph{Operations Sharing Resources} 1- A readoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
+\textbf{Def 2-} \emph{Operations Sharing Resources} 1- A forcedreadoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
 2- A readdata and writedata operations are said to be sharing resources if they both operate on the same inode AND the range of (offset, offset + length) within one overlaps with that of the other.\\
@@
 \textbf{Def 4-} \emph{Commit Instant and Commit Operation}: A transaction commits when it invokes the "commit" operation.
-A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" mabe by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$.
+A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" made by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$.
 After a transaction invokes commit operation, the transactin ends and no more operation by transaction is done.
@@
 \textbf{Def 6-} \emph{Visbility of Writes}: Assume $T_i$ is an uncommitted transaction and $T_{commited}$ indicates the set of commited transaction (those which have invoked the "commit" operation).
-A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by precedent write operation $a$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
+A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by preceding write operation $a$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
 
@@
 
-\subsection{Rules}
+\section{Rules For }
 
@@
 
-\textbf{Rule 5-}\emph{Operation in the Set of Execeuted Operations Belongin to Committed Transactions Should Be Able To Precede Those in The Transaction About to Commit}: $OP_{executed} = \{op_1,..., op_n\}$ represents the set of executed operations before instant $t_j$ and $T_{committed}$ represents the set of committed transactions committed successfully before $t_j$.
+\textbf{Rule 5-}\emph{Operation in the Set of Execeuted Operations Belonging to Committed Transactions Should Be Able To Precede Those in The Transaction About to Commit}: $OP_{executed} = \{op_1,..., op_n\}$ represents the set of executed operations before instant $t_j$ and $T_{committed}$ represents the set of committed transactions committed successfully before $t_j$.
 If $T_j$ invokes ${commit}$ operation at instant $t_j$ - then $T_j$ commits at instant $t_j$ if and only if operations in $OP$ can be commuted in a way such that $\forall op_i \in OP_{T{committed}}$, $\forall op_j \in OP_{T_j}$, $op_i \rightarrow op_j$.\\
@@
 Now we'll show that if all committed operations can not precede operation of $T_j$ the $T_j$ can not commit.
-$OP = \{op_{T_j}(1), ..., op{T_j}(m)} represent the operations in $T_j$ excluding the ${commit}$ in the order they have occured in $OP_{executed}$.
-Assume \{op_{T_j}(k),...op{T_j}(m)\} can be relocated in $OP_{executed}$ in the standing \{n-(m-k), ...,n-1) but op_{T_j}(k-1) can not.
-This means first of all op_{T_j}(k-1) is a ${read}$ operation reading $r_n$(each transaction has only one ${commit$} operation).
+$OP = \{op_{T_j}(1), ..., op{T_j}(m)\}$ represent the operations in $T_j$ excluding the ${commit}$ in the order they have occured in $OP_{executed}$.
+Assume \{$op_{T_j}(k),...op{T_j}(m)$\} can be relocated in $OP_{executed}$ in the standing \{n-(m-k), ...,n-1) but $op_{T_j}(k-1)$ can not.
+This means first of all $op_{T_j}(k-1)$ is a ${read}$ operation reading $r_n$(each transaction has only one ${commit}$ operation).
 Furthermore, this implies there is a ${commit}$ operation by some transactione $T_i$ between $op{T_j}(k-1)$ and commit operation by $T_j$ and $ \exists op in OP{T_i}$ such that writes $r_n$ and $\not \exists op_i \in OP{T_j}$ such that $op_i \rightarrow op_{T_i}(k-1)$.
@@
 
-proof: Obviously such modifications are not valid and are probably part of a faulty operation.\\
+%proof: Obviously such modifications are not valid and are probably part of a faulty operation.\\
 
-Principle 1) \emph{Reads Should be Validated At Commit Instant}: If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
+%Principle 1) \emph{Reads Should be Validated At Commit Instant}: If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
 
-proof: If the data is not valid anymore it means the data $r_n$ has been written since $t_{i-1}$.
+%proof: If the data is not valid anymore it means the data $r_n$ has been written since $t_{i-1}$.
 This implies at least one operation $b$ has written the data since the use and $b$ does not precede $a$ and $a$ precedes $b$.
@@
 
-The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
+%The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
 Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$.
@@
 
-Principle 2: emph{If Reads Are Valid At Commit Instant, the Transaction Commits}: If by applying Principle 1 for $T_i$ it is ensured that $\forall r_i \in R{T_i}$ (all data read by $T_i$) is still valid at commit instant, then $\forall T_j \in T_{committed} T_j \rightarrow T_j$ and hence according to Rule 4 $T_i$ commits.\\
+%Principle 2: emph{If Reads Are Valid At Commit Instant, the Transaction Commits}: If by applying Principle 1 for $T_i$ it is ensured that $\forall r_i \in R{T_i}$ (all data read by $T_i$) is still valid at commit instant, then $\forall T_j \in T_{committed} T_j \rightarrow T_j$ and hence according to Rule 4 $T_i$ commits.\\
 
-proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.\\
+%proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.\\
 
@@
 %According to priciple 1 the offset chosen should be validated at the the commit instant.\\
-\section{Implementation Overview}
+%\section{Implementation Overview}
 
@@
 Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known.
-Now we will describe the components of our system and demosntrate how the algorithm conforms to the function just described, and how all the rules principles are gurantedd.
 
-to be continued
+%Now we will describe the components of our system and demosntrate how the algorithm conforms to the function just described, and how all the rules principles are gurantedd.
+
+%to be continued
 

### 2008-09-29 Robust/Transactions/Notes/draft.tex
*** empty log message ***

@@
 \begin{document}
+\tableofcontents
 \section{Correctness}
+\subsection{Transactions}
+We have a set of Threads $T$ each representing a transaction.The code for a 
+Transaction is like below:
 
-{Correctness}: A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
+\hspace{12mm}	Thread.doIt(new Callable)()\{
+
+\hspace{12mm}		// code for transaction
+
+\hspace{12mm}	\}
+
+This is adopted from dstm and can and may be changed.
+Within this block which represents a member of set $T$.
+The functions beginTransction and endTransaction are implicitly called by the system without the intervention of the programmer.However, the programmer can read and write from TransactionalFile Objects within the blocks of a member of $T$.
+To provide consisteny the read and write from ordinary Java object files should be prohibited, otherwise the semantics of transactions would not be preserved.
+Hence, the sequence of operations provided to the programmer within a member of $T$ is the set \{TransactionalFile.Read(), TransactionalFile.Write()i, TransactionalFile.Seek()\}.
+However, always a beginTransaction() and commitTransaction() (if the transaction does not abort prior to this point) are performed too.
+\\
+
+A Transaction consists of a sequence of operations.
+Thus, a transaction can be represented as the \{$op_1$, $op_2$, ..., $op_n$\}.
+The flow of program should be in a manner that we could have an arbitrary serial order of the members of $T$ (e.g.
+$T_5,T_6,T_1$,...) or any other order.
+The serial order should be in such a way that for any given two members of the set $T$, it looks all the operations of one occur before all the operation of the other.
+%In the first case we would say the $T_i$ precedes $T_j$ and in the seconds case $T_j$ preceds $T_i$ and $T_i$ can observe all the effects made by the operations in $T_j$.
+\\
+
+\subsection{Defenitions}
+
+textbf{Def 1-} \emph{Set of Primitive Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
+We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
+
+\textbf{Def 2-} \emph{Operations Sharing Resources} 1- A forcedreadoffset operation and writeoffset operations are said to be sharing resources if they both operate on the same filedescriptor.
+2- A readdata and writedata operations are said to be sharing resources if they both operate on the same inode AND the range of (offset, offset + length) within one overlaps with that of the other.\\
+
+\textbf{Def 3-} A read operation can only see the writes made by write operations sharing reources.\\
+
+\textbf{Def 4-} \emph{Commit Instant and Commit Operation}: A transaction commits when it invokes the "commit" operation.
+A transaction $T_i$ is said to "commit" at instant $t_i$, if and only if it reflects its "writes" made by write operations in the filesystem or equivalently makes it writes visible to the whole system for all members of $T$ accesing the data at instant $t_j$ such that $t_j > t_i$.
+After a transaction invokes commit operation, the transactin ends and no more operation by transaction is done.
+An operation $\in OP_{T_i}$ is said to commit if and only if $T_i$ commits.
+Commit instant are not splittable, hence it appears to other transactions that all writes are refleted in the file system together.\\
+
+\textbf{Def 5-} \emph{Precedence Relationship}: If $OP_{executed} = \{op_0, op_1, ..., op_n\}$ represnts the operations executed so far(from all transactions running), and the indices represnt the order of operations executed so far in an ascending manner, we define $op_i \rightarrow op_j$ (precedes) if and only if $i<j$.\\
+
+\textbf{Def 6-} \emph{Visbility of Writes}: Assume $T_i$ is an uncommitted transaction and $T_{commited}$ indicates the set of commited transaction (those which have invoked the "commit" operation).
+A read operation $b \in OP_{T_i}$ MAY ONLY see the writes(changes) made by preceding write operation $a$ that shares resources with $b$ AND also is subject to one of the following conditions:\\
+
+\hspace{7mm} 1- $a \in OP_{T_j}$ ($j \neq i$) such that $T_j \in T_{commited}$ \\
+
+\hspace{7mm} 2- $a \in OP_{T_i}$ and $a$ happens before $b$ in the natural order of the transaction. Formally, $a \rightarrow b$\\
+
+\textbf{Corrolary 1-} \emph{No See in The Fututre}: If $ \exists op_i \in WRITEOP_{T_i}$ and $\exists op_j \in READOP{T_j}$ such that $i \neq j$ and $op_i \rightarrow op_j$ then if $op_j \rightarrow commit-operation_{T_i}$, writes made by $op_j$ are not seen by $op_i$.i\\
+
+proof: Follows immediately from Def 5 and Def 6.\\
+
+\textbf{Corrolary 2-} \emph{Read Must See Most Recent Comitted Write}: If $a \in OP{T_i}$ reads the resource $r_i$ at $t_i$.
+In case $a$ has multiple writer precedessors sharing $r_i$ (denoted as $OP_{precedessors-for-r_i}$), then if all of them are from sets other than $OP_{T_i}$, $a$ sees the writes made by $op_{T_j} \in OP_{precedessors-for-r_i}$ such that $T_j$ has the greatest "commit instant" less than $t_i$ between all transaction with such operations .
+Otherwise, $a$ sees the most recent precedessor in $OP_{T_i}$.
+\\
+
+axiom: Assume $a$ is accessing data at $t_i$, according to Def 6, only writes by those transactions that have already committed would be visble.
+Hence, $t_i$ is neccasarily gretaer than all members of \{$committime_{T_1}, ..., commitime_{T_{i-1}}$\},and hence the writes to $r_i$ made by these commited transaction, have accroding to Def 4 been already reflected in the file system.
+Since, $T_{i-1}$ has the greatest commit instant its changes have overriden that of previously commited transactions and thus, $a$ reading $r_i$ from file system sees these changes.\\
+
+In case 2 that there are writer operations writng $r_i$ and preceding $a$ in $OP_{T_i}$, according to defenition of transaction, $r_i$ should be read from the writes made by write operations in $T_i$, and as the last of such write operation overrides the written data to $r_i$ by other operations, $a$ gets to see the most recent precedessor in $T_i$.\\
+
+\textbf{Def 7-} \emph{Precedence Relationship For Transactions:} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+
+\textbf{Def 8-} \emph{Correctness:} A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
+Behavior for an operation means the data it has read or wants to write.
+Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence.
+However writs always writes the same value no matter what.
+Hence the behavior of a write operation is not alterable
+
+\textbf{Note 1:} Def 7 and Def 8 indicate that if operations can be commuted in a given sequnce of $OP_{executed} = \{op_{T_1}(0), op_{T_4}(0), ...
+op_{T_1}(n)\}$ such that a total ordering of transactions (e.g \{$OP_{T_1}, OP_{T_2}, ..., OP_{T_n}) $\} can be obtained then the execution is consistent and correct.
+The eligiblity to commute is subject to conforming to Corrolary 1 \& 2.\\
+
+\textbf{Def 9-} \emph{Relocation Operations in A Sequence}: In a sequence of operations $OP = \{op_1, op_2, ...,op_n\}$, any operation can relocate its position in the sequence unless as a result of this change, the behavior of a read operation changes (it reads different data).\\
+
+\textbf{Note 2:} \emph{No Commute for Operations Belonging to The Same Transaction}: If $op_i \in OP_{T_i}$ and $op_{i+1} \in OP_{T_i}$, we never commute $op_i$ and $op_{i+1}$, since even if this exchange does not change any operations behavior, there is still no point in doing this as the aim is to put all operations belonging to the same transaction together, the internal order among these is not any of our concern, and the precedence relationship among these as indicated by the execution should be maintained.\\
+
+\textbf{Note 3:} \emph{Precedence Relationship Between Commit Operations Should Be Preserved}: As a rquirement we want to have the notion that transaction are executed in the serial order imposed by their commit operations.
+Hence, commit operations can not be commuted.\\
+
+All the rules explained later are based on the assumptions made in Note 2 \& 3, hence these two types of commution are ruled out by default.\\
+
+\subsection{Rules}
+
+\textbf{Rule 1-} $\forall op_i \in  OP{T_i}$, $\forall op_j \in  OP{T_j}$, $\forall op_k \in  OP{T_k}$, if $op_i \rightarrow op_k$ and  $op_k \rightarrow op_j$, then $op_i \rightarrow op_j$ \\
+
+proof: Follows from the defenition of $\rightarrow$ \\
+
+\textbf{Rule 2-} If $T_i \rightarrow T_k$ and $T_k \rightarrow T_j$ then $T_i \rightarrow T_j$ \\
+
+proof: Follws from Rule 1 and Def 7. \\
+
+\textbf{Rule 3-} \emph{Exchnaging Position of Consecutive Operations}: Formally having the sequence of operations $OP = \{op_1,...,op_i,op_{i+1},...,op_n\}$, if $op_i \in OP_{T_n}$ and $op_{i+1} \in OP{T_m}$ such that $ n\neq m$, $op_i$ and $op_{i+1}$ can exchange positions if and only if none of the follwing conditions apply:\\
+
+\hspace{8mm} 1- If $op_i = {commit}$ and $op_{i+1} = {read}$ and $op_{i+1}$ reads $r_k$, and $\not \exists op_k$ in $OP_{T_m}$ such that writes to $r_k$, and if there  $exists op_l \in OP_{T_n}$ such that writes the data $r_k$, then $op_i$ and $op_{i+1}$ can not exchange positions.\\
+
+\hspace{8mm} 2- If $op_{i+1} = {commit}$ and $op_{i} = {read}$ and $op_{i}$ reads $r_k$ and $\not \exists op_k$ in $OP_{T_n}$ such that writes to $r_k$, and if there $exists op_l \in OP_{T_m}$ such that writes the data $r_k$, $op_i$ and $op_{i+1}$ can not exchange positions.\\
+
+proof: According to Def 9, none of the operatios in the sequence should change behavior as the result of this exchange, however in this argument only $op_i$ and $op_{i+1}$ may change behavior as those are the only operations that their postions in the sequence is changed.
+However, since behavior is only defined for read operations, one of these without losing generality lets say $op_i$ should be a read operation on agiven resource $r_k$.\\
+
+Now changing the $(op_i, op_{i+1})$ to $(op_{i+1}, op_i)$ changes the behavior of $op_i$ if and only if $op_{i+1}$ writes $r_k$ at the file system (all the previous precedessors are still the same, only $op{i+1}$ has been added).
+This means by defenition the $op_{i+1}$ should be a commit operation.
+And, if $op_{i+1}$ is a commit operation for $T_m$, and there is at least one write operation in $T_m$ writing to $r_k$, then according to Corrolary $op_i$ should see the most recent results and hence if there is no precedessor for $op_i$ in $T_n$ itself that writes to $r_k$, then $op_i$ sees the changes made by the write operarion in $T_m$.
+These changes could not have been seen in the first case $(op_i, op_{i+1})$ due to Corrolary 1 (No See in The Future).\\
+
+\textbf{Rule 4} -\emph{Relocating the Position of an Operation Within the Sequence}: Given a sequence of operations $OP = \{op_1, ..., op_i, op_{i+1}, ..., op_j, op_{j+1}, ..., op_n\}$, $op_j$ can be put into the standing $i<j$ within the sequence (resulting in $OP = \{op_1, ..., op_i,op_j,op_{i+1},..., op_{j+1},...,op_n\}$) if and only if $\forall op \in \{op_{i+1}, ..., op_{j-1}\}$, $op$ and $op_j$ belong to different transactions and the pair $(op_j, op)$ or $(op,op_j)$ is not a pair subject to one of the conditions in Rule 3.
+The same holds true for $i>j$.\\
+
+proof: We use induction to prove if assumptions above hold true $op_j$ can be relocated to $i = j-n$.
+Assume the same $OP$ as before.
+If $n = 1$ then since according to assumption the pair $(op_j, op_{j-1})$ is not subject to the conditions in Rule 3, these two can be easily exchanged.
+Now, lets assume the $op_j$ can be relocated to $j-n-1$, now we prove it for $n$.
+After relocation to $j-n-1$, $op_{i+1}$ immediately precedes $op_j$, as according to assumption and Rule 3 $op_j$ and $op_{i+1}$ can exchange positions.
+After this exchange, $op_j$ has been relocated by $n$ and to $i$ and $op_i$ now immediately precedes $op_j$.\\
+
+Now we prove the other side of the argument, that if $op_j$ can be relocated in $i$, $\forall op \in \{op_{i+1}, ..., op{j-1}\}, (op_j, op)$ is not a pair subject to the condition in Rule 3.
+Lets assume there is $op$ in $T_i$ such that $(op, op_{j})$ is a $({read r_n}, {commit})$  and the commit invlolves making a write in $T_j$ to $r_n$ durable and a precedessor writer that writes to $r_n$ does not exists for $op$ in $OP_{T_i}$ , now if $op_j$ is relocated to position $i$, $op_j$ would precede $op$ and hence $op$ would see the writes by the operation in $T_j$ (defenition of commit Def 4 \& Corrolary  2) and hence the behavior of $op$ would change as it does not read the same data as before (the data read before could not have been the same thing due to Corrolary 1).
+If the pair of $(op, op_j)$ is $({commit}, {read r_n})$ the same reasoning would do.\\
+
+The whole argument can be used to prove the Rule for $i > j$ as well.\\
+
+\textbf{Rule 5-}\emph{Operation in the Set of Execeuted Operations Belonging to Committed Transactions Should Be Able To Precede Those in The Transaction About to Commit}: $OP_{executed} = \{op_1,..., op_n\}$ represents the set of executed operations before instant $t_j$ and $T_{committed}$ represents the set of committed transactions committed successfully before $t_j$.
+If $T_j$ invokes ${commit}$ operation at instant $t_j$ - then $T_j$ commits at instant $t_j$ if and only if operations in $OP$ can be commuted in a way such that $\forall op_i \in OP_{T{committed}}$, $\forall op_j \in OP_{T_j}$, $op_i \rightarrow op_j$.\\
+
+proof: If all those operations can be commuted tp precede those in $T_j$ we could have $OP_{executed} = \{op_1,...,OP{T_j}\}$.
+This by defenition of transaction means $T_j$ can commit (it is executed in its whole entierty).\\
+
+Now we have to prove $T_j$ commits only if $\forall T_i \in T_{committed} T_i \rightarrow T_j$.
+Now we'll show that if all committed operations can not precede operation of $T_j$ the $T_j$ can not commit.
+$OP = \{op_{T_j}(1), ..., op{T_j}(m)\}$ represent the operations in $T_j$ excluding the ${commit}$ in the order they have occured in $OP_{executed}$.
+Assume \{$op_{T_j}(k),...op{T_j}(m)$\} can be relocated in $OP_{executed}$ in the standing \{n-(m-k), ...,n-1) but $op_{T_j}(k-1)$ can not.
+This means first of all $op_{T_j}(k-1)$ is a ${read}$ operation reading $r_n$(each transaction has only one ${commit}$ operation).
+Furthermore, this implies there is a ${commit}$ operation by some transactione $T_i$ between $op{T_j}(k-1)$ and commit operation by $T_j$ and $ \exists op in OP{T_i}$ such that writes $r_n$ and $\not \exists op_i \in OP{T_j}$ such that $op_i \rightarrow op_{T_i}(k-1)$.
+On the other hand since there is a ${commit}$ by $T_i$ in the middle, the commit by $T_J$ can not be commuted in a way so $OP$ precedes it without any operation belonging to other transaction in the middle (two ${commits}$ can not commute).
+Hence we can not have a sequence where all operations belonging to $T_j$ are located next to each other, this contradicts the defenition of transaction, hence the transaction can not commit.
+
+%\subsection{TransactionalFile Opeartions}
+%TransactioalFiles can be either created inside or outside $T$.
+The TransactionalFile object ensures transactional access no matter where it is created and accessed.
+Meaning the first time $T_i$ \emph {uses} $tf_j$ the flow of the program should look like no other piece of code (i.e Transactional and non-transactional) outside $T_i$ will \emph {modify} $tf_j$ before $OP(endtransaction)_{T_i}$.
+Otherwise, $T_i$ has to abort.
+\\
+
+%A Transactionalfile can be shared among any subset of the members of $T$. If shared, the offset is shared between these too.
+
+%\section{Implications for the System}
+
+%\subsection{General Implications}
+%Now, if $T_i$ and $T_j$ do not either write the data the other one reads, according to Rule 2 and 3 both can commit.
+This means even if $T_i$ accesses $r_k$ before $T_j$ does, but $T_j$ commits before $T_i$, given that $T_j$ has not modified the data in use by $T_i$, $T_i$ could still commit.
+\\
+
+%It should be noted that according to Rule 3 even if all but one of the transactions in the set of committed transaction precede $T_i$ which is about to commit, , still the transaction can not commit.
+Therefore it takes only one operation to make the transaction dependent (all the committed transaction should precede this transaction but can not since one of the operations in the committed transaction does not precede an operation in this transaction).
+Formally, if there is an operation $b \in OP_{T_j}$ and an operation $a \in OP_{T_i}$ such that $a$ does not precede $b$ then $T_i$ can not precede $T_j$.
+In the rules below $T_i$ is not commited yet and $T$ denotes the set of all commited or active transactions.
+\\
+
+%Assumption : The reads within transaction do actually occur when they are encountered.
+However, no change to the file system is done before commit instant as said before (writes, changing the offset and etc.)\\
+
+%Assumption: seek operation means after this operation is executed, the offset should be at the chosen value regardless of the actual value of the offset in the file system.\\
+
+%Principle 0: An operation should not see any modifications other than those made by precedessors (either in the same transaction or others)\\
+
+%proof: Obviously such modifications are not valid and are probably part of a faulty operation.\\
+
+%Principle 1) \emph{Reads Should be Validated At Commit Instant}: If an operation $a$ that "reads" some data $r_n$ (reads the data at some $t < t_{commit-of-the-transaction}$(the commit instant)), it should be ensured that the data $r_n$ is still valid in the actual file system at $t_{commit-of-the-transaction}$ (commit instant) or $T_i$ has to abort.\\
+
+%proof: If the data is not valid anymore it means the data $r_n$ has been written since $t_{i-1}$.
+This implies at least one operation $b$ has written the data since the use and $b$ does not precede $a$ and $a$ precedes $b$.
+$b$ is either an operation in the same transaction or a different one.
+According to Def 4, however if $b$ is in the same transaction, then $b$ can not have commited yet and hence the changes are not reflected in the filesystem so it is still valid at commit instant.
+Hence, $b$ belongs to a different transaction namely $T_j$.
+Since $T_j$ should have already commited, according to Rule 3 all operation in $OP_{T_j}$ should precede those in $OP_{T_i}$, however, we know there is at least an operation $b$ that does not precede $a$ (since $a$ has not seen the "writes" made to $r_n$ by $b$).
+Hence, $T_i$ can not commit.\\
+
+%The same reasoning could be done for $T_i$ and $T_{i-1}$, $T_{i-1}$ the last commited transaction before $T_{i}$.
+Now according to rule 3, since $T_j$ succeds $T_i$ and $T_i$ succeds $T_{i-1}$, hence $T_j$ succeds $T_{i-1}$.
+Same reasoning is applied for all the members of $T_{commited}$.
+\\
+
+%Principle 2: emph{If Reads Are Valid At Commit Instant, the Transaction Commits}: If by applying Principle 1 for $T_i$ it is ensured that $\forall r_i \in R{T_i}$ (all data read by $T_i$) is still valid at commit instant, then $\forall T_j \in T_{committed} T_j \rightarrow T_j$ and hence according to Rule 4 $T_i$ commits.\\
+
+%proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.\\
+
+%Principle 2) 1-A seek operation in $OP_{T_i}$ does not make $T_i$ dependent on any data and hence does not count as "using" ("use" as defined in Def 1).\\
+
+%The seek operations seeks to an offste within the file descriptor regardless of the changes made by opretaions in all transaction, hence the result would always be the same so according to Def 2 it does not count as using.\\
+
+%rinciple 3) 1- A read operation in $OP_{T_i}$ "uses" contents read and makes $T_i$ dependent on the file contents read.\\
+
+%proof: Due to assumption 1 and since the data read by this operation can be used for computation, in case the data read would change, the data and hence computations results would be different.
+According to Def 2 it uses the data\\
+
+%Principle 4) 1- A write operation in $OP_{T_i}$ does not make $T_i$ dependent on file contents.\\
+
+%proof: The result of a write would always be the same contents thus, according to Def 2 does not count as using.\\
+
+%\subsection{A Model for Offset and Data Dependeny for Operations}
+
+%Assumption: Each operation has a offset status assioated with it. We call this operation.offsetstatus. Each operation has a data satus assosiated with it namely operation.datastatus\\
+
+%Assumption:  An operation with Speculative offset means the offset that the operation would be perfomed at can be relocated in the commit instant.
+An operation with absolute offset means the value is absolute and does not depend on any other operation OR the operation only specifies a specific value for the offset for the next operation (i.e.
+seek).
+An operation with defenite offset means the offset value that operation has to be carried on from, can not be relocated, but still could have changed before commit instant by other committed transaction and not being valid at commit instant\\
+
+%Assumption: Based on previous assumptions read.datastatus = Defenite and others are Speculative, hence they do not use the "file contents"
+
+%Principle 5: an operation with defeinte offset status assosiated with it is the only one "using" the offset value.\\
+
+%proof: For speculative and absolute it comes form the defeniton that they do not count as using, since one is determined at commit instant and hence read at the same time, and the other is always the same value.
+However, with defenite, if some other transaction changes the offset of the file descriptor, then the result of the operation would have been possibly different.
+According to Def 2 it uses the offset data.\\
+
+%Def: We define a function $f$ that takes as input an operation (i.e.
+seek, read, write) and gives as the output the offsetstatus assosiated with that operation.
+In speaking, $f$ determines the offsetstatus assoiated with an operation given that it is the ONLY operation in the operation set of the transaction.
+\\
+
+%1- $f$(Seek) = Absolute
+
+%proof: seek operation does not invlove reading offset value hence, according to assumptions it is considered as absoulute.\\
+
+%2-$f$(Read) = Defenite
+
+%proof: Since according to Principle 3, read is actually done before the commit instant and hence can not be relocated in the commit instant.
+According to Principle 1 and 5 the offset the read is done from should not be affected by other members of $T$ before this transaction gets to its commit instant.
+This means not the only offset can not be relocated, but a check should be done at the commit instant for its validity.\\
+
+%3-$f$(Write) = Speculative
+
+%proof: If write is the only operation, then since according to Principle 4 the write does not use any file contents before commit instant, hence the ofsset value can be determined at commit instant from the most recently commited offset value by then.
+Then the write is done on the offset.
+This preserves the semantics since the commit instant is atomic by defenition and Rule 6 and 5 are preserved, as the write operation is getting the most recent data(offset) and hence would see all the changes made to it by commited transactions so far and hence this write operation would succed all the operations in other commited transaction.
+Consequently this transaction can succed those.\\
+
+%Requirements: To determine an operation should use Absolute, Define or Speculative offset type (the first and third would be used in commit instant) respective to other operatins in the set, the requirements below should be provided:\\
+
+%Req 1- 1-Any operation follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Absolute, has offsetstatus = Absolute itself.
+2-Any operation that applying $f$ to it would yield in Absolute, has offsettype = absolute \\
+
+%proof: 1-Lets assume $op$ is the first operation with offsettype = Absolute in the set of operatopns.
+The immediate operation ($op_{imm}$) after $op$ uses the absolute offset specified by $op$ or the absolute offset advanced by a certain number in case of read or write.
+$op_{imm}$ either advances this value or specifies another absolute value, in either case the offset type for $op_{imm}$ would be absolute.
+The same reasoning could be done for all the follwing operations.\\
+
+%2- Since such an operation is seek and seek regardless of all other operation (in and out of transaction) sets the offset and hence is always absolute.\\
+
+%Req 2- 1- Any operations $op$ that applying $f$ on it would yield in Definite, has offsettype = Defenite unless speified otherwise by Req 1  2-Any operation immediately follwoing an operation $op$ (which belongs to the same set of operations) with offsetstatus = Defenite, has offsetstatus = Defenite itself.
+unless specified otherwise by Req 1\\
+
+%proof: 1- if $f$ makes the output Defenite it means this operation should "use" offset value at that time unless some previous instruction has set the offset to specific value independent of other transactions and thus changing the offset value would not have any effect on the outcome of $op$ as the value $op$ should be carried on from would be independent.
+Operation having such an effect is the one with Absolute offsettype.\\
+
+%2- The following operation should be Defenite type since $op$ has bound the offset to a value that should be validated at commit instant (Principle 1), unless it is a seek that only sets the offset.\\
+
+%Req 3: Any operation with offsetstaus = Defenite, should change the offsetstatus for prveious operations with a value of Speculative, to Defenite.\\
+
+%If $op.offsettype = Definte$ means no previous operations are Absolute (Req 1).
+So it just could be a mixture of Speculative and Defenite.
+Lets assume $op_{Def}$ as the first operation after a $op_{spec}$ a Speculative one (Rq 2 ensure after A Defenite there is no Speculative).
+$op_{Def}$ makes the offset bound to a specific value and $op_{Def} succeds $op{Spec}$ so it should be able to see the changes made by $op{Spec} this neccesitaes that $op{Spec}$ be done at a specific offset such that when advanced as the effect of operation, it gives the offset chosen by $op{Def}$, otherwise $op{Def}$ does not see the effects of $op{Spec}$ which is in contradiction to presumtions.
+Hence, $op_{Spec}.offsettype$ should be converted to Defenite.\\
+
+%Req 4: Any operation $op$ which applying $f$ on it yields in Speculative has offsettype=Speculative unless specified otherwise by previous requirements.\\
+
+%proof: If we denote $OP_{prev}.offsettype$ as the offsettypes for the prviously encountered operations, considering all requirements this means all (if any) the members of $OP_{prev}$ should be Speculative for $op$ to be able to be Speculative.
+In this case the offset passed to $op$ is Speculative and if $op$ is Speculative as considered alone then it would carry on the actions in the passed-in Speculative offset.\\
+
+%Req 5: An operation with datastatus = Defenite, converts all the speculative offsttypes of the previous operations to Defenite. This requirement is always enforced.\\
+
+%proof: Since if datastatus = Defenite, this mean the operation is "using" or "reading" some file contents- an irreversible action- and as this operation should be able to see the modifications made by all preceding operations, if these are speculative, at commit instant they may "relocate" their modifications, this means eitehr $op$ may not see some changes made by precedessors or may see some changes not made by any precedessors (since the speculatively changes were used by $op$ however these did not get reflected in the actual file system since they were relocated at commit instant).
+Either way contradicts the defenitions and principles (Def 8 and Principle 0).\\
+
+%Note: Req 5 suggest if datatype = Definite this causes all the previous operation with Speculative as offsettype to be changed to Defenite.
+
+%Def: We define a function $g(offsetstat_1, offsettat_2, ..., offsetstat_{n-1}, operation)$ that takes an input  $n-1$ number of $op.offsetstatus$ plus an operation and gives as the output $n$ number of $op.offsetstatus$.
+The $g$ functions provides the requirements mentioned above.
+Follwing rules determine the output, the rules are ordererd according to their priority:\\
+
+%1- if $f(operation) = Absolute$, $g(offsetstat_1, ..., {offsetstat_{n-1}}, operation) = ({offsetstat_1}, ..., {offsetstat_{n-1}}, Absolute)$ leaving all offsetstats intact.\\
+
+%2- if $f(operation) = Defenite$:\\
+
+%\hspace{ 8mm}
+%	2.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}$\} such that offset = Absolute,  $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ...
+,Absolute)$ leaving all offsestats intact.\\
+
+%\hspace{ 8mm}
+%	2.2- else $\forall offsetstat \in (offsetstat_0, ..., offsetstat_{n-1})$ if offsetstat = Speculative, change its value to Defenite in the output of $g$, plus appending a Defenite to the output (for instane $g(speculative, speculative, read) = (defenite, defeinte, definte)$)\\
+
+%3- if $f(operation) = Speculative$:\\
+
+%\hspace{ 8mm}
+%	3.1- if $\exists offset \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offset = Absolute, $g(offsetstat_1, ...
+offsetstat_{n-1}, operation) = (offsetstat_1, ...
+Absolute)$ leaving all offsestats intact.\\
+
+%\hspace{ 8mm}
+%	3.2- else if $\exists offsetstat \in \{offsetstat_1, ..., offsetstat_{n-1}\}$ such that offsetstat = {Defenite},  $g(offsetstat_1, ...,  offsetstat_{n-1}, operation) = (offsetstat_1 ,..., offsetstat_{n-1}, Defenite)$\\
+
+%\hspace{ 8mm}
+%	3.3- else $g(offsetstat_1, ..., offsetstat_{n-1}, operation) = (offsetstat_1, ..., offsetstat_{n-1}, Speculative)$\\
+
+%4- After doing the above check if datastatus = Defenite, then change all offsettypes in the input that are Speculative to Defenite in the output.
+
+%51, 2.1, 3.1 ensure Req 1. 2.2 and 3.2 ensures Req 2. 2. ensure Req 3, and finally 3.3 provides Req 4. 4 also ensures Req 5.
+
+%$f: \{op_0.offsetstatus,op_1.offsetstatus,...,op_{n-1}.offsetstatus\} \rightarrow \{op_0.offsetstatus, op_1.offsettatus,...,op_{n-1}.offsetstatus,op_m.offsetstatus, \}
+
+%2- Since due to assumption 1, the read should be actually done, it has to be done from a real offset, and since the commited offset at the commit instant is unknown in adavance, the currenlty most recent commited offset is chosen.
+This makes the read and hence transaction dependent on the offset value read.
+
+%2- Since all the following read and writes at least succed this seek operation, they should be able to see the changes made by it unless some other operation in between changes the data in question (offset).
+Lets first assume the operation ($op$) following the seek.
+If $op$ is a read or write, then it would carry on reading or writing the data from the absolute offset so it would advance the aboslute offset resulting in another absolute offset and hence no "use" of the actual offset would be applicable.
+If the following is a seek, then the resultant offset would be another absolute offste.
+Same reasoning could be done for all the succeding operations and hence the offset would be still absolute.
+To prove only seek can make the offset absolute it should have been made absolute by read or write, however as we'll see in Principles 2 and 3 they can not yield in an absolute offset.
+Hence, an absolute offset indicates there has been a seek.\\
+%According to priciple 1 the offset chosen should be validated at the the commit instant.\\
+%\section{Implementation Overview}
+
+%proof: A write operation writes to the most recently commited offset (unless imposed otherwise by a seek or a prior read or a following read as shown above) of the file descriptor.
+According to Def 2, it does not "use" any data.
+Since the write does not happen till commit instant, the offset chosen during the execution of transaction can be speculative, and the actual offset to be written to, is determined at the sommit instant, when the most recently commited offset is known.
+
+%Now we will describe the components of our system and demosntrate how the algorithm conforms to the function just described, and how all the rules principles are gurantedd.
+
+\section{An Abstract Model For The System}
+\subsection{Assumption For The System}
+%{Correctness}: A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
 Behavior for an operation means the data it has read or wants to write.
@@
 
-\textbf{Def 1-} \emph{Set of Primitive Operations}: Operations are taken from the set \{force-readoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.\\
+%\textbf{Def 10-} \emph{Set of Primitive Operations}: Operations are taken from the set \{force-readoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.\\
 
-\textbf{Def 2-} \emph{Set of User-Level Operations}: User-Level Operations are taken from the set \{Read(fildescriptor), GetFilePointer(filedescriptor), Write(filedescriptor), Seek(filedescriptor), EndTransaction\}.\\
+\textbf{Def 10-} \emph{Set of User-Level Operations}: User-Level Operations are taken from the set \{Read(fildescriptor), GetFilePointer(filedescriptor), Write(filedescriptor), Seek(filedescriptor), EndTransaction\}.\\
 
-\textbf{Note 1-} \emph{Assignment Operations Need Not Be Shown In $OP_{excecuted}$}: Operations like offset = offset + length and other assignment operations in $OP_{T_i}$ need not be shown in the actual sequence of operations namely $OP_{executed}$ that consists of operations executed by different transaction so far, the reason is simply all such operations are local to the transaction and do not affect any other transaction's state and hence do not restrict the commution of other operations in any manner.\\
+\textbf{Note 4-} \emph{Assignment Operations Need Not Be Shown In $OP_{excecuted}$}: Operations like offset = offset + length and other assignment operations in $OP_{T_i}$ need not be shown in the actual sequence of operations namely $OP_{executed}$ that consists of operations executed by different transaction so far, the reason is simply all such operations are local to the transaction and do not affect any other transaction's state and hence do not restrict the commution of other operations in any manner.\\
 
-\textbf{Note 2} \emph{Forced-Readoffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
+\textbf{Note 4-} \emph{Forced-Readoffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
 
-\section{FileDescriptor Offset State per Transaction}:
+\subsection{Transaction Dependency on FileDescriptor Offset}:
 
@@
 
-\section{User-Level Operations Structure}
+\subsection{User-Level Operations Structure}
 
@@
 
-\section{FileDescriptor Offset State per writedata Operation}
+\subsection{$writedata$ Dependecy on Offset}
 
@@
 
-\section{Guidelines for Implementaion}
+\subsection{Guidelines for Implementaion}
 
@@
 
-proof: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.
+\textbf{Axiom}: If all data read is still valid at commit instant, means all operation in the set of operations belonging to committed transactions, can be relocated to precede those in $T_i$ (since no writes have been seen), and consequently all those transactions precede $T_i$.
 Rule 5 ensures such transaction would be able to commit.\\

### 2008-09-29 Robust/Transactions/Notes/sysgurantees.tex
*** empty log message ***

@@
 
-This is adopted from dstm and can and may be changed. Within this block which 
-represents a member of set $T$.
+This is adopted from dstm and can and may be changed.
+Within this block which represents a member of set $T$.
 The functions beginTransction and endTransaction are implicitly called by the system without the intervention of the programmer.However, the programmer can read and write from TransactionalFile Objects within the blocks of a member of $T$.
@@
 
-\textbf{Def 1-} \emph{Set of Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
+textbf{Def 1-} \emph{Set of Primitive Operations}: Operations are taken from the set \{forcedreadoffset(filedescriptor), writeoffset(filedescriptor), readdata(inode, offset, length), writedata(inode, offset, length), commit\}.
 We denote read operations as readoffset and readdata and write operations as writeoffset and writedata.\\
@@
 
-\textbf{Def 7-} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
+\textbf{Def 7-} \emph{Precedence Relationship For Transactions:} $\forall$ $op_{T_i}$ $\in OP_{T_i}$ and $\forall op_{T_j}\in OP_{T_j}$ if and only if $op_{T_i} \rightarrow op_{T_j}$ then $T_i$ $\rightarrow T_j$ \hspace{8mm} (this defines precedes relationship for members of $T$) \\
 
-\textbf{Def 8-} \emph{Correctness}: A sequence of tarnsaction are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
-Behavior for an operation means the data it has read.
-Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence.\\
+\textbf{Def 8-} \emph{Correctness:} A sequence of transactions are said to be consistent if and only if a total ordeing of them according to precedence relationship can be established that demonstrates the same behavior as the execution of the program.
+Behavior for an operation means the data it has read or wants to write.
+Demonstrating the same behavior thus means all the read operations should still see the same data in the new sequence as they have seen in the actual sequence.
+However writs always writes the same value no matter what.
+Hence the behavior of a write operation is not alterable
 
@@
 
-\section{Rules For }
+\subsection{Rules}
 

### 2008-09-30 Robust/Transactions/Notes/draft.tex
*** empty log message ***

@@
 However writs always writes the same value no matter what.
-Hence the behavior of a write operation is not alterable
+Hence the behavior of a write operation is not alterable.\\
 
@@
 
-proof: According to Def 9, none of the operatios in the sequence should change behavior as the result of this exchange, however in this argument only $op_i$ and $op_{i+1}$ may change behavior as those are the only operations that their postions in the sequence is changed.
+\textbf{Proof}: According to Def 9, none of the operatios in the sequence should change behavior as the result of this exchange, however in this argument only $op_i$ and $op_{i+1}$ may change behavior as those are the only operations that their postions in the sequence is changed.
 However, since behavior is only defined for read operations, one of these without losing generality lets say $op_i$ should be a read operation on agiven resource $r_k$.\\
@@
 Assume \{$op_{T_j}(k),...op{T_j}(m)$\} can be relocated in $OP_{executed}$ in the standing \{n-(m-k), ...,n-1) but $op_{T_j}(k-1)$ can not.
-This means first of all $op_{T_j}(k-1)$ is a ${read}$ operation reading $r_n$(each transaction has only one ${commit}$ operation).
+This means first of all $op_{T_j}(k-1)$ is a ${read}$ operation reading $r_n$(each transaction has only one ${commit}$ operation).\\
+
 Furthermore, this implies there is a ${commit}$ operation by some transactione $T_i$ between $op{T_j}(k-1)$ and commit operation by $T_j$ and $ \exists op in OP{T_i}$ such that writes $r_n$ and $\not \exists op_i \in OP{T_j}$ such that $op_i \rightarrow op_{T_i}(k-1)$.
@@
 
-\textbf{Note 4-} \emph{Forced-Readoffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
+\textbf{Note 5-} \emph{Forced-Readoffset(fd)}: Reads the offset for the filedescriptor and makes the transaction bound to this value.\\
 
-\subsection{Transaction Dependency on FileDescriptor Offset}:
+\subsection{Transaction Dependency on FileDescriptor Offset}
 
@@
 
+\textbf{Guideline 5}: \emph{A Transaction About to Commit Can Abort Other Transaction Safely}: A transaction about to commit can check to what resources it has alreay written (denote this as $R_i$), an then $\forall T_j in T$  such that $T_j$ is active at this instant can check to see if any of those have read $r_i \in R_i$, if so and no other operation in $OP_{T_j}$ preceding this read has written to $r_i$ then $T_i$ can abort $T_j$, since $T_j$ is doomed to abrot anyway (according to Guideline 3).\\
+
+\section{System Implementation Overview}
+
+\subsection{Components}
+
+In this sextion we will show how our system conforms to the guidlines and rules required by the system.
+Only the main components of the system are depicted in the figure and listed below.
+It should be noted that even for theses classes the major functions and fields are exposed in the illustration.\\
+
+\includegraphics[scale = 0.3]{uml.png}\\
+
+\textbf{TransactionalFile}: This is the object most user-level operations are perfomed on.
+It can be either created inside or outside a transaction.
+Accessing a TransactionalFile by $T_i$ means $T_i$ has invoked a user-level operation on the object.
+A Transactionalfile can be shared among any subset of the members of $T$.
+If shared, the offset is shared between these as well.\\
+
+\textbf{ExtendedTransaction}: The class and data structures required to do the actions required by a transaction (commit, abort, ...).\\
+
+\textbf{TransactionalLocalFileAttributes}: The class to maintain the data structures specific to a transaction regarding an already accessed TransactionalFile object (offset status for the transaction, inital offset status for each Write operation and etc.).\\
+
+\textbf{GlobalOffset}: The class to maintain the global offset assosiated with each TransactionalFile object (the value, who owns the offset, who reads the offset, etc.) \\
+
+\textbf{GlobalDataStructure}: The class to maintain the global data structure assosiated with each inode (such as mapping of block locks for each inode).\\
+
+\textbf{ConflictManager}: The manager to resolve the conflict, this can be  when a transaction can not successfully commit  or a read or write has to do subsidary actions regarding other transaction or conflict over locks and etc.\\
+
+\textbf{BlockDataStructure}: The data structure representing a block in an inode. GlobalDataStructure uses instances of this class to preserve the info
+rmation.\\
+
+\textbf{WriteOperation}: The structure of a writedata operatin, including the range it is supposed to write, the data to be written and wether this is an absolute or unknown offset value.\\
+
+\subsection{Algorithm}
+
+In this section we examine the psudecode for user-level operations in the propsed system and show how our system conforms to the formalisatiom buitl up in earlier sections.
+
+\textbf{$tf_i$.Read(data[])}{\\
+
+\hspace{8mm} If (tfla = currenttransaction.accessedfile.contains($tf_i$))
+
+\hspace{11mm}	for any of the writes in writeuffer to $tf_i$.inode
+
+\hspace{14mm}		if [tfla.localoffset, tfla.offset + data.length] overlaps with range for the write
+
+\hspace{17mm}			copy the intersect portion to the correspondent portion of data[]
+
+\hspace{11mm}	if any non-filled portion of data[] exists{
+
+\hspace{14mm}		try to lock $tf_i$.offset.lock
+
+\hspace{14mm}		try to lock all the blocks within range [tfla.localoffset, tfla.offset + data.length]
+
+\hspace{14mm}		if all locks succeed then read the non-filled portions from $tf_i$.file
+
+\hspace{14mm}		if not succeed consult contentionManager to resolve the conflict
+
+\hspace{8mm} else add $tf_i$.inode to files accessed by this transaction and create the corresponding TransactionalLocalFileAttributes and call Read(data[])
+
 \end{document}

### 2009-10-07 Robust/src/Main/Main.java
add recovery Task file

@@ -268,6 +268,8 @@ public class Main {
     if (state.THREAD||state.DSM||state.SINGLETM) {
       sc.getClass("Thread");
     }
+    if(state.DSM)
+      sc.getClass("Task");
 
     sc.semanticCheck();
 

### 2009-10-08 Robust/src/Analysis/MLP/MLPAnalysis.java
disjoint analysis with a set of flagged allocation sites of live-in variable.

@@ -48,6 +48,8 @@ public class MLPAnalysis {
   private Hashtable< FlatNode, CodePlan                 > codePlans;
 
   private Hashtable< FlatEdge, FlatWriteDynamicVarNode  > wdvNodesToSpliceIn;
+  
+  private Hashtable< MethodContext, HashSet<AllocationSite>> mapMethodContextToLiveInAllocationSiteSet;
 
   public static int maxSESEage = -1;
 
@@ -100,6 +102,8 @@ public class MLPAnalysis {
     notAvailableResults  = new Hashtable< FlatNode, Set<TempDescriptor>      >();
     codePlans            = new Hashtable< FlatNode, CodePlan                 >();
     wdvNodesToSpliceIn   = new Hashtable< FlatEdge, FlatWriteDynamicVarNode  >();
+    
+    mapMethodContextToLiveInAllocationSiteSet = new Hashtable< MethodContext, HashSet<AllocationSite>>();
     
 
     FlatMethod fmMain = state.getMethodFlat( typeUtil.getMain() );
@@ -191,6 +195,26 @@ public class MLPAnalysis {
       FlatMethod fm = state.getMethodFlat( d );
       methodEffects(fm);
     }
+    
+    // disjoint analysis with a set of flagged allocation sites of live-in variable
+	try {
+		OwnershipAnalysis oa2 = new OwnershipAnalysis(state, tu, callGraph,
+				state.OWNERSHIPALLOCDEPTH, state.OWNERSHIPWRITEDOTS,
+				state.OWNERSHIPWRITEALL, state.OWNERSHIPALIASFILE,
+				state.METHODEFFECTS,
+				mapMethodContextToLiveInAllocationSiteSet);
+		// debug
+		methItr = oa2.descriptorsToAnalyze.iterator();
+		while (methItr.hasNext()) {
+			Descriptor d = methItr.next();
+			FlatMethod fm = state.getMethodFlat(d);
+			debugFunction(oa2, fm);
+		}
+		//
+	} catch (IOException e) {
+		System.err.println(e);
+	}
+    
 
 
     // 7th pass
@@ -789,6 +813,35 @@ public class MLPAnalysis {
     } // end switch
   }
   
+  private void debugFunction(OwnershipAnalysis oa2, FlatMethod fm) {
+	  
+	  String methodName="method1";
+	  
+	  MethodDescriptor md=fm.getMethod();
[…]

### 2009-10-08 Robust/src/Analysis/OwnershipAnalysis/AllocationSite.java

@@ -39,6 +39,8 @@ public class AllocationSite {
   public static final int SHADOWAGE_in_I          = -101;
   public static final int SHADOWAGE_oldest        = -102;
   public static final int SHADOWAGE_summary       = -103;
+  
+  private boolean flag=false;
 
 
   public AllocationSite(int allocationDepth, FlatNew flatNew, String disjointId) {
@@ -195,5 +197,13 @@ public class AllocationSite {
     } else {
       return                              toString()+"\\n"+getType().toPrettyString();
     }
+  }
+  
+  public void setFlag(boolean flag){
+	  this.flag=flag;
+  }
+  
+  public boolean getFlag(){
+	  return flag;
   }
 }

### 2009-10-08 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java

@@ -343,6 +343,9 @@ public class OwnershipAnalysis {
 	
 	//keep internal ownership graph by method context and flat node
 	private Hashtable<MethodContext, Hashtable<FlatNode, OwnershipGraph>> mapMethodContextToFlatNodeOwnershipGraph;
+	
+	//map method context to a set of allocation sites of live-in vars
+	private Hashtable<MethodContext, HashSet<AllocationSite>> mapMethodContextToLiveInAllocationSiteSet;
 
 
 
@@ -374,6 +377,26 @@ public class OwnershipAnalysis {
 	  init(state,tu,callGraph,allocationDepth,writeDOTs,writeAllDOTs,aliasFile);
 	  
   }
+  
+  // new constructor for on-demand disjoint analysis
+	public OwnershipAnalysis(
+			State state,
+			TypeUtil tu,
+			CallGraph callGraph,
+			int allocationDepth,
+			boolean writeDOTs,
+			boolean writeAllDOTs,
+			String aliasFile,
+			boolean methodEffects,
+			Hashtable<MethodContext, HashSet<AllocationSite>> mapMethodContextToLiveInAllocationSiteSet)
+			throws java.io.IOException {
+
+		this.methodEffects = methodEffects;
+		this.mapMethodContextToLiveInAllocationSiteSet=mapMethodContextToLiveInAllocationSiteSet;
+		init(state, tu, callGraph, allocationDepth, writeDOTs, writeAllDOTs,
+				aliasFile);
+
+	}
   
   private void init(State state,
           TypeUtil tu,
@@ -874,6 +897,21 @@ public class OwnershipAnalysis {
       lhs = fnn.getDst();
       if( !lhs.getType().isImmutable() || lhs.getType().isArray() ) {
 	AllocationSite as = getAllocationSiteFromFlatNewPRIVATE(fnn);
+	
+	if (mapMethodContextToLiveInAllocationSiteSet != null){
+		HashSet<AllocationSite> alllocSet=mapMethodContextToLiveInAllocationSiteSet.get(mc);
+		if(alllocSet!=null){
+			for (Iterator iterator = alllocSet.iterator(); iterator
+					.hasNext();) {
+				AllocationSite allocationSite = (AllocationSite) iterator
+						.next();
+				if(allocationSite.flatNew.equals(as.flatNew)){
+					as.setFlag(true);
+				}
+			}
+		}
+	}
+	
 	og.assignTempEqualToNewAlloc(lhs, as);
       }
       break;

### 2009-10-08 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -1330,6 +1330,10 @@ public class OwnershipGraph {
       if( as.getType().isClass() ) {
 	hasFlags = as.getType().getClassDesc().hasFlags();
       }
+      
+      if(as.getFlag()){
+    	  hasFlags=as.getFlag();
+      }
 
       hrnSummary = createNewHeapRegionNode(idSummary,    // id or null to generate a new one 
                                            false,	 // single object?			 

### 2009-10-08 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java
Allow some disjointness improvements to be turned off, add script to run all benchmarks add aggregate results (way overdue), also checking in a test that verifies strong update and global sweep can alter sharing for some programs

@@ -119,25 +119,36 @@ public class OwnershipAnalysis {
   // use the methods given above to check every possible alias
   // between task parameters and flagged allocation sites reachable
   // from the task
-  public void writeAllAliases(String outputFile, String timeReport) throws java.io.IOException {
+  public void writeAllAliases(String outputFile, 
+                              String timeReport,
+                              String justTime,
+                              boolean tabularOutput,
+                              int numLines
+                              ) throws java.io.IOException {
     checkAnalysisComplete();
 
     BufferedWriter bw = new BufferedWriter(new FileWriter(outputFile) );
 
-    bw.write("Conducting ownership analysis with allocation depth = "+allocationDepth+"\n");
-    bw.write(timeReport+"\n");
+    if( !tabularOutput ) {
+      bw.write("Conducting ownership analysis with allocation depth = "+allocationDepth+"\n");
+      bw.write(timeReport+"\n");
+    }
+    
+    int numAlias = 0;
 
     // look through every task for potential aliases
     Iterator taskItr = state.getTaskSymbolTable().getDescriptorsIterator();
     while( taskItr.hasNext() ) {
       TaskDescriptor td = (TaskDescriptor) taskItr.next();
 
-      bw.write("\n---------"+td+"--------\n");
+      if( !tabularOutput ) {
+        bw.write("\n---------"+td+"--------\n");
+      }
 
       HashSet<AllocationSite> allocSites = getFlaggedAllocationSitesReachableFromTask(td);
 
       Set<HeapRegionNode> common;
-
+      
       // for each task parameter, check for aliases with
       // other task parameters and every allocation site
       // reachable from this task
@@ -152,11 +163,15 @@ public class OwnershipAnalysis {
 	  common = createsPotentialAliases(td, i, j);
 	  if( !common.isEmpty() ) {
 	    foundSomeAlias = true;
-	    bw.write("Potential alias between parameters "+i+" and "+j+".\n");
-	    bw.write(prettyPrintNodeSet( common )+"\n" );
+            if( !tabularOutput ) {
+              bw.write("Potential alias between parameters "+i+" and "+j+".\n");
+              bw.write(prettyPrintNodeSet( common )+"\n" );
+            } else {
+              ++numAlias;
+            }
 	  }
 	}
-
+        
[…]

### 2009-10-08 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -7,6 +7,11 @@ import java.io.*;
 
 public class OwnershipGraph {
 
+  // use to disable improvements for comparison
+  protected static final boolean DISABLE_STRONG_UPDATES = false;
+  protected static final boolean DISABLE_GLOBAL_SWEEP   = false;
+
+
   private int allocationDepth;
   private TypeUtil typeUtil;
 
@@ -402,8 +407,10 @@ public class OwnershipGraph {
 	      (hrnX.isSingleObject() && lnX.getNumReferencees() == 1)    // case 2
 	      )
 	  ) {
-	strongUpdate = true;
-	clearReferenceEdgesFrom( hrnX, f.getType(), f.getSymbol(), false );
+        if( !DISABLE_STRONG_UPDATES ) {
+          strongUpdate = true;
+          clearReferenceEdgesFrom( hrnX, f.getType(), f.getSymbol(), false );
+        }
       }
     }
     
@@ -514,8 +521,10 @@ public class OwnershipGraph {
 
     // if there was a strong update, make sure to improve
     // reachability with a global sweep
-    if( strongUpdate ) {      
-      globalSweep();
+    if( strongUpdate ) {    
+      if( !DISABLE_GLOBAL_SWEEP ) {
+        globalSweep();
+      }
     }
   }
 
@@ -2091,8 +2100,9 @@ public class OwnershipGraph {
 	  if( (hrn.getNumReferencers()                                == 1) || // case 1
 	      (hrn.isSingleObject() && argLabel_i.getNumReferencees() == 1)    // case 2	     	     
 	    ) {
-	    
-	    effectCalleeStrongUpdates( paramIndex, ogCallee, hrn );
+	    if( !DISABLE_STRONG_UPDATES ) {
+              effectCalleeStrongUpdates( paramIndex, ogCallee, hrn );
+            }
 	  }
 	}
       }
@@ -3025,8 +3035,9 @@ public class OwnershipGraph {
 
 
     // improve reachability as much as possible
-    globalSweep();
-
+    if( !DISABLE_GLOBAL_SWEEP ) {
+      globalSweep();
+    }
 
 
     if( mc.getDescriptor().getSymbol().equals( debugCaller ) &&
@@ -4249,7 +4260,9 @@ public class OwnershipGraph {
     Set<HeapRegionNode> common = new HashSet<HeapRegionNode>();
     if( aliasDetected ) {
[…]

### 2009-10-08 Robust/src/Benchmarks/Ownership/makeTable.sh

@@ -1,0 +1,119 @@
+#!/bin/bash
+
+NAME[0]=Bank
+BDIR[0]=BankApp
+
+NAME[1]=Chat
+BDIR[1]=ChatTag
+
+NAME[2]=Conglomerator
+BDIR[2]=Conglomerator/Tag
+
+NAME[3]=jHTTPp2
+BDIR[3]=Jhttpp2/BR
+
+NAME[4]=MapReduce1
+BDIR[4]=MapReduce/Tag
+
+NAME[5]=MultiGame
+BDIR[5]=MMG/Tag
+
+NAME[6]=Performance
+BDIR[6]=Performance
+
+NAME[7]=PERT
+BDIR[7]=PERT/Tag
+
+NAME[8]=FilterBank
+BDIR[8]=Scheduling/FilterBank
+
+NAME[9]=Fractal
+BDIR[9]=Scheduling/Fractal
+
+NAME[10]=MolDynamics
+BDIR[10]=Scheduling/JGFMolDyn
+
+NAME[11]=MonteCarlo
+BDIR[11]=Scheduling/JGFMonteCarlo
+
+NAME[12]=Series
+BDIR[12]=Scheduling/JGFSeries
+
+NAME[13]=KMeans
+BDIR[13]=Scheduling/KMeans
+
+NAME[14]=MapReduce2
+BDIR[14]=Scheduling/MapReduce
+
+NAME[15]=FluidAnimate
+BDIR[15]=Scheduling/PSFluidAnimate
+
+NAME[16]=Spider1
+BDIR[16]=Spider/BR
+
+NAME[17]=Spider2
+BDIR[17]=Spider/BRTag
+
+NAME[18]=TileSearch
+BDIR[18]=TileSearch/Tag
+
+NAME[19]=TicTacToe
+BDIR[19]=TTTTag
+
+NAME[20]=WebServer1
+BDIR[20]=WebServer
+
+NAME[21]=WebServer2
+BDIR[21]=WebServerTag
+
+NUMBENCHMARKS=22
+
+
+
+###########################
+# No need to modify below!
+###########################
+
+BENCHTOP=~/research/Robust/src/Benchmarks
+BENCHSUM=$BENCHTOP/Ownership
+
+TABFILE=tabResults.tex
+rm -f $TABFILE
+touch $TABFILE
+echo '\begin{tabular}{|l|l|r|r|r|}'                        >> $TABFILE
+echo '\hline'                                              >> $TABFILE
[…]

### 2009-10-08 Robust/src/IR/State.java

@@ -66,6 +66,7 @@ public class State {
   public boolean OWNERSHIPWRITEDOTS=false;
   public boolean OWNERSHIPWRITEALL=false;
   public String OWNERSHIPALIASFILE=null;
+  public boolean OWNERSHIPALIASTAB=false;
   public boolean OPTIONAL=false;
   public boolean ARRAYBOUNDARYCHECK=true;
   public boolean RAW=false;

### 2009-10-08 Robust/src/Main/Main.java

@@ -139,8 +139,12 @@ public class Main {
 	if (args[++i].equals("all")) {
 	  state.OWNERSHIPWRITEALL=true;
 	}
-      } else if (option.equals("-ownaliasfile"))
+      } else if (option.equals("-ownaliasfile")) {
 	state.OWNERSHIPALIASFILE=args[++i];
+      } else if (option.equals("-ownaliasfiletab")) {
+	state.OWNERSHIPALIASFILE=args[++i];
+        state.OWNERSHIPALIASTAB=true;
+      }
       else if (option.equals("-optional"))
 	state.OPTIONAL=true;
       else if (option.equals("-optimize"))

### 2009-10-08 Robust/src/Tests/OwnershipAnalysisTest/proveStrongAndGlobal/test.java

@@ -1,0 +1,66 @@
+
+public class Parameter {
+  flag w;
+  int a;
+  int b;
+  Foo f;
+  Foo g;
+  Parameter p;
+  Parameter q;
+  public Parameter() {}
+}
+
+public class Foo {
+  Foo f;
+  Foo g;
+  Parameter p;
+  Parameter q;
+  public Foo() {}
+  void noFlaggedAlias() {
+    this.f.p = new Parameter();
+  }
+}
+
+task Startup( StartupObject s{ initialstate } ) {
+  Parameter p0 = new Parameter();
+  taskexit( s{ !initialstate } );
+}
+
+task noAliasAlways( Parameter p0{ w }, Parameter p1{ !w } ) {
+  p0.f = new Foo();
+  p1.g = new Foo();
+  taskexit( p0{ !w }, p1{ w } );
+}
+
+task noAliasWithStrong( Parameter p0{ w }, Parameter p1{ !w } ) {
+  p0.f = new Foo();
+  p1.g = p0.f;
+  p1.g = new Foo();
+  taskexit( p0{ !w }, p1{ w } );
+}
+
+task noAliasWithGlobal( Parameter p0{ w }, Parameter p1{ !w } ) {
+  Foo f0 = new Foo();
+  f0.f = new Foo();
+
+  f0.p = p0;
+  f0.f.p = p1;
+
+  f0.noFlaggedAlias();
+
+  taskexit( p0{ !w }, p1{ w } );
+}
+
+task noAliasWithGlobalAndStrong( Parameter p0{ w }, Parameter p1{ !w } ) {
+  p0.f = new Foo();
+  p0.f.f = new Foo();
+  p0.f.f.p = new Parameter();
+
+  p1.f = p0.f;
+  p1.f.f.p = new Parameter();
+
+  p0.f.f = null;
+  p0.f = null;
+
+  taskexit( p0{ !w }, p1{ w } );
+}

### 2009-10-08 Robust/src/ClassLibrary/JavaDSM/GlobalString.java
global classes

@@ -1,0 +1,129 @@
+public class GlobalString {
+  char value[];
+  int count;
+  int offset;
+
+  public GlobalString() {
+  }
+
+  public GlobalString(String str) {
+		atomic {
+			value = global new char[str.count];
+			for(int i =0; i< str.count;i++) {
+				value[i] = str.value[i+str.offset];
+			}
+		  count = str.count;
+			offset = 0;
+		}
+  }
+
+	public GlobalString(GlobalString gstr) {
+		atomic {
+			this.value = gstr.value;
+			this.count = gstr.count;
+			this.offset = gstr.offset;
+		}
+	}
+
+	public GlobalString(GlobalStringBuffer gsb) {
+		atomic {
+			value = global new char[gsb.length()];
+			count = gsb.length();
+			offset = 0;
+			for (int i = 0; i < count; i++) 
+				value[i] = gsb.value[i];
+		}
+	}
+
+	public static char[] toLocalCharArray(GlobalString str) {
+		char[] c;
+		int length;
+
+		atomic { 
+			length = str.length();
+		}
+
+		c = new char[length];
+
+		atomic {
+			for (int i = 0; i < length; i++) {
+				c[i] = str.value[i+str.offset];
+			}
+		}
+		return c;
+	}
+
+	public String toLocalString() {
+		return new String(toLocalCharArray(this));
+	}
+
+	public int length() {
+		return count;
+	}
+
+	public int indexOf(int ch, int fromIndex) {
+		for (int i = fromIndex; i < count; i++)
+			if (this.charAt(i) == ch) 
+				return i;
+		return -1;
+	}
+
+	public int lastindexOf(int ch) {
+		return this.lastindexOf(ch, count - 1);
+	}
+
+	public int lastindexOf(int ch, int fromIndex) {
+		for (int i = fromIndex; i > 0; i--) 
+			if (this.charAt(i) == ch) 
+				return i;
+		return -1;
+	}
+
+	public char charAt(int i) {
+		return value[i+offset];
+	}
+
+	public int indexOf(GlobalString str) {
+		return this.indexOf(str, 0);
+	}
+
+	public int indexOf(GlobalString str, int fromIndex) {
+		if (fromIndex < 0) 
+			fromIndex = 0;
+		for (int i = fromIndex; i <= (count-str.count); i++)
+			if (regionMatches(i, str, 0, str.count)) 
+				return i;
+		return -1;
+	}	
+
[…]

### 2009-10-08 Robust/src/ClassLibrary/JavaDSM/GlobalStringBuffer.java

@@ -1,0 +1,124 @@
+public class GlobalStringBuffer {
+  char value[];
+  int count;
+  //    private static final int DEFAULTSIZE=16;
+
+  public GlobalStringBuffer(String str) {
+		GlobalString gstr;
+
+		atomic {
+			gstr = global new GlobalString(str);
+		}
+		GlobalStringBuffer(gstr);
+  }
+
+	public GlobalStringBuffer(GlobalString str) {
+		atomic {
+			value = global new char[str.count+16];
+			count = str.count;
+			for (int i = 0; i < count; i++) 
+				value[i] = str.value[i+str.offset];
+		}
+	}
+
+	public GlobalStringBuffer(StringBuffer sb) {
+		atomic {
+			value = global new char[sb.count];
+			for (int i = 0; i < sb.count; i++) 
+				value[i] = sb.value[i];
+			count = sb.count;
+		}
+	}
+
+  public GlobalStringBuffer() {
+		atomic {
+			value = global new char[16];    //16 is DEFAULTSIZE
+			count = 0;
+		}
+  }
+
+  public int length() {
+    return count;
+  }
+
+  public int capacity() {
+    return value.length;
+  }
+
+  public char charAt(int x) {
+    return value[x];
+  }
+
+  public GlobalStringBuffer append(char c) {
+    return append(String.valueOf(c));
+  }
+
+  public GlobalStringBuffer append(String s) {
+		GlobalString str;
+		atomic {
+			str = global new GlobalString(s);
+		}
+		return append(str);
+  }
+
+  public GlobalStringBuffer append(GlobalString s) {
+		atomic {
+			if ((s.count+count) > value.length) {
+				// Need to allocate
+				char newvalue[] = global new char[s.count+count+16];       //16 is DEFAULTSIZE
+				for(int i = 0; i < count; i++)
+					newvalue[i] = value[i];
+				for(int i = 0; i < s.count; i++)
+					newvalue[i+count] = s.value[i+s.offset];
+				value = newvalue;
+				count += s.count;
+			} else {
+				for(int i = 0; i < s.count; i++) {
+					value[i+count] = s.value[i+s.offset];
+				}
+				count += s.count;
+			}
+		}
+    return this;
+  }
+
+  public GlobalStringBuffer append(StringBuffer s) {
+		GlobalStringBuffer gsb;
+		atomic {
+			gsb = global new GlobalStringBuffer(s);
+		}
+		return append(gsb);
+	}
+
+
[…]

### 2009-10-08 Robust/src/ClassLibrary/JavaDSM/Queue.java

@@ -1,0 +1,187 @@
+/* =============================================================================
+ *
+ * queue.java
+ *
+ * =============================================================================
+ *
+ * Copyright (C) Stanford University, 2006.  All Rights Reserved.
+ * Author: Chi Cao Minh
+ *
+ * Ported to Java
+ * Author:Alokika Dash
+ * University of California, Irvine
+ *
+ * =============================================================================
+ * 
+ * Unless otherwise noted, the following license applies to STAMP files:
+ * 
+ * Copyright (c) 2007, Stanford University
+ * All rights reserved.
+ * 
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions are
+ * met:
+ * 
+ *     * Redistributions of source code must retain the above copyright
+ *       notice, this list of conditions and the following disclaimer.
+ * 
+ *     * Redistributions in binary form must reproduce the above copyright
+ *       notice, this list of conditions and the following disclaimer in
+ *       the documentation and/or other materials provided with the
+ *       distribution.
+ * 
+ *     * Neither the name of Stanford University nor the names of its
+ *       contributors may be used to endorse or promote products derived
+ *       from this software without specific prior written permission.
+ * 
+ * THIS SOFTWARE IS PROVIDED BY STANFORD UNIVERSITY ``AS IS'' AND ANY
+ * EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+ * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR
+ * PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL STANFORD UNIVERSITY BE LIABLE
+ * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+ * CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+ * SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
[…]

### 2009-10-21 Robust/src/Analysis/Liveness.java
Added feature for nullfying dead variables, which didn't change sharing for benchmarks.  It is left in, but commented out, until we decide we need it.

@@ -67,4 +67,19 @@ public class Liveness {
     }
     return liveoutmap;
   }
+
+
+  // Also allow an instantiation of this object that memoizes results
+  protected Hashtable< FlatMethod, Hashtable< FlatNode, Set<TempDescriptor> > > fm2liveMap;
+
+  public Liveness() {
+    fm2liveMap = new Hashtable< FlatMethod, Hashtable< FlatNode, Set<TempDescriptor> > >();
+  }
+
+  public Set<TempDescriptor> getLiveInTemps( FlatMethod fm, FlatNode fn ) {
+    if( !fm2liveMap.containsKey( fm ) ) {
+      fm2liveMap.put( fm, Liveness.computeLiveTemps( fm ) );
+    }
+    return fm2liveMap.get( fm ).get( fn );
+  }
 }

### 2009-10-21 Robust/src/Analysis/MLP/MLPAnalysis.java

@@ -1,6 +1,7 @@
 package Analysis.MLP;
 
 import Analysis.CallGraph.*;
+import Analysis.Liveness;
 import Analysis.OwnershipAnalysis.*;
 import IR.*;
 import IR.Flat.*;
@@ -199,7 +200,7 @@ public class MLPAnalysis {
     
     // disjoint analysis with a set of flagged allocation sites of live-in variable
 	try {
-		OwnershipAnalysis oa2 = new OwnershipAnalysis(state, tu, callGraph,
+	  OwnershipAnalysis oa2 = new OwnershipAnalysis(state, tu, callGraph, new Liveness(),
 				state.OWNERSHIPALLOCDEPTH, false,
 				false, state.OWNERSHIPALIASFILE,
 				state.METHODEFFECTS,

### 2009-10-21 Robust/src/Analysis/OwnershipAnalysis/OwnershipAnalysis.java

@@ -1,6 +1,7 @@
 package Analysis.OwnershipAnalysis;
 
 import Analysis.CallGraph.*;
+import Analysis.Liveness;
 import IR.*;
 import IR.Flat.*;
 import IR.Tree.Modifiers;
@@ -315,6 +316,7 @@ public class OwnershipAnalysis {
   // data from the compiler
   public State     state;
   public CallGraph callGraph;
+  public Liveness  liveness;
   public TypeUtil  typeUtil;
   public int       allocationDepth;
 
@@ -393,27 +395,29 @@ public class OwnershipAnalysis {
   public OwnershipAnalysis(State state,
                            TypeUtil tu,
                            CallGraph callGraph,
+			   Liveness liveness,
                            int allocationDepth,
                            boolean writeDOTs,
                            boolean writeAllDOTs,
                            String aliasFile) throws java.io.IOException {
 	  
 	  this.methodEffects = false;
-	  init(state,tu,callGraph,allocationDepth,writeDOTs,writeAllDOTs,aliasFile);
+	  init(state,tu,callGraph,liveness,allocationDepth,writeDOTs,writeAllDOTs,aliasFile);
 	  
   }
   
   public OwnershipAnalysis(State state,
-          TypeUtil tu,
-          CallGraph callGraph,
-          int allocationDepth,
-          boolean writeDOTs,
-          boolean writeAllDOTs,
-          String aliasFile,
-          boolean methodEffects) throws java.io.IOException {
+			   TypeUtil tu,
+			   CallGraph callGraph,
+			   Liveness liveness,
+			   int allocationDepth,
+			   boolean writeDOTs,
+			   boolean writeAllDOTs,
+			   String aliasFile,
+			   boolean methodEffects) throws java.io.IOException {
 	  
 	  this.methodEffects = methodEffects;
-	  init(state,tu,callGraph,allocationDepth,writeDOTs,writeAllDOTs,aliasFile);
+	  init(state,tu,callGraph,liveness,allocationDepth,writeDOTs,writeAllDOTs,aliasFile);
 	  
   }
   
@@ -422,6 +426,7 @@ public class OwnershipAnalysis {
 			State state,
 			TypeUtil tu,
 			CallGraph callGraph,
+			Liveness liveness,
 			int allocationDepth,
 			boolean writeDOTs,
 			boolean writeAllDOTs,
@@ -432,24 +437,26 @@ public class OwnershipAnalysis {
 
 		this.methodEffects = methodEffects;
[…]

### 2009-10-21 Robust/src/Analysis/OwnershipAnalysis/OwnershipGraph.java

@@ -75,6 +75,9 @@ public class OwnershipGraph {
   public Hashtable<Integer, TokenTuple> paramIndex2paramTokenSecondaryStar;
 
 
+
+
+
   public OwnershipGraph() {
 
     id2hrn                    = new Hashtable<Integer,        HeapRegionNode>();
@@ -299,6 +302,34 @@ public class OwnershipGraph {
   //  of the nodes and edges involved.
   //
   ////////////////////////////////////////////////////
+
+  public void nullifyDeadVars( Set<TempDescriptor> liveIn ) {
+
+    // make a set of the temps that are out of scope, don't
+    // consider them when nullifying dead in-scope variables
+    Set<TempDescriptor> outOfScope = new HashSet<TempDescriptor>();
+    outOfScope.add( tdReturn );
+    outOfScope.add( tdAliasBlob );
+    outOfScope.addAll( paramIndex2tdQ.values() );
+    outOfScope.addAll( paramIndex2tdR.values() );    
+    
+    Iterator varItr = td2ln.entrySet().iterator();
+    while( varItr.hasNext() ) {
+      Map.Entry      me = (Map.Entry)      varItr.next();
+      TempDescriptor td = (TempDescriptor) me.getKey();
+      LabelNode      ln = (LabelNode)      me.getValue();
+
+      // if this variable is not out-of-scope or live
+      // in graph, nullify its references to anything
+      if( !outOfScope.contains( td ) &&
+	  !liveIn.contains( td ) 
+	  ) {
+	clearReferenceEdgesFrom( ln, null, null, true );
+      }
+    }
+  }
+
+
   public void assignTempXEqualToTempY(TempDescriptor x,
                                       TempDescriptor y) {
 

### 2009-10-21 Robust/src/Main/Main.java

@@ -43,6 +43,7 @@ import Analysis.FlatIRGraph.FlatIRGraph;
 import Analysis.OwnershipAnalysis.OwnershipAnalysis;
 import Analysis.MLP.MLPAnalysis;
 import Analysis.Loops.*;
+import Analysis.Liveness;
 import IR.MethodDescriptor;
 import IR.Flat.FlatMethod;
 import Interface.*;
@@ -347,9 +348,11 @@ public class Main {
     
     if (state.OWNERSHIP && !state.MLP) {
       CallGraph callGraph = new CallGraph(state);
+      Liveness liveness = new Liveness();
       OwnershipAnalysis oa = new OwnershipAnalysis(state,
                                                    tu,
                                                    callGraph,
+						   liveness,
                                                    state.OWNERSHIPALLOCDEPTH,
                                                    state.OWNERSHIPWRITEDOTS,
                                                    state.OWNERSHIPWRITEALL,
@@ -359,9 +362,11 @@ public class Main {
 
     if (state.MLP) {
       CallGraph callGraph = new CallGraph(state);
+      Liveness liveness = new Liveness();
       OwnershipAnalysis oa = new OwnershipAnalysis(state,
                                                    tu,
                                                    callGraph,
+						   liveness,
 						   state.OWNERSHIPALLOCDEPTH,
                                                    state.OWNERSHIPWRITEDOTS,
                                                    state.OWNERSHIPWRITEALL,
@@ -406,9 +411,11 @@ public class Main {
       if (state.SCHEDULING) {
 	// Use ownership analysis to get alias information
 	CallGraph callGraph = new CallGraph(state);
+	Liveness liveness = new Liveness();
 	OwnershipAnalysis oa = new OwnershipAnalysis(state,
 	                                             tu,
 	                                             callGraph,
+						     liveness,
 	                                             state.OWNERSHIPALLOCDEPTH,
 	                                             state.OWNERSHIPWRITEDOTS,
 	                                             state.OWNERSHIPWRITEALL,

### 2009-10-21 Robust/src/Analysis/Scheduling/ScheduleAnalysis.java
change to use static mapping of core # and block # in multicore garbage modul

@@ -395,7 +395,8 @@ public class ScheduleAnalysis {
                       (cdname.equals("Fractal")) ||
                       (cdname.equals("KMeans")) || 
                       (cdname.equals("ZTransform")) ||
-											(cdname.equals("TestRunner"))) {
+											(cdname.equals("TestRunner")) || 
+											(cdname.equals("LinkList"))) {
                     newRate = this.coreNum;
                   } else if(cdname.equals("SentenceParser")) {
                     newRate = 4;

### 2009-10-21 Robust/src/Runtime/multicoregarbage.c

@@ -48,16 +48,17 @@ int gclobjtailindex2=0;
 struct lobjpointerblock *gclobjspare=NULL;
 
 #ifdef GC_DEBUG
+// dump whole mem in blocks
 inline void dumpSMem() {
 	int block = 0;
 	int sblock = 0;
 	int j = 0;
 	int i = 0;
-	bool reverse = false;
 	int coren = 0;
 	int x = 0;
 	int y = 0;
 	tprintf("Dump shared mem: \n");
+	// reserved blocks for sblocktbl
 	tprintf("++++ reserved sblocks ++++ \n");
 	for(i=BAMBOO_BASE_VA; i<gcbaseva; i+= 4*16) {
 		tprintf("0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x 0x%08x \n",
@@ -68,71 +69,34 @@ inline void dumpSMem() {
 	}
 	sblock = gcreservedsb;
 	bool advanceblock = false;
+	// remaining memory
 	for(i=gcbaseva;i<BAMBOO_BASE_VA+BAMBOO_SHARED_MEM_SIZE;i+=4*16){
 		advanceblock = false;
+		// computing sblock # and block #, core coordinate (x,y) also
 		if(j%((BAMBOO_SMEM_SIZE)/(4*16)) == 0) {
+			// finished a sblock
 			if(j < ((BAMBOO_LARGE_SMEM_BOUND)/(4*16))) {
 				if((j > 0) && (j%((BAMBOO_SMEM_SIZE_L)/(4*16)) == 0)) {
+					// finished a block
 					block++;
 					advanceblock = true;
 				}
 			} else {
+				// finished a block
 				block++;
 				advanceblock = true;
 			}
+			// compute core #
 			if(advanceblock) {
-				if(block%NUMCORES == 0) {
-					reverse = !reverse;
-				} else {
-					if(((!reverse) && (y%2)) || (reverse && ((y%2)==0))) {
-						if((x == 0) || ((x==1)&&(y==6))){
-							if(reverse) {
-								if(coren > 48) {
-									coren -= bamboo_width - 1;
-								} else {
-									coren -= bamboo_width;
-								}
-							} else {
-								if(coren > 47) {
[…]

### 2009-10-21 Robust/src/Runtime/multicoregarbage.h

@@ -1,6 +1,7 @@
 #ifndef MULTICORE_GARBAGE_H
 #define MULTICORE_GARBAGE_H
 #include "multicoregc.h"
+#include "multicorehelper.h"  // for mappins between core # and block #
 #include "structdefs.h"
 
 #ifndef bool
@@ -45,7 +46,7 @@ int gcself_numreceiveobjs;
 INTPTR gcheaptop;
 int gcloads[NUMCORES];
 int gctopcore; // the core host the top of the heap
-bool gcheapdirection; // 0: decrease; 1: increase
+int gctopblock; // the number of current top block
 
 int gcnumlobjs;
 
@@ -82,6 +83,8 @@ int gcbaseva; // base va for shared memory without reserved sblocks
 #define ALIGNSIZE(s, as) \
 	(*((int*)as)) = (((s) & (~(BAMBOO_CACHE_LINE_MASK))) + (BAMBOO_CACHE_LINE_SIZE))
 
+// mapping of pointer to block # (start from 0), here the block # is the global
+// index
 #define BLOCKINDEX(p, b) \
   { \
 		int t = (p) - gcbaseva; \
@@ -92,8 +95,22 @@ int gcbaseva; // base va for shared memory without reserved sblocks
 		} \
 	}
 
+// mapping of pointer to core #
+#define RESIDECORE(p, c) \
+{ \
+	if(1 == (NUMCORES)) { \
+		(*((int*)c)) = 0; \
+	} else {\
+		int b; \
+		BLOCKINDEX((p), &b); \
+		(*((int*)c)) = gc_block2core[(b%124)]; \
+	}\
+}
+
+#if 0
+// mapping of pointer to host core (x,y)
 #define RESIDECORE(p, x, y) \
-	{ \
+  { \
 		if(1 == (NUMCORES)) { \
 			(*((int*)x)) = 0; \
 			(*((int*)y)) = 0; \
@@ -126,8 +143,12 @@ int gcbaseva; // base va for shared memory without reserved sblocks
 			} \
 		} \
 	}
+#endif
 
 // NOTE: n starts from 0
+// mapping of heaptop (how many bytes there are in the local heap) to the number of
+// the block
+// the number of the block indicates that the block is the xth block on the local heap
 #define NUMBLOCKS(s, n) \
 	if(s < (BAMBOO_SMEM_SIZE_L)) { \
 		(*((int*)(n))) = 0; \
@@ -142,6 +163,9 @@ int gcbaseva; // base va for shared memory without reserved sblocks
[…]

### 2009-10-21 Robust/src/Runtime/multicorehelper.h

@@ -1,0 +1,22 @@
+#ifndef MULTICORE_HELPER_H
+#define MULTICORE_HELPER_H
+
+static int gc_core2block[124] = {0,123,  15,108,  16,107,  31,92,  32,91,  47,76,    
+                                 1,122,  14,109,  17,106,  30,93,  33,90,  46,77,  48,75,  61,62,
+                                 2,121,  13,110,  18,105,  29,94,  34,89,  45,78,  49,74,  60,63,
+                                 3,120,  12,111,  19,104,  28,95,  35,88,  44,79,  50,73,  59,64,
+                                 4,119,  11,112,  20,103,  27,96,  36,87,  43,80,  51,72,  58,65,
+                                 5,118,  10,113,  21,102,  26,97,  37,86,  42,81,  52,71,  57,66,
+                                 6,117,   9,114,  22,101,  25,98,  38,85,  41,82,  53,70,  56,67,
+                                 7,116,   8,115,  23,100,  24,99,  39,84,  40,83,  54,69,  55,68};
+
+static int gc_block2core[124] = { 0,  6, 14, 22, 30, 38, 46, 54, 55, 47, 39, 31, 23, 15,  7,  1,
+                                  2,  8, 16, 24, 32, 40, 48, 56, 57, 49, 41, 33, 25, 17,  9,  3,
+                                  4, 10, 18, 26, 34, 42, 50, 58, 59, 51, 43, 35, 27, 19, 11,  5,
+                                     12, 20, 28, 36, 44, 52, 60, 61, 53, 45, 37, 29, 21, 13,    
+                                     13, 21, 29, 37, 45, 53, 61, 60, 52, 44, 36, 28, 20, 12,    
+                                  5, 11, 19, 27, 35, 43, 51, 59, 58, 50, 42, 34, 26, 18, 10,  4,
+                                  3,  9, 17, 25, 33, 41, 49, 57, 56, 48, 40, 32, 24, 16,  8,  2,
+                                  1,  7, 15, 23, 31, 39, 47, 55, 54, 46, 38, 30, 22, 14,  6,  0};
+
+#endif // MULTICORE_HELPER_H

### 2009-10-21 Robust/src/Runtime/multicoretask.c

@@ -88,7 +88,7 @@ void initruntimedata() {
 	gcnumlobjs = 0;
 	gcheaptop = 0;
 	gctopcore = 0;
-	gcheapdirection = 1;
+	gctopblock = 0;
 	gcmovestartaddr = 0;
 	gctomove = false;
 	gcmovepending = 0;

### 2010-04-05 Robust/src/Tests/mlp/stephen/Test.java
Updated Test.java to working condition (parallelized)

@@ -25,20 +25,22 @@ public class Test
         {
 		int innerSum = 0;
 		
-		rblock a {
+		sese a 
+		{
 		
-		int oppositeNum = MAX - i;
+			int oppositeNum = MAX - i;
         		
-	        if(isPrime(i))
-	        	innerSum += i;
+	        	if(isPrime(i))
+	        		innerSum += i;
 	        	
-	        if(i != oppositeNum && isPrime(oppositeNum))
-	        	innerSum += oppositeNum;
-	    }
+	        	if(i != oppositeNum && isPrime(oppositeNum))
+	        		innerSum += oppositeNum;
+	    	}
             
-	    rblock b {
-        	sum += innerSum;
-	    }
+	    	sese b 
+		{
+        		sum += innerSum;
+	    	}
         }
 
         System.out.println("The sum of primes from 1 to " + MAX + " is " + sum + ".");

### 2010-04-05 Robust/src/Runtime/mlp_lock.h
bring last changes for proper handling 64bit before more changes are made.

@@ -4,7 +4,7 @@
 #include <stdio.h>
 #include <assert.h>
 
-#define __xg(x) ((volatile long *)(x))
+#define __xg(x) ((volatile INTPTR *)(x))
 
 #define CFENCE   asm volatile("":::"memory");
 
@@ -35,8 +35,19 @@ static inline int atomic_sub_and_test(int i, volatile int *v) {
   return c;
 }
 
+#ifdef BIT64
+static inline INTPTR LOCKXCHG(volatile INTPTR * ptr, INTPTR val){
+  INTPTR retval;
+  //note: xchgl always implies lock 
+  __asm__ __volatile__("xchgq %0,%1"
+		       : "=r"(retval)
+		       : "m"(*ptr), "0"(val)
+		       : "memory");
+  return retval;
+ 
+}
+#else
 static inline int LOCKXCHG(volatile int* ptr, int val){
-  
   int retval;
   //note: xchgl always implies lock 
   __asm__ __volatile__("xchgl %0,%1"
@@ -46,6 +57,7 @@ static inline int LOCKXCHG(volatile int* ptr, int val){
   return retval;
  
 }
+#endif
 
 /*
 static inline int write_trylock(volatile int *lock) {
@@ -58,16 +70,17 @@ static inline int write_trylock(volatile int *lock) {
 }
 */
 
-static inline int CAS(volatile int* mem, int cmp, int val){
-  int prev;
-  asm volatile ("lock; cmpxchgl %1, %2"             
-		: "=a" (prev)               
-		: "r" (val), "m" (*(mem)), "0"(cmp) 
-		: "memory", "cc");
+#ifdef BIT64
+static inline INTPTR CAS(volatile void *ptr, unsigned INTPTR old, unsigned INTPTR new){
+  unsigned INTPTR prev;
+  __asm__ __volatile__("lock; cmpxchgq %1,%2"
+		       : "=a"(prev)
+		       : "r"(new), "m"(*__xg(ptr)), "0"(old)
+		       : "memory");
   return prev;
 }
-
-static inline long CAS32(volatile void *ptr, unsigned long old, unsigned long new){
+#else
+static inline long CAS(volatile void *ptr, unsigned long old, unsigned long new){
   unsigned long prev;
   __asm__ __volatile__("lock; cmpxchgl %k1,%2"
 		       : "=a"(prev)
[…]

### 2010-04-05 Robust/src/Runtime/mlp_runtime.c

@@ -239,11 +239,11 @@ int ADDTABLE(MemoryQueue *q, REntry *r) {
   //at this point, have table
   Hashtable* table=(Hashtable*)q->tail;
   BinItem * val;
-  int key=generateKey((unsigned int)r->dynID);
+  int key=generateKey((unsigned int)(unsigned INTPTR)r->dynID);
   do {  
     val=(BinItem*)0x1;       
     BinElement* bin=table->array[key];
-    val=(BinItem*)LOCKXCHG((unsigned int*)&(bin->head), (unsigned int)val);//note...talk to me about optimizations here. 
+    val=(BinItem*)LOCKXCHG((unsigned INTPTR*)&(bin->head), (unsigned INTPTR)val);//note...talk to me about optimizations here. 
   } while(val==(BinItem*)0x1);
   //at this point have locked bin
   if (val==NULL) {
@@ -433,7 +433,7 @@ ADDVECTOR(MemoryQueue *Q, REntry *r) {
   r->vector=V;
   if (BARRIER() && V->item.status==READY) {
     void* flag=NULL;
-    flag=(void*)LOCKXCHG((unsigned int*)&(V->array[index]), (unsigned int)flag); 
+    flag=(void*)LOCKXCHG((unsigned INTPTR*)&(V->array[index]), (unsigned INTPTR)flag); 
     if (flag!=NULL) {
       if (isParent(r)) { //parent's retire immediately
         atomic_dec(&V->item.total);
@@ -466,7 +466,7 @@ ADDSCC(MemoryQueue *Q, REntry *r) {
       Q->head=(MemoryQueueItem*)S;
     }
     void* flag=NULL;
-    flag=(void*)LOCKXCHG((unsigned int*)&(S->val), (unsigned int)flag);
+    flag=(void*)LOCKXCHG((unsigned INTPTR*)&(S->val), (unsigned INTPTR)flag);
     if (flag!=NULL) {
       return READY;
     } else {
@@ -507,7 +507,7 @@ RETIREHASHTABLE(MemoryQueue *q, REntry *r) {
 }
 
 RETIREBIN(Hashtable *T, REntry *r, BinItem *b) {
-  int key=generateKey((unsigned int)r->dynID);
+  int key=generateKey((unsigned int)(unsigned INTPTR)r->dynID);
   if(isFineRead(r)) {
     atomic_dec(&b->total);
   }
[…]

### 2010-04-05 Robust/src/Tests/mlp/stephen/Test.java
Updated Test.java; it now achieves a speed-up of 8x on dc-11

@@ -16,25 +16,30 @@ public class Test
     public void doSomeWork()
     {
         int MAX = 100000;
+	int ittr = 100;
+
         long sum = 0;
         long time = System.currentTimeMillis();
         
         //I did the for loop this way so that each parallel thread would take
         //about the same time 
-        for(int i = 0; i < MAX/2 + 1; i++)
+        for(int i = 0; i < MAX/2 + 1; i += ittr)
         {
 		int innerSum = 0;
 		
 		sese a 
 		{
+		    for(int j = i; (j < i + ittr) && j < MAX/2 + 1; j++)
+			{
 		
-			int oppositeNum = MAX - i;
+			    int oppositeNum = MAX - j;
         		
-	        	if(isPrime(i))
-	        		innerSum += i;
+			    if(isPrime(j))
+	        		innerSum += j;
 	        	
-	        	if(i != oppositeNum && isPrime(oppositeNum))
+			    if(i != oppositeNum && isPrime(oppositeNum))
 	        		innerSum += oppositeNum;
+			}
 	    	}
             
 	    	sese b 
@@ -45,7 +50,7 @@ public class Test
 
         System.out.println("The sum of primes from 1 to " + MAX + " is " + sum + ".");
         System.out.println("Note: 1 is counted as a prime.");
-        System.out.println("Time Consumed (Not Parallelized): " + (System.currentTimeMillis() - time) + " ms");
+        System.out.println("Time Consumed: " + (System.currentTimeMillis() - time) + " ms");
 
     }
     

### 2010-04-05 Robust/src/Tests/mlp/stephen/Primes/Test.java
Moved Primes into its own folder

@@ -1,0 +1,77 @@
+public class Test
+{
+    //Apparently global variables are not yet supported
+    //private int MAX = 100000;
+
+    public Test(){}
+
+    public static void main(String args[]) {
+
+        System.out.println("# it starts");
+        Test t = new Test();
+        t.doSomeWork();
+
+    }
+
+    public void doSomeWork()
+    {
+        int MAX = 100000;
+	int ittr = 100;
+
+        long sum = 0;
+        long time = System.currentTimeMillis();
+        
+        //I did the for loop this way so that each parallel thread would take
+        //about the same time 
+        for(int i = 0; i < MAX/2 + 1; i += ittr)
+        {
+		int innerSum = 0;
+		
+		sese a 
+		{
+		    for(int j = i; (j < i + ittr) && j < MAX/2 + 1; j++)
+			{
+		
+			    int oppositeNum = MAX - j;
+        		
+			    if(isPrime(j))
+	        		innerSum += j;
+	        	
+			    if(i != oppositeNum && isPrime(oppositeNum))
+	        		innerSum += oppositeNum;
+			}
+	    	}
+            
+	    	sese b 
+		{
+        		sum += innerSum;
+	    	}
+        }
+
+        System.out.println("The sum of primes from 1 to " + MAX + " is " + sum + ".");
+        System.out.println("Note: 1 is counted as a prime.");
+        System.out.println("Time Consumed: " + (System.currentTimeMillis() - time) + " ms");
+
+    }
+    
+
+    private boolean isPrime(int number)
+    {
+    	//handles special cases
+        if(number < 1)
+            return false;
+
+        if (number < 3)
+        	return true;
+
+        //Tests the rest of the numbers
+        for(int i = 2; i < number; i++)
+        {
+            if(number%i == 0)
+                return false;
+        }
+        
+        return true;
+    }
+
+}

### 2010-04-05 Robust/src/Tests/mlp/stephen/Test.java
Moved Prime Program into its own folder

@@ -1,77 +1,0 @@
-public class Test
-{
-    //Apparently global variables are not yet supported
-    //private int MAX = 100000;
-
-    public Test(){}
-
-    public static void main(String args[]) {
-
-        System.out.println("# it starts");
-        Test t = new Test();
-        t.doSomeWork();
-
-    }
-
-    public void doSomeWork()
-    {
-        int MAX = 100000;
-	int ittr = 100;
-
-        long sum = 0;
-        long time = System.currentTimeMillis();
-        
-        //I did the for loop this way so that each parallel thread would take
-        //about the same time 
-        for(int i = 0; i < MAX/2 + 1; i += ittr)
-        {
-		int innerSum = 0;
-		
-		sese a 
-		{
-		    for(int j = i; (j < i + ittr) && j < MAX/2 + 1; j++)
-			{
-		
-			    int oppositeNum = MAX - j;
-        		
-			    if(isPrime(j))
-	        		innerSum += j;
-	        	
-			    if(i != oppositeNum && isPrime(oppositeNum))
-	        		innerSum += oppositeNum;
-			}
-	    	}
-            
-	    	sese b 
-		{
-        		sum += innerSum;
-	    	}
-        }
-
-        System.out.println("The sum of primes from 1 to " + MAX + " is " + sum + ".");
-        System.out.println("Note: 1 is counted as a prime.");
-        System.out.println("Time Consumed: " + (System.currentTimeMillis() - time) + " ms");
-
-    }
-    
-
-    private boolean isPrime(int number)
-    {
-    	//handles special cases
-        if(number < 1)
-            return false;
-
-        if (number < 3)
-        	return true;
-
-        //Tests the rest of the numbers
-        for(int i = 2; i < number; i++)
-        {
-            if(number%i == 0)
-                return false;
-        }
-        
-        return true;
-    }
-
-}

### 2010-04-05 Robust/src/Analysis/Disjoint/DisjointAnalysis.java
implemented stack method visit but with callees on top, something crazy is happening to sharing for ALL visit methods...

@@ -380,6 +380,13 @@ public class DisjointAnalysis {
   protected Hashtable<Descriptor, Integer> 
     mapDescriptorToPriority;
 
+  // when analyzing a method and scheduling more:
+  // remember set of callee's enqueued for analysis
+  // so they can be put on top of the callers in
+  // the stack-visit mode
+  protected Set<Descriptor>
+    calleesToEnqueue;
+
 
   // maps a descriptor to its current partial result
   // from the intraprocedural fixed-point analysis--
@@ -484,7 +491,9 @@ public class DisjointAnalysis {
     mapTypeToArrayField = 
       new Hashtable <TypeDescriptor, FieldDescriptor>();
 
-    if( state.DISJOINTDVISITSTACK ) {
+    if( state.DISJOINTDVISITSTACK ||
+        state.DISJOINTDVISITSTACKEESONTOP 
+        ) {
       descriptorsToVisitStack =
         new Stack<DescriptorQWrapper>();
     }
@@ -500,6 +509,9 @@ public class DisjointAnalysis {
     mapDescriptorToPriority =
       new Hashtable<Descriptor, Integer>();
     
+    calleesToEnqueue = 
+      new HashSet<Descriptor>();    
+
     mapDescriptorToAllocSiteSet =
     	new Hashtable<Descriptor,    HashSet<AllocSite> >();
     
@@ -549,8 +561,13 @@ public class DisjointAnalysis {
     this.snapNodeCounter         = 0; // count nodes from 0
     this.pm=new PointerMethod();
 
-    assert state.DISJOINTDVISITSTACK || state.DISJOINTDVISITPQUE;
+    assert
+      state.DISJOINTDVISITSTACK ||
+      state.DISJOINTDVISITPQUE  ||
+      state.DISJOINTDVISITSTACKEESONTOP;
     assert !(state.DISJOINTDVISITSTACK && state.DISJOINTDVISITPQUE);
+    assert !(state.DISJOINTDVISITSTACK && state.DISJOINTDVISITSTACKEESONTOP);
+    assert !(state.DISJOINTDVISITPQUE  && state.DISJOINTDVISITSTACKEESONTOP);
 	    
     // set some static configuration for ReachGraphs
     ReachGraph.allocationDepth = allocationDepth;
@@ -596,7 +613,9 @@ public class DisjointAnalysis {
 
 
   protected boolean moreDescriptorsToVisit() {
[…]

### 2010-04-05 Robust/src/Benchmarks/disjoint/genTable-all-benchmarks.sh

@@ -18,17 +18,17 @@ NAME[$num]=jHTTPp2
 BDIR[$num]=Jhttpp2/BR
 num=$[$num+1]
 
-#NAME[$num]=MapReduce
-#BDIR[$num]=MapReduce/Tag
-#num=$[$num+1]
+NAME[$num]=MapReduce1
+BDIR[$num]=MapReduce/Tag
+num=$[$num+1]
 
-#NAME[$num]=MultiGame
-#BDIR[$num]=MMG/Tag
-#num=$[$num+1]
+NAME[$num]=MultiGame
+BDIR[$num]=MMG/Tag
+num=$[$num+1]
 
-#NAME[$num]=PERT
-#BDIR[$num]=PERT/Tag
-#num=$[$num+1]
+NAME[$num]=PERT
+BDIR[$num]=PERT/Tag
+num=$[$num+1]
 
 NAME[$num]=FilterBank
 BDIR[$num]=Scheduling/FilterBank
@@ -54,24 +54,36 @@ NAME[$num]=KMeans-Bamboo
 BDIR[$num]=Scheduling/KMeans
 num=$[$num+1]
 
-#NAME[$num]=FluidAnimate
-#BDIR[$num]=Scheduling/PSFluidAnimate
-#num=$[$num+1]
+NAME[$num]=MapReduce2
+BDIR[$num]=Scheduling/MapReduce
+num=$[$num+1]
 
-NAME[$num]=Spider
+NAME[$num]=FluidAnimate
+BDIR[$num]=Scheduling/PSFluidAnimate
+num=$[$num+1]
+
+NAME[$num]=Spider1
 BDIR[$num]=Spider/BR
 num=$[$num+1]
 
-#NAME[$num]=TileSearch
-#BDIR[$num]=TileSearch/Tag
-#num=$[$num+1]
+NAME[$num]=Spider2
+BDIR[$num]=Spider/BRTag
+num=$[$num+1]
+
+NAME[$num]=TileSearch
+BDIR[$num]=TileSearch/Tag
+num=$[$num+1]
 
 NAME[$num]=TicTacToe
 BDIR[$num]=TTTTag
 num=$[$num+1]
 
-NAME[$num]=WebServer
+NAME[$num]=WebServer1
 BDIR[$num]=WebServer
+num=$[$num+1]
+
+NAME[$num]=WebServer2
+BDIR[$num]=WebServerTag
 num=$[$num+1]
 
 NAME[$num]=Tracking

### 2010-04-05 Robust/src/Benchmarks/disjoint/genTable-paper-benchmarks.sh

@@ -1,0 +1,129 @@
+#!/bin/bash
+
+num="0"
+
+NAME[$num]=Bank
+BDIR[$num]=BankApp
+num=$[$num+1]
+
+NAME[$num]=Chat
+BDIR[$num]=ChatTag
+num=$[$num+1]
+
+NAME[$num]=WebPortal
+BDIR[$num]=Conglomerator/Tag
+num=$[$num+1]
+
+NAME[$num]=jHTTPp2
+BDIR[$num]=Jhttpp2/BR
+num=$[$num+1]
+
+#NAME[$num]=MapReduce
+#BDIR[$num]=MapReduce/Tag
+#num=$[$num+1]
+
+NAME[$num]=MultiGame
+BDIR[$num]=MMG/Tag
+num=$[$num+1]
+
+#NAME[$num]=PERT
+#BDIR[$num]=PERT/Tag
+#num=$[$num+1]
+
+NAME[$num]=FilterBank
+BDIR[$num]=Scheduling/FilterBank
+num=$[$num+1]
+
+NAME[$num]=Fractal
+BDIR[$num]=Scheduling/Fractal
+num=$[$num+1]
+
+NAME[$num]=MolDyn
+BDIR[$num]=Scheduling/JGFMolDyn
+num=$[$num+1]
+
+NAME[$num]=MonteCarlo
+BDIR[$num]=Scheduling/JGFMonteCarlo
+num=$[$num+1]
+
+NAME[$num]=Series
+BDIR[$num]=Scheduling/JGFSeries
+num=$[$num+1]
+
+NAME[$num]=KMeans-Bamboo
+BDIR[$num]=Scheduling/KMeans
+num=$[$num+1]
+
+NAME[$num]=FluidAnimate
+BDIR[$num]=Scheduling/PSFluidAnimate
+num=$[$num+1]
+
+NAME[$num]=Spider
+BDIR[$num]=Spider/BR
+num=$[$num+1]
+
+#NAME[$num]=TileSearch
+#BDIR[$num]=TileSearch/Tag
+#num=$[$num+1]
+
+#NAME[$num]=TicTacToe
+#BDIR[$num]=TTTTag
+#num=$[$num+1]
+
+NAME[$num]=WebServer
+BDIR[$num]=WebServer
+num=$[$num+1]
+
+NAME[$num]=Tracking
+BDIR[$num]=Scheduling/Tracking
+num=$[$num+1]
+
+
+
+###########################
+# No need to modify below!
[…]

### 2010-04-05 Robust/src/IR/State.java

@@ -85,6 +85,7 @@ public class State {
   public boolean DISJOINTSNAPSTOPAFTER=false;
   public boolean DISJOINTDVISITSTACK=true;
   public boolean DISJOINTDVISITPQUE=false;
+  public boolean DISJOINTDVISITSTACKEESONTOP=false;
 
   public boolean OPTIONAL=false;
   public boolean ARRAYPAD=false;

### 2010-04-05 Robust/src/Main/Main.java

@@ -221,12 +221,19 @@ public class Main {
         state.DISJOINTRELEASEMODE = true;        
 
       } else if( option.equals( "-disjoint-dvisit-stack" ) ) {
-        state.DISJOINTDVISITSTACK = true;      
-        state.DISJOINTDVISITPQUE  = false;
+        state.DISJOINTDVISITSTACK         = true;      
+        state.DISJOINTDVISITPQUE          = false;
+        state.DISJOINTDVISITSTACKEESONTOP = false;
 
       } else if( option.equals( "-disjoint-dvisit-pqueue" ) ) {
-        state.DISJOINTDVISITPQUE  = true;
-        state.DISJOINTDVISITSTACK = false;      
+        state.DISJOINTDVISITPQUE          = true;
+        state.DISJOINTDVISITSTACK         = false;
+        state.DISJOINTDVISITSTACKEESONTOP = false;
+
+      } else if( option.equals( "-disjoint-dvisit-stack-callees-on-top" ) ) {
+        state.DISJOINTDVISITSTACKEESONTOP = true;
+        state.DISJOINTDVISITPQUE          = false;
+        state.DISJOINTDVISITSTACK         = false;      
       }
       
 

### 2010-04-05 Robust/src/Analysis/Disjoint/AllocSite.java
objects with bamboo-parameter flags got dropped from analysis by accident

@@ -68,7 +68,23 @@ public class AllocSite extends Canonical {
     this.allocationDepth = allocationDepth;
     this.flatNew         = flatNew;
     this.disjointId      = disjointId;
-    this.isFlagged       = disjointId != null;
+
+    // mark this allocation site as being flagged
+    // for the analysis if
+    // 1) we have a non-null disjointID (a named flagged site) 
+    // OR
+    // 2) the type is a class with Bamboo-parameter flags 
+    this.isFlagged = false;
+
+    if( disjointId != null ) {
+      this.isFlagged = true;
+
+    } else if( flatNew.getType().isClass() &&
+               flatNew.getType().getClassDesc().hasFlags()
+               ) {
+      this.isFlagged = true;
+    }
+
 
     ithOldest = new Vector<Integer>( allocationDepth );
     id        = generateUniqueAllocSiteID();

### 2010-04-06 Robust/src/Analysis/MLP/WaitingElement.java
changes for handling unresolved in-var pointer.

@@ -3,11 +3,22 @@ package Analysis.MLP;
 import java.util.HashSet;
 import java.util.Iterator;
 
+import IR.Flat.TempDescriptor;
+
 public class WaitingElement {
 
 	private int waitingID;
 	private int status;
 	private String dynID="";
+	private TempDescriptor tempDesc;
+	
+	public void setTempDesc(TempDescriptor tempDesc){
+		this.tempDesc=tempDesc;
+	}
+	
+	public TempDescriptor getTempDesc(){
+		return tempDesc;
+	}
 
 	public void setWaitingID(int waitingID) {
 		this.waitingID = waitingID;

### 2010-04-06 Robust/src/IR/Flat/BuildCode.java

@@ -3359,55 +3359,7 @@ public class BuildCode {
     //  create it's lock and take it immediately
     output.println("     pthread_mutex_init( &(seseToIssue->common.lock), NULL );");
 //    output.println("     pthread_mutex_lock( &(seseToIssue->common.lock) );");
-    
-    // count up memory conflict dependencies,
-    // eom
-	ConflictGraph graph = null;
-	FlatSESEEnterNode parent = fsen.getParent();
-	if (parent != null) {
-		if (parent.isCallerSESEplaceholder) {
-			graph = mlpa.getConflictGraphResults().get(parent.getfmEnclosing());
-		} else {
-			graph = mlpa.getConflictGraphResults().get(parent);
-		}
-	}
-	if (graph != null && graph.hasConflictEdge()) {
-		HashSet<SESELock> seseLockSet = mlpa.getConflictGraphLockMap().get(
-				graph);
-		output.println();
-		output.println("     //add memory queue element");
-		Set<WaitingElement> waitingQueueSet = graph
-				.getWaitingElementSetBySESEID(fsen.getIdentifier(),
-						seseLockSet);
-		if (waitingQueueSet.size() > 0) {
-			output.println("     {");
-			output.println("     REntry* rentry=NULL;");
-			output.println("     seseToIssue->common.rentryIdx=0;");
-			for (Iterator iterator = waitingQueueSet.iterator(); iterator
-					.hasNext();) {
-				WaitingElement waitingElement = (WaitingElement) iterator
-						.next();
-				
-				if( waitingElement.getStatus() >= ConflictNode.COARSE ){
-					output.println("     rentry=mlpCreateREntry("+ waitingElement.getStatus()+ ", seseToIssue);");
-				}else{
-					output.println("     rentry=mlpCreateFineREntry("+ waitingElement.getStatus()+ ", seseToIssue,  seseToIssue->"+ waitingElement.getDynID() + ");");	
-				}		
-				output.println("     rentry->queue=parentCommon->memoryQueueArray["+ waitingElement.getQueueID()+ "];");
-				output.println("     seseToIssue->common.rentryArray[seseToIssue->common.rentryIdx++]=rentry;");
-				output
-						.println("     if(ADDRENTRY(parentCommon->memoryQueueArray["
-								+ waitingElement.getQueueID()
-								+ "],rentry)==NOTREADY){");
-				output.println("        ++(localCount);");
-				output.println("     } ");
-				output.println();
-			}
-			output.println("     }");
-		}
[…]

### 2010-04-06 Robust/src/Runtime/mlp_runtime.c

@@ -163,6 +163,7 @@ Hashtable* createHashtable(){
     newTable->array[i]->head=NULL;
     newTable->array[i]->tail=NULL;
   }
+  newTable->unresolvedQueue=NULL;
   return newTable;
 }
 
@@ -238,6 +239,41 @@ int ADDTABLE(MemoryQueue *q, REntry *r) {
 
   //at this point, have table
   Hashtable* table=(Hashtable*)q->tail;
+  r->hashtable=table;
+  if(*(r->pointer)==0 || (*(r->pointer)!=0 && table->unresolvedQueue!=NULL)){
+     struct Queue* val;
+    // grab lock on the queue    
+    do {  
+      val=(struct Queue*)0x1;       
+      val=(struct Queue*)LOCKXCHG((unsigned INTPTR*)&(table->unresolvedQueue), (unsigned INTPTR)val);
+    } while(val==(struct Queue*)0x1);  
+
+    if(val==NULL){
+      //first case
+      if(*(r->pointer)!=0){
+	// pointer is already resolved.
+	table->unresolvedQueue=val; //released lock;
+	return ADDTABLE(q,r);
+      }
+      table->unresolvedQueue=(struct Queue*)0x1;
+      struct Queue* queue=createQueue();
+      addNewItem(queue,r);
+      atomic_inc(&table->item.total); 
+      table->unresolvedQueue=queue; // expose new queue     
+    }else{
+      if(val==NULL){
+	// someone else has already cleared all queue stuff
+	table->unresolvedQueue=val; // released lock
+	return ADDTABLE(q,r);
+      }
+      addNewItemBack(val,r);
+      atomic_inc(&table->item.total);    
+      table->unresolvedQueue=val; // released lock
+    }   
+    return NOTREADY;
+  }
+
+  r->dynID=(void*)*(r->pointer); // interim fix.
   BinItem * val;
   int key=generateKey((unsigned int)(unsigned INTPTR)r->dynID);
   do {  
@@ -247,17 +283,37 @@ int ADDTABLE(MemoryQueue *q, REntry *r) {
   } while(val==(BinItem*)0x1);
   //at this point have locked bin
   if (val==NULL) {
-    return EMPTYBINCASE(table, table->array[key], r);
+    return EMPTYBINCASE(table, table->array[key], r, TRUE);
   } else {
     if (isFineWrite(r)) {
[…]

### 2010-04-06 Robust/src/Runtime/mlp_runtime.h

@@ -58,6 +58,7 @@ typedef struct REntry_t{
   psemaphore parentStallSem;
   void* seseRec;
   void* dynID;
+  INTPTR* pointer;
 } REntry;
 
 typedef struct MemoryQueueItem_t {
@@ -82,6 +83,7 @@ typedef struct BinItem_t {
 typedef struct Hashtable_t {
   MemoryQueueItem item;
   struct BinElement_t* array[NUMBINS];
+  struct Queue*   unresolvedQueue;
 } Hashtable;
 
 typedef struct BinElement_t {
@@ -153,8 +155,10 @@ typedef struct SESEcommon_t {
 
   int numMemoryQueue;
   int rentryIdx;
+  int unresolvedRentryIdx;
   struct MemoryQueue_t** memoryQueueArray;
   struct REntry_t* rentryArray[NUMRENTRY];
+  struct REntry_t* unresolvedRentryArray[NUMRENTRY];
 
 } SESEcommon;
 

### 2010-04-06 Robust/src/IR/Flat/BuildCode.java
bug fix.

@@ -3398,49 +3398,73 @@ public class BuildCode {
   			graph = mlpa.getConflictGraphResults().get(parent);
   		}
   	}
-  	if (graph != null && graph.hasConflictEdge()) {
-  		HashSet<SESELock> seseLockSet = mlpa.getConflictGraphLockMap().get(
-  				graph);
-  		output.println();
-  		output.println("     //add memory queue element");
-  		Set<WaitingElement> waitingQueueSet = graph
-  				.getWaitingElementSetBySESEID(fsen.getIdentifier(),
-  						seseLockSet);
-  		if (waitingQueueSet.size() > 0) {
-  			output.println("     {");
-  			output.println("     REntry* rentry=NULL;");
-  			output.println("     seseToIssue->common.rentryIdx=0;");
-  			for (Iterator iterator = waitingQueueSet.iterator(); iterator
-  					.hasNext();) {
-  				WaitingElement waitingElement = (WaitingElement) iterator
-  						.next();
-  				
-  				if( waitingElement.getStatus() >= ConflictNode.COARSE ){
-  					output.println("     rentry=mlpCreateREntry("+ waitingElement.getStatus()+ ", seseToIssue);");
-  				}else{
-  					TempDescriptor td=waitingElement.getTempDesc();
-  					VariableSourceToken vst=fsen.getStaticInVarSrc(td);
-  					String srcId="SESE_"+vst.getSESE().getPrettyIdentifier()+vst.getSESE().getIdentifier()+"_"+vst.getAge();
-  					output.println("     rentry=mlpCreateFineREntry("+ waitingElement.getStatus()+ ", seseToIssue,  seseToIssue->"+ waitingElement.getDynID() + ");");
-  					output.println("     if(seseToIssue->"+ waitingElement.getDynID()+" == NULL) {");
-  					output.println("        rentry->pointer=(void*)&seseToIssue->"+srcId+"->"+waitingElement.getDynID()+";");
-  					output.println("        seseToIssue->common.unresolvedRentryArray[seseToIssue->common.unresolvedRentryIdx++]=rentry;");
-  					output.println("     }");
-  				}		
-  				output.println("     rentry->queue=parentCommon->memoryQueueArray["+ waitingElement.getQueueID()+ "];");
-  				output.println("     seseToIssue->common.rentryArray[seseToIssue->common.rentryIdx++]=rentry;");
-  				output
[…]

### 2010-04-06 Robust/src/IR/Flat/BuildCode.java
bug fixes for handling unresolved pointer.

@@ -3421,6 +3421,12 @@ public class BuildCode {
 									+ ", seseToIssue);");
 						} else {
 							TempDescriptor td = waitingElement.getTempDesc();
+								output
+										.println("     rentry=mlpCreateFineREntry("
+												+ waitingElement.getStatus()
+												+ ", seseToIssue,  seseToIssue->"
+												+ waitingElement.getDynID()
+												+ ");");
 							if (td != null) {
 								VariableSourceToken vst = fsen
 										.getStaticInVarSrc(td);
@@ -3428,12 +3434,6 @@ public class BuildCode {
 										+ vst.getSESE().getPrettyIdentifier()
 										+ vst.getSESE().getIdentifier() + "_"
 										+ vst.getAge();
-								output
-										.println("     rentry=mlpCreateFineREntry("
-												+ waitingElement.getStatus()
-												+ ", seseToIssue,  seseToIssue->"
-												+ waitingElement.getDynID()
-												+ ");");
 								output.println("     if(seseToIssue->"
 										+ waitingElement.getDynID()
 										+ " == NULL) {");

### 2010-04-06 Robust/src/Runtime/mlp_runtime.c

@@ -240,7 +240,7 @@ int ADDTABLE(MemoryQueue *q, REntry *r) {
   //at this point, have table
   Hashtable* table=(Hashtable*)q->tail;
   r->hashtable=table;
-  if(*(r->pointer)==0 || (*(r->pointer)!=0 && table->unresolvedQueue!=NULL)){
+  if(r->pointer!=0 && (*(r->pointer)==0 || (*(r->pointer)!=0 && table->unresolvedQueue!=NULL))){
      struct Queue* val;
     // grab lock on the queue    
     do {  
@@ -272,8 +272,9 @@ int ADDTABLE(MemoryQueue *q, REntry *r) {
     }   
     return NOTREADY;
   }
-
-  r->dynID=(void*)*(r->pointer); // interim fix.
+  if(r->pointer!=0){
+    r->dynID=(void*)*(r->pointer); // interim fix.
+  }
   BinItem * val;
   int key=generateKey((unsigned int)(unsigned INTPTR)r->dynID);
   do {  

### 2010-04-06 Robust/src/Benchmarks/Ownership/genTable-all-benchmarks.sh
changes to automate old and new analysis benchmark suites, want tabular output to match for easily comparisons

@@ -1,0 +1,141 @@
+#!/bin/bash
+
+num="0"
+
+NAME[$num]=Bank
+BDIR[$num]=BankApp
+num=$[$num+1]
+
+NAME[$num]=Chat
+BDIR[$num]=ChatTag
+num=$[$num+1]
+
+NAME[$num]=WebPortal
+BDIR[$num]=Conglomerator/Tag
+num=$[$num+1]
+
+NAME[$num]=jHTTPp2
+BDIR[$num]=Jhttpp2/BR
+num=$[$num+1]
+
+NAME[$num]=MapReduce1
+BDIR[$num]=MapReduce/Tag
+num=$[$num+1]
+
+NAME[$num]=MultiGame
+BDIR[$num]=MMG/Tag
+num=$[$num+1]
+
+NAME[$num]=PERT
+BDIR[$num]=PERT/Tag
+num=$[$num+1]
+
+NAME[$num]=FilterBank
+BDIR[$num]=Scheduling/FilterBank
+num=$[$num+1]
+
+NAME[$num]=Fractal
+BDIR[$num]=Scheduling/Fractal
+num=$[$num+1]
+
+NAME[$num]=MolDyn
+BDIR[$num]=Scheduling/JGFMolDyn
+num=$[$num+1]
+
+NAME[$num]=MonteCarlo
+BDIR[$num]=Scheduling/JGFMonteCarlo
+num=$[$num+1]
+
+NAME[$num]=Series
+BDIR[$num]=Scheduling/JGFSeries
+num=$[$num+1]
+
+NAME[$num]=KMeans-Bamboo
+BDIR[$num]=Scheduling/KMeans
+num=$[$num+1]
+
+NAME[$num]=MapReduce2
+BDIR[$num]=Scheduling/MapReduce
+num=$[$num+1]
+
+NAME[$num]=FluidAnimate
+BDIR[$num]=Scheduling/PSFluidAnimate
+num=$[$num+1]
+
+NAME[$num]=Spider1
+BDIR[$num]=Spider/BR
+num=$[$num+1]
+
+NAME[$num]=Spider2
+BDIR[$num]=Spider/BRTag
+num=$[$num+1]
+
+NAME[$num]=TileSearch
+BDIR[$num]=TileSearch/Tag
+num=$[$num+1]
+
+NAME[$num]=TicTacToe
+BDIR[$num]=TTTTag
+num=$[$num+1]
+
+NAME[$num]=WebServer1
[…]

### 2010-04-06 Robust/src/Benchmarks/Ownership/genTable-paper-benchmarks.sh

@@ -18,17 +18,17 @@ NAME[$num]=jHTTPp2
 BDIR[$num]=Jhttpp2/BR
 num=$[$num+1]
 
-NAME[$num]=MapReduce
-BDIR[$num]=MapReduce/Tag
-num=$[$num+1]
+#NAME[$num]=MapReduce
+#BDIR[$num]=MapReduce/Tag
+#num=$[$num+1]
 
 NAME[$num]=MultiGame
 BDIR[$num]=MMG/Tag
 num=$[$num+1]
 
-NAME[$num]=PERT
-BDIR[$num]=PERT/Tag
-num=$[$num+1]
+#NAME[$num]=PERT
+#BDIR[$num]=PERT/Tag
+#num=$[$num+1]
 
 NAME[$num]=FilterBank
 BDIR[$num]=Scheduling/FilterBank
@@ -62,13 +62,13 @@ NAME[$num]=Spider
 BDIR[$num]=Spider/BR
 num=$[$num+1]
 
-NAME[$num]=TileSearch
-BDIR[$num]=TileSearch/Tag
-num=$[$num+1]
+#NAME[$num]=TileSearch
+#BDIR[$num]=TileSearch/Tag
+#num=$[$num+1]
 
-NAME[$num]=TicTacToe
-BDIR[$num]=TTTTag
-num=$[$num+1]
+#NAME[$num]=TicTacToe
+#BDIR[$num]=TTTTag
+#num=$[$num+1]
 
 NAME[$num]=WebServer
 BDIR[$num]=WebServer
@@ -77,7 +77,6 @@ num=$[$num+1]
 NAME[$num]=Tracking
 BDIR[$num]=Scheduling/Tracking
 num=$[$num+1]
-
 
 
 
@@ -98,12 +97,10 @@ echo '\hline'                                              >> $TABFILE
 
 i="0"
 while [ $i -lt $num ]; do
-  echo ${NAME[$i]}
-
   cd $BENCHTOP/${BDIR[$i]}
   # unfortunately this echo adds an unwanted newline
   echo ${NAME[$i]} >> $BENCHSUM/$TABFILE 
-  make -f $BENCHSUM/makefile
+  make -f $BENCHSUM/makefile tabbed
   cat aliases.txt >> $BENCHSUM/$TABFILE
   make -f $BENCHSUM/makefile clean
   i=$[$i+1]

### 2010-04-06 Robust/src/Tests/mlp/Tu/test.java
First test case

@@ -1,0 +1,65 @@
+public class test {
+
+    public static void main(String args[]) {
+	System.out.println("# it starts");	
+	test t = new test();
+	t.doSomeWork();
+    }    
+    
+    public void doSomeWork(){
+	
+	int numpoints = 100000000;
+	int numberOfWorker = 10;
+	int numpointsEachWorker = numpoints/numberOfWorker;
+	int numOfPointsInCircle = 0;
+	
+	
+
+
+	double side = 10;//side of the square
+	double x_conner = 0;
+	double y_conner = 0; //lower left conner of the square
+	double midpoint = 5;//(midpoint, midpoint) = (5,5)
+	    for (int i = 0; i < numberOfWorker; i++)
+            {
+		sese parallel{
+		    //each worker has its own random object
+		    Random r = new Random();
+		    r.random_alloc();
+		    int countPointInCircle = 0;//keep track of points in circle
+                for (int j = 0; j < numpointsEachWorker; j++)
+                {
+		    int x =  (r.random_generate())%10;
+		    int y =  (r.random_generate())%10;
+		    //if the random point is outside the square then pick again
+		    while ((x > side) || (y > side))
+		    {
+			x = (r.random_generate())%10;
+			y = (r.random_generate())%10;
+		    }
+		    //calculate the distance between the random point and the center of circle
+		    double distance = (double)Math.sqrt(((x-midpoint)*(x-midpoint)) + ((y-midpoint)*(y-midpoint)));
+		    //note: each worker has one countPointInCircle variable
+                    if (distance <= 5.0) // side/2 is the radius of the circle
+		    {
+		        countPointInCircle++;
+		    }
+                }
+	    
+	    }
+	    //add all the countPointInCircle together
+             sese serial{
+		 numOfPointsInCircle += countPointInCircle;
+             }
+         }
+
+	    //calculate PI   
+            double PI = (double)(4*(double)numOfPointsInCircle)/(double)(numpoints);  
+
+	    System.out.println("PI="+PI);
+    }
+
+    public test(){}
+    
+}
+

### 2010-04-07 Robust/src/Runtime/DSTM/interface_recovery/dstm.h
two phase recovery

@@ -289,11 +289,11 @@ unsigned int updateLiveHosts();
 void updateLiveHostsList(int mid);
 int updateLiveHostsCommit();
 void receiveNewHostLists(int accept);
-void stopTransactions();
+void stopTransactions(int TRANS_FLAG);
 void sendTransList(int acceptfd);
 void receiveTransList(int acceptfd);
 int combineTransactionList(tlist_node_t* tArray,int size);
-char inspectTransaction(char control,unsigned int transid);
+char inspectTransaction(char control,unsigned int transid,char* debug,int TRANS_FLAG);
 
 void respondToLeader();
 void setLocateObjHosts();

### 2010-04-07 Robust/src/Runtime/DSTM/interface_recovery/dstmserver.c

@@ -538,7 +538,7 @@ void *dstmAccept(void *acceptfd) {
 #ifdef RECOVERY
       case REQUEST_TRANS_WAIT:
         receiveNewHostLists((int)acceptfd);        
-        stopTransactions();
+        stopTransactions(TRANS_BEFORE);
 
         response = RESPOND_TRANS_WAIT;
         send_data((int)acceptfd,&response,sizeof(char));
@@ -557,6 +557,10 @@ void *dstmAccept(void *acceptfd) {
         printf("control -> REQUEST_TRANS_LIST\n");
         sendTransList((int)acceptfd);
         receiveTransList((int)acceptfd);
+
+        pthread_mutex_lock(&liveHosts_mutex);
+        okCommit = TRANS_AFTER;
+        pthread_mutex_unlock(&liveHosts_mutex);
         break;
 
       case REQUEST_TRANS_RESTART:
@@ -960,6 +964,8 @@ int processClientReq(fixed_data_t *fixed, trans_commit_data_t *transinfo,
     return 1;
   }
 
+//  printf("%s -> Waiting for transID : %u\n",__func__,fixed->transid);
+
 	int timeout = recv_data((int)acceptfd, &control, sizeof(char));
 
 #ifdef RECOVERY
@@ -967,7 +973,7 @@ int processClientReq(fixed_data_t *fixed, trans_commit_data_t *transinfo,
     control = -1;
   }
   // check if it is allowed to commit
-  control = inspectTransaction(control,fixed->transid);
+  control = inspectTransaction(control,fixed->transid,"processClientReq",TRANS_BEFORE);
   thashInsert(fixed->transid, control);
 
 #endif
@@ -1029,10 +1035,13 @@ int processClientReq(fixed_data_t *fixed, trans_commit_data_t *transinfo,
 
   tlist_node_t* tNode = tlistSearch(transList,fixed->transid);
   tNode->status = TRANS_OK;
+  inspectTransaction(control,fixed->transid,"processClientReq",TRANS_AFTER);
 
   pthread_mutex_lock(&clearNotifyList_mutex);
   transList = tlistRemove(transList,fixed->transid);
   pthread_mutex_unlock(&clearNotifyList_mutex);
+
+  // ====================after transaction point
 
 #endif
 
@@ -1845,15 +1854,15 @@ void receiveNewHostLists(int acceptfd)
 }
 
 /* wait until all transaction waits for leader's decision */
[…]

### 2010-04-07 Robust/src/Runtime/DSTM/interface_recovery/trans.c

@@ -1154,7 +1154,7 @@ int transCommit() {
 
 #ifdef RECOVERY
   while(okCommit != TRANS_OK) {
-    printf("%s -> new Transactin is waiting\n",__func__);
+//    printf("%s -> new Transactin is waiting\n",__func__);
     sleep(2);
   }
 
@@ -1358,11 +1358,9 @@ int transCommit() {
 
 #ifdef RECOVERY
 // wait until leader fix the system
+
     if(okCommit != TRANS_OK) {
-      while(okCommit != TRANS_OK) {
-        printf("%s -> Coordinator is waiting finalResponse : %d\n",__func__,finalResponse);
-        sleep(1);
-      }
+      inspectTransaction(finalResponse,transID,"transCommit before response",TRANS_AFTER);
       finalResponse = TRANS_ABORT;
     }
 #endif
@@ -1452,8 +1450,13 @@ int transCommit() {
 	} while (treplyretry && deadmid != -1);
 
 #ifdef RECOVERY
+
+  //===========  after transaction point
   tlist_node_t* tNode = tlistSearch(transList,transID);
+  inspectTransaction(finalResponse,transID,"Coordinator",TRANS_AFTER);
+
   tNode->status = TRANS_OK;
+  finalResponse = tNode->decision;
 
   pthread_mutex_lock(&clearNotifyList_mutex);
   transList = tlistRemove(transList,transID);
@@ -1555,7 +1558,7 @@ void handleLocalReq(trans_req_data_t *tdata, trans_commit_data_t *transinfo, cha
 char doLocalProcess(char finalResponse, trans_req_data_t *tdata, trans_commit_data_t *transinfo) {
 
 #ifdef RECOVERY
-  finalResponse = inspectTransaction(finalResponse,tdata->f.transid);
+  finalResponse = inspectTransaction(finalResponse,tdata->f.transid,"Local Commit",TRANS_BEFORE);
   thashInsert(tdata->f.transid,finalResponse);
 #endif
 
@@ -1833,10 +1836,10 @@ void restoreDuplicationState(unsigned int deadHost)
 
   // clear transaction
   clearTransaction();
+//  getchar();
 
   // transfer lost objects
   duplicateLostObjects(deadHost);
-  getchar();
   // restart transactions
   restartTransactions();
 
@@ -1860,8 +1863,6 @@ void notifyRestoration()
   int sd;
   int sdlist[numHostsInSystem];
 
[…]

### 2010-04-07 Robust/src/Analysis/Disjoint/ReachGraph.java
just improved some output

@@ -2449,7 +2449,10 @@ public class ReachGraph {
 	// see what type variable we are assigning it to
 	if( !isSuperiorType( returnTemp.getType(), reCallee.getType() ) ) {
 	  System.out.println( "*** NOT EXPECTING TO SEE THIS: Throwing out "+
-                              reCallee+" for return temp "+returnTemp );
+                              reCallee+
+                              " for return temp "+returnTemp+
+                              " of type "+returnTemp.getType() 
+                              );
 	  // prune
 	  continue;
 	}	
@@ -4101,7 +4104,8 @@ public class ReachGraph {
         // not every node at an allocation is referenced
         // (think of it as garbage-collected), etc.
         if( !pruneGarbage        ||
-            hrn.isOutOfContext()
+            hrn.isOutOfContext() ||
+            (hrn.isFlagged() && hrn.getID() > 0 && !hrn.isWiped()) // a non-shadow flagged node
             ) {
           
           if( !visited.contains( hrn ) ) {

### 2010-04-07 Robust/src/Analysis/Disjoint/DisjointAnalysis.java
added compiler option to desire determinism, it currently has little effect on determinism, though, so will get back to other bugs for now

@@ -316,6 +316,10 @@ public class DisjointAnalysis {
   // run in faster mode, only when bugs wrung out!
   public static boolean releaseMode;
 
+  // use command line option to set this, analysis
+  // should attempt to be deterministic
+  public static boolean determinismDesired;
+
   // data from the compiler
   public State            state;
   public CallGraph        callGraph;
@@ -548,6 +552,7 @@ public class DisjointAnalysis {
     this.arrayReferencees        = arrayReferencees;
     this.allocationDepth         = state.DISJOINTALLOCDEPTH;
     this.releaseMode             = state.DISJOINTRELEASEMODE;
+    this.determinismDesired      = state.DISJOINTDETERMINISM;
 
     this.writeFinalDOTs          = state.DISJOINTWRITEDOTS && !state.DISJOINTWRITEALL;
     this.writeAllIncrementalDOTs = state.DISJOINTWRITEDOTS &&  state.DISJOINTWRITEALL;
@@ -773,7 +778,13 @@ public class DisjointAnalysis {
     Set<FlatNode> flatNodesToVisit = new HashSet<FlatNode>();
     flatNodesToVisit.add( fm );
 
-    Set<FlatNode> debugVisited = new HashSet<FlatNode>();
+    // if determinism is desired by client, shadow the
+    // set with a queue to make visit order deterministic
+    Queue<FlatNode> flatNodesToVisitQ = null;
+    if( determinismDesired ) {
+      flatNodesToVisitQ = new LinkedList<FlatNode>();
+      flatNodesToVisitQ.add( fm );
+    }
     
     // mapping of current partial results
     Hashtable<FlatNode, ReachGraph> mapFlatNodeToReachGraph =
@@ -784,10 +795,15 @@ public class DisjointAnalysis {
     HashSet<FlatReturnNode> setReturns = new HashSet<FlatReturnNode>();
 
     while( !flatNodesToVisit.isEmpty() ) {
-      FlatNode fn = (FlatNode) flatNodesToVisit.iterator().next();
-      flatNodesToVisit.remove( fn );
 
-      debugVisited.add( fn );
+      FlatNode fn;      
+      if( determinismDesired ) {
+        assert !flatNodesToVisitQ.isEmpty();
+        fn = flatNodesToVisitQ.remove();
+      } else {
+        fn = flatNodesToVisit.iterator().next();
+      }
+      flatNodesToVisit.remove( fn );
 
       // effect transfer function defined by this node,
[…]

### 2010-04-07 Robust/src/IR/State.java

@@ -70,6 +70,7 @@ public class State {
   
   public boolean DISJOINT=false;
   public boolean DISJOINTRELEASEMODE=false;
+  public boolean DISJOINTDETERMINISM=false;
   public int DISJOINTALLOCDEPTH=3;
   public boolean DISJOINTWRITEDOTS=false;
   public boolean DISJOINTWRITEALL=false;

### 2010-04-07 Robust/src/Main/Main.java

@@ -220,6 +220,9 @@ public class Main {
       } else if( option.equals( "-disjoint-release-mode" ) ) {
         state.DISJOINTRELEASEMODE = true;        
 
+      } else if( option.equals( "-disjoint-desire-determinism" ) ) {
+        state.DISJOINTDETERMINISM = true;        
+
       } else if( option.equals( "-disjoint-dvisit-stack" ) ) {
         state.DISJOINTDVISITSTACK         = true;      
         state.DISJOINTDVISITPQUE          = false;

### 2010-04-07 Robust/src/Analysis/Disjoint/DescriptorComparator.java
deterministic mode works

@@ -1,0 +1,21 @@
+package Analysis.Disjoint;
+
+import IR.*;
+import IR.Flat.*;
+import java.util.*;
+import java.io.*;
+
+public class DescriptorComparator implements Comparator {
+
+  public int compare( Object o1, Object o2  ) {
+
+    assert o1 instanceof Descriptor;
+    assert o2 instanceof Descriptor;
+
+    Descriptor d1 = (Descriptor) o1;
+    Descriptor d2 = (Descriptor) o2;
+
+    return d1.getNum() - d2.getNum();
+  }
+  
+}

### 2010-04-07 Robust/src/Analysis/Disjoint/DisjointAnalysis.java

@@ -465,8 +465,17 @@ public class DisjointAnalysis {
 
   // allocate various structures that are not local
   // to a single class method--should be done once
-  protected void allocateStructures() {    
-    descriptorsToAnalyze = new HashSet<Descriptor>();
+  protected void allocateStructures() {
+    
+    if( determinismDesired ) {
+      // use an ordered set
+      descriptorsToAnalyze 
+        = new TreeSet<Descriptor>( new DescriptorComparator() );
+      
+    } else {
+      // otherwise use a speedy hashset
+      descriptorsToAnalyze = new HashSet<Descriptor>();
+    }
 
     mapDescriptorToCompleteReachGraph =
       new Hashtable<Descriptor, ReachGraph>();
@@ -521,6 +530,8 @@ public class DisjointAnalysis {
     
     mapDescriptorToReachGraph = 
     	new Hashtable<Descriptor, ReachGraph>();
+
+    pm = new PointerMethod();
   }
 
 
@@ -564,7 +575,6 @@ public class DisjointAnalysis {
     this.stopAfterCapture        = state.DISJOINTSNAPSTOPAFTER;
     this.snapVisitCounter        = 1; // count visits from 1 (user will write 1, means 1st visit)
     this.snapNodeCounter         = 0; // count nodes from 0
-    this.pm=new PointerMethod();
 
     assert
       state.DISJOINTDVISITSTACK ||
@@ -578,7 +588,19 @@ public class DisjointAnalysis {
     ReachGraph.allocationDepth = allocationDepth;
     ReachGraph.typeUtil        = typeUtil;
 
-    ReachGraph.debugCallSiteVisitsUntilExit = state.DISJOINTDEBUGCALLCOUNT;
+    ReachGraph.debugCallSiteVisitStartCapture
+      = state.DISJOINTDEBUGCALLVISITTOSTART;
+
+    ReachGraph.debugCallSiteNumVisitsToCapture
+      = state.DISJOINTDEBUGCALLNUMVISITS;
+
+    ReachGraph.debugCallSiteStopAfter
+      = state.DISJOINTDEBUGCALLSTOPAFTER;
+
+    ReachGraph.debugCallSiteVisitCounter 
+      = 0; // count visits from 1, is incremented before first visit
+    
+    
 
     allocateStructures();
 
@@ -1050,21 +1072,48 @@ public class DisjointAnalysis {
       break;
 
     case FKind.FlatCall: {
[…]

### 2010-04-07 Robust/src/Analysis/Disjoint/ReachGraph.java

@@ -1883,7 +1883,7 @@ public class ReachGraph {
 
 
     if( writeDebugDOTs ) {    
-      debugGraphPrefix = String.format( "call%02d", debugCallSiteVisits );
+      debugGraphPrefix = String.format( "call%02d", debugCallSiteVisitCounter );
       rg.writeGraph( debugGraphPrefix+"calleeview", 
                      resolveMethodDebugDOTwriteLabels,    
                      resolveMethodDebugDOTselectTemps,    
@@ -1907,8 +1907,10 @@ public class ReachGraph {
   private static boolean resolveMethodDebugDOThideEdgeTaints  = true;
 
   static String debugGraphPrefix;
-  static int debugCallSiteVisits = 0;
-  static int debugCallSiteVisitsUntilExit = 0;
+  static int debugCallSiteVisitCounter;
+  static int debugCallSiteVisitStartCapture;
+  static int debugCallSiteNumVisitsToCapture;
+  static boolean debugCallSiteStopAfter;
   
 
   public void 
@@ -1921,11 +1923,11 @@ public class ReachGraph {
 
     if( writeDebugDOTs ) {
       System.out.println( "  Writing out visit "+
-                          debugCallSiteVisits+
+                          debugCallSiteVisitCounter+
                           " to debug call site" );
 
       debugGraphPrefix = String.format( "call%02d", 
-                                        debugCallSiteVisits );
+                                        debugCallSiteVisitCounter );
       
       rgCallee.writeGraph( debugGraphPrefix+"callee", 
                            resolveMethodDebugDOTwriteLabels,    
@@ -2676,22 +2678,13 @@ public class ReachGraph {
     }
     
 
-
-
-
     if( writeDebugDOTs ) {
       writeGraph( debugGraphPrefix+"caller90AfterTransfer", 
                   resolveMethodDebugDOTwriteLabels,    
                   resolveMethodDebugDOTselectTemps,    
                   resolveMethodDebugDOTpruneGarbage,   
                   resolveMethodDebugDOThideSubsetReach,
-                  resolveMethodDebugDOThideEdgeTaints );
-
-      ++debugCallSiteVisits;
-      if( debugCallSiteVisits >= debugCallSiteVisitsUntilExit ) {
-        System.out.println( "!!! Exiting after requested visits to call site. !!!" );
-        System.exit( 0 );
-      }
+                  resolveMethodDebugDOThideEdgeTaints );     
     }
   } 
 

### 2010-04-07 Robust/src/IR/State.java

@@ -77,13 +77,18 @@ public class State {
   public boolean DISJOINTWRITEIHMS=false;
   public String DISJOINTALIASFILE=null;
   public boolean DISJOINTALIASTAB=false;
-  public int DISJOINTDEBUGCALLCOUNT=0;
+
   public String DISJOINTDEBUGCALLEE=null;
   public String DISJOINTDEBUGCALLER=null;
+  public int DISJOINTDEBUGCALLVISITTOSTART=0;
+  public int DISJOINTDEBUGCALLNUMVISITS=0;
+  public boolean DISJOINTDEBUGCALLSTOPAFTER=false;
+
   public String DISJOINTSNAPSYMBOL=null;
   public int DISJOINTSNAPVISITTOSTART=0;
   public int DISJOINTSNAPNUMVISITS=0;
   public boolean DISJOINTSNAPSTOPAFTER=false;
+
   public boolean DISJOINTDVISITSTACK=true;
   public boolean DISJOINTDVISITPQUE=false;
   public boolean DISJOINTDVISITSTACKEESONTOP=false;

### 2010-04-07 Robust/src/Main/Main.java

@@ -196,13 +196,23 @@ public class Main {
 	} else if( arg.equals("tabbed") ) {
           state.DISJOINTALIASTAB = true;
         } else {
-          throw new Error("disjoint-alias-file requires arguments <filename> <normal/tabbed>");
+          throw new Error("disjoint-alias-file requires arguments: <filename> <normal/tabbed>");
         }
 
       } else if (option.equals("-disjoint-debug-callsite")) {
 	state.DISJOINTDEBUGCALLEE=args[++i];
 	state.DISJOINTDEBUGCALLER=args[++i];
-	state.DISJOINTDEBUGCALLCOUNT=Integer.parseInt(args[++i]);
+	state.DISJOINTDEBUGCALLVISITTOSTART=Integer.parseInt(args[++i]);
+	state.DISJOINTDEBUGCALLNUMVISITS=Integer.parseInt(args[++i]);
+        String arg = args[++i];
+	if( arg.equals("true") ) {
+	  state.DISJOINTDEBUGCALLSTOPAFTER = true;
+	} else if( arg.equals("false") ) {
+          state.DISJOINTDEBUGCALLSTOPAFTER = false;
+        } else {
+          throw new Error("disjoint-debug-callsite requires arguments:\n"+
+                          "  <callee symbol> <caller symbol> <# visit to start> <# visits to capture> <T/F stop after>");
+        }
       
       } else if (option.equals("-disjoint-debug-snap-method")) {
 	state.DISJOINTSNAPSYMBOL=args[++i];
@@ -214,14 +224,12 @@ public class Main {
 	} else if( arg.equals("false") ) {
           state.DISJOINTSNAPSTOPAFTER = false;
         } else {
-          throw new Error("disjoint-debug-snap-method requires arguments <method symbol> <# visit to start> <# visits to snap> <T/F stop after>");
+          throw new Error("disjoint-debug-snap-method requires arguments:\n"+
+                          "  <method symbol> <# visit to start> <# visits to snap> <T/F stop after>");
         }
 
       } else if( option.equals( "-disjoint-release-mode" ) ) {
         state.DISJOINTRELEASEMODE = true;        
-
-      } else if( option.equals( "-disjoint-desire-determinism" ) ) {
-        state.DISJOINTDETERMINISM = true;        
 
       } else if( option.equals( "-disjoint-dvisit-stack" ) ) {
         state.DISJOINTDVISITSTACK         = true;      
@@ -237,6 +245,16 @@ public class Main {
[…]

### 2010-04-08 Robust/src/Benchmarks/Recovery/Spider/recovery/QueryTask.java
rewrite

@@ -1,390 +1,426 @@
 public class QueryTask extends Task {
-	int maxDepth;
-	int maxSearchDepth;
-	GlobalQueue toprocess;
-	DistributedHashMap results;
-	DistributedLinkedList results_list;
-	DistributedHashMap visitedList;
-	GlobalString gTitle;
-	GlobalString workingURL;
+  int maxDepth;
+  int maxSearchDepth;
+  DistributedHashMap results;
+  DistributedLinkedList results_list;
+  DistributedHashMap visitedList;
+  GlobalString gTitle;
+  GlobalString workingURL;
+  GlobalString hostname;
+  GlobalString path;
+  int depth;
 
-  public QueryTask(GlobalQueue todoList, DistributedHashMap visitedList, int maxDepth, int maxSearchDepth, DistributedHashMap results, DistributedLinkedList results_list) {
-    this.todoList = todoList;
-		this.visitedList = visitedList;
-		this.maxDepth = maxDepth;
-		this.maxSearchDepth = maxSearchDepth;
-		this.results = results;
-		this.results_list = results_list;
-		toprocess = global new GlobalQueue();
-  }
-
-  public void execute() {
-		int depth;
-		int max;
-		int maxSearch;
-		
-		atomic {
-			depth = ((GlobalQuery)myWork).getDepth();
-            max = this.maxDepth;
-			maxSearch = this.maxSearchDepth;
-		}
-
-		if (depth < max) {
-			/* global variables */
-			GlobalQuery gq;
-
-			/* local variables */
-			LocalQuery lq;
-			String hostname;
-			String path;
-			String title;
-
-			atomic {
-				gq = (GlobalQuery)myWork;
-				hostname = new String(GlobalString.toLocalCharArray(gq.getHostName()));
-				path = new String(GlobalString.toLocalCharArray(gq.getPath()));
-
-				GlobalStringBuffer gsb = global new GlobalStringBuffer(hostname);
-				gsb.append("/");
-				gsb.append(path);
-				workingURL = global new GlobalString(gsb.toGlobalString());
-				gTitle = null;
-			}
-			lq = new LocalQuery(hostname, path, depth);
-
-/*			System.printString("["+lq.getDepth()+"] ");
-			System.printString("Processing - Hostname : ");
-			System.printString(hostname);
-			System.printString(", Path : ");
-			System.printString(path);
-			System.printString("\n");
-*/
-			if (isDocument(path)) {
[…]

### 2010-04-08 Robust/src/Benchmarks/Recovery/Spider/recovery/Spider.java

@@ -5,85 +5,68 @@ Usage :
 
 
 public class Spider {
-	public static void main(String[] args) {
-		int NUM_THREADS = 3;
-		int maxDepth = 3;
-		int maxSearchDepth = 10;
-		int i, j;
-		Work[] works;
-		QueryTask[] qt;
-		GlobalQuery[] currentWorkList;
+  public static void main(String[] args) {
+    int NUM_THREADS = 3;
+    int maxDepth = 3;
+    int maxSearchDepth = 10;
+    int i, j;
     String fm = "www.uci.edu";
     String fp = "";
-
+    
     if(args.length != 3) {
       System.out.println("./Spider.java master <num_thread> <first machine> <maxDepth>");
       System.exit(0);
-    }
-    else {
+    } else {
       NUM_THREADS = Integer.parseInt(args[0]);
       fm = args[1];
       maxDepth = Integer.parseInt(args[2]);
     }
+    
+    int mid[] = new int[8];
 
-		GlobalString firstmachine;
-		GlobalString firstpage;
+    mid[0] = (128<<24)|(195<<16)|(136<<8)|162;
+    mid[1] = (128<<24)|(195<<16)|(136<<8)|163;
+    mid[2] = (128<<24)|(195<<16)|(136<<8)|164;
+    mid[3] = (128<<24)|(195<<16)|(136<<8)|165;
+    mid[4] = (128<<24)|(195<<16)|(136<<8)|166;
+    mid[5] = (128<<24)|(195<<16)|(136<<8)|167;
+    mid[6] = (128<<24)|(195<<16)|(136<<8)|168;
+    mid[7] = (128<<24)|(195<<16)|(136<<8)|169;
+    
+    TaskSet ts;
+    atomic {
+      //set up workers
+      ts=global new TaskSet(NUM_THREADS);
+      for (i = 0; i < NUM_THREADS; i++) {
+	ts.threads[i] = global new Worker(ts,i);
+      }
+    }
 
-		int mid[] = new int[8];
+    atomic {
+      GlobalString firstmachine = global new GlobalString(fm);
+      GlobalString firstpage = global new GlobalString("");
+      DistributedHashMap visitedList = global new DistributedHashMap(500, 500, 0.75f);
+      DistributedHashMap results = global new DistributedHashMap(100, 100, 0.75f);
+      DistributedLinkedList results_list = global new DistributedLinkedList();
[…]

### 2010-04-08 Robust/src/Benchmarks/Recovery/Spider/recovery/Task.java
new files

@@ -1,0 +1,15 @@
+public class Task {
+  //Current worker thread
+  Worker w;
+  public void execute();
+  public void setWorker(Worker w) {
+    this.w = w;
+  }
+  public void dequeueTask() {
+    w.workingtask=null;
+  }
+  public void enqueueTask(Task t) {
+    w.tasks.todo.push(t);
+  }
+  public native void execution();
+}

### 2010-04-08 Robust/src/Benchmarks/Recovery/Spider/recovery/TaskSet.java

@@ -1,0 +1,13 @@
+public class TaskSet {
+  public TaskSet(int nt) {
+    numthreads=nt;
+    threads=global new Worker[nt];
+    todo=global new GlobalQueue();
+  }
+
+  //Tasks to be executed
+  GlobalQueue todo;
+  //Vector of worker threads
+  Worker threads[];
+  int numthreads;
+}

### 2010-04-08 Robust/src/Benchmarks/Recovery/Spider/recovery/Worker.java

@@ -1,0 +1,50 @@
+public class Worker extends Thread {
+  Object[] currentWorkList;
+  int mid;
+  TaskSet tasks;
+  Task workingtask;
+
+  Worker(TaskSet tasks, int mid) {
+    this.tasks = tasks;
+    this.currentWorkList = currentWorkList;
+    mid = mid;
+  }
+  
+  public void run() {
+    boolean notdone=true;
+    while(notdone) {
+      Task t=null;
+      atomic {
+        if (!tasks.todo.isEmpty()) {
+          //grab segment from todo list
+          t=workingtask=(Task) tasks.todo.pop();
+	  t.setWorker(this);
+        } else {
+          //steal work from dead threads
+          Worker[] threads=tasks.threads;
+	  boolean shouldexit=true;
+          for(int i=0;i<threads.length;i++) {
+            Worker w=(Worker)threads[i];
+	    if (w.workingtask!=null)
+	      shouldexit=false;
+            if (w.getStatus()==-1&&w.workingtask!=null) {
+              //steal work from this thread
+              t=workingtask=w.workingtask;
+              w.workingtask=null;
+	      t.setWorker(this);
+              break;
+            }
+          }
+	  if (shouldexit)
+	    notdone=false;
+        }
+      }
+      if (t!=null) {
+        t.execution();
+        continue;
+      } else if (notdone)
+	sleep(500000);
+    }
+  }
+  public static native void printRecoveryStat();
+}

### 2010-04-15 Robust/src/Benchmarks/Recovery/runjava.sh
changes to the recovery script : enable killing of one machine using USR signal

@@ -10,8 +10,8 @@
 BASEDIR=`pwd`
 RECOVERYDIR='recovery'
 JAVASINGLEDIR='java'
-WAITTIME=200
-KILLDELAY=20
+WAITTIME=75
+KILLDELAY=2
 LOGDIR=~/research/Robust/src/Benchmarks/Recovery/runlog
 DSTMDIR=${HOME}/research/Robust/src/Benchmarks/Prefetch/config
 MACHINELIST='dc-1.calit2.uci.edu dc-2.calit2.uci.edu dc-3.calit2.uci.edu dc-4.calit2.uci.edu dc-5.calit2.uci.edu dc-6.calit2.uci.edu dc-7.calit2.uci.edu dc-8.calit2.uci.edu'
@@ -19,12 +19,16 @@ USER='adash'
 
 # 0 mean new test 
 # 1~8 machine id to be killed
+
 ORDER=( 0 1 3 5 7 8 2    
         0 1 2 3 4 5 6 
         0 1 8 4 6 3 7 
         0 8 7 3 6 5 4
         0 7 4 6 8 1 2 );
 
+#ORDER=( 0 1 3 5 7 8 2 );
+
+#
 # killClients <fileName> <# of machines>
 function killclients {
   k=1;
@@ -52,7 +56,8 @@ function killonemachine {
   fileName=$1
   let "machine= $2";
   echo "killing dc-$machine ${fileName}";
-  ssh dc-${machine} pkill -u ${USER} -f ${fileName}
+  #ssh dc-${machine} pkill -u ${USER} -f ${fileName}
+  ssh dc-${machine} killall -USR1 ${fileName} 
 }
 
 # runmachines <log filename>
@@ -69,20 +74,21 @@ function runMachines {
   # Run machines
   while [ $k -gt 1 ]; do
     echo "SSH into dc-${k}"
-    ssh dc-${k} 'cd '$DIR'; ./'$BM_NAME'.bin '>> $1'-'$k 2>&1 &
+    ssh dc-${k} 'cd '$DIR'; ./'$BM_NAME'.bin '>> log'-'$k 2>&1 &
     k=`expr $k - 1`
     sleep 1
   done
+  sleep 2
   echo "Running master machine ... "
   echo "ssh dc-1 cd $DIR'; ./$BM_NAME.bin master $NUM_MACHINE $BM_ARGS";
[…]

### 2010-04-15 Robust/src/Analysis/Disjoint/DisjointAnalysis.java
bug fix, some callees were not being rescheduled because code to do it was conditional on caller having a new result since last visit

@@ -469,6 +469,9 @@ public class DisjointAnalysis {
   static protected Hashtable<FlatNode, ReachGraph> fn2rg =
     new Hashtable<FlatNode, ReachGraph>();
 
+  private Hashtable<FlatCall, Descriptor> fc2enclosing;
+  
+
 
   // allocate various structures that are not local
   // to a single class method--should be done once
@@ -537,6 +540,11 @@ public class DisjointAnalysis {
     	new Hashtable<Descriptor, ReachGraph>();
 
     pm = new PointerMethod();
+
+    if( state.DISJOINTDEBUGSCHEDULING ) {
+      fc2enclosing = new Hashtable<FlatCall, Descriptor>();
+    }
+
   }
 
 
@@ -801,27 +809,23 @@ public class DisjointAnalysis {
             System.out.println( "    "+dNext );
           }
 	}
-
-        if( state.DISJOINTDVISITSTACKEESONTOP ) {
-
-          depsItr = calleesToEnqueue.iterator();
-          while( depsItr.hasNext() ) {
-            Descriptor dNext = depsItr.next();
-            enqueue( dNext );
-          }
-          calleesToEnqueue.clear();
-        }
-
-      } else {
-        // we got the result result as the last visit
-        // to this method, but we might need to clean
-        // something up
-        if( state.DISJOINTDVISITSTACKEESONTOP ) {
-          calleesToEnqueue.clear();
-        }
       }
-     
-    }
+
+      // whether or not the method under analysis changed,
+      // we may have some callees that are scheduled for 
+      // more analysis, and they should go on the top of
+      // the stack now (in other method-visiting modes they
+      // are already enqueued at this point
+      if( state.DISJOINTDVISITSTACKEESONTOP ) {
+        Iterator<Descriptor> depsItr = calleesToEnqueue.iterator();
+        while( depsItr.hasNext() ) {
+          Descriptor dNext = depsItr.next();
+          enqueue( dNext );
+        }
+        calleesToEnqueue.clear();
+      }     
+
+    }   
   }
 
   protected ReachGraph analyzeMethod( Descriptor d ) 
@@ -1014,7 +1018,6 @@ public class DisjointAnalysis {
         rg.merge( rgContrib );
       }
 
-
       // additionally, we are enforcing STRICT MONOTONICITY for the
       // method's initial context, so grow the context by whatever
       // the previously computed context was, and put the most
@@ -1184,6 +1187,11 @@ public class DisjointAnalysis {
 
[…]

### 2010-04-16 Robust/src/Runtime/multicoregarbage.c
disable Timer interrupt and some bug fixing

@@ -448,7 +448,7 @@ inline void checkMarkStatue() {
 	for(i = 1; i < NUMCORESACTIVE; ++i) {
 	  gccorestatus[i] = 1;
 	  // send mark phase finish confirm request msg to core i
-	  send_msg_1(i, GCMARKCONFIRM);
+	  send_msg_1(i, GCMARKCONFIRM, false);
 	}                         // for(i = 1; i < NUMCORESACTIVE; ++i)
       } else {
 	// check if the sum of send objs and receive obj are the same
@@ -478,7 +478,7 @@ inline void checkMarkStatue() {
 	  // restore the gcstatus for all cores
 	  for(i = 0; i < NUMCORESACTIVE; ++i) {
 	    gccorestatus[i] = 1;
-	  }                               // for(i = 0; i < NUMCORESACTIVE; ++i)
+	  }  // for(i = 0; i < NUMCORESACTIVE; ++i)
 	} else {
 	  // wait for a while and ask for confirm again
 	  int h = 100;
@@ -513,7 +513,7 @@ inline bool preGC() {
     for(i = 1; i < NUMCORESACTIVE; ++i) {
       corestatus[i] = 1;
       // send status confirm msg to core i
-      send_msg_1(i, STATUSCONFIRM);
+      send_msg_1(i, STATUSCONFIRM, false);
     }             // for(i = 1; i < NUMCORESACTIVE; ++i)
 
 #ifdef DEBUG
@@ -980,7 +980,7 @@ inline void moveLObjs() {
 #endif
 	if(host != BAMBOO_NUM_OF_CORE) {
 	  // send the original host core with the mapping info
-	  send_msg_3(host, GCLOBJMAPPING, ptr, tmpheaptop);
+	  send_msg_3(host, GCLOBJMAPPING, ptr, tmpheaptop, false);
 #ifdef DEBUG
 	  BAMBOO_DEBUGPRINT(0xcdcb);
 	  BAMBOO_DEBUGPRINT_REG(ptr);
@@ -1065,7 +1065,7 @@ inline void moveLObjs() {
 #endif
 	if(host != BAMBOO_NUM_OF_CORE) {
 	  // send the original host core with the mapping info
-	  send_msg_3(host, GCLOBJMAPPING, ptr, tmpheaptop);
+	  send_msg_3(host, GCLOBJMAPPING, ptr, tmpheaptop, false);
 #ifdef DEBUG
[…]

### 2010-04-16 Robust/src/Runtime/multicoreruntime.h

@@ -22,8 +22,8 @@ unsigned long long bamboo_start_time;
 #define BAMBOO_OUT_BUF_LENGTH 3000
 #define BAMBOO_MSG_BUF_LENGTH 3000
 int msgdata[BAMBOO_MSG_BUF_LENGTH];
-int msgdataindex;
-int msgdatalast;
+volatile int msgdataindex;
+volatile int msgdatalast;
 int msglength;
 volatile bool msgdatafull;
 int outmsgdata[BAMBOO_OUT_BUF_LENGTH];
@@ -31,7 +31,7 @@ int outmsgindex;
 int outmsglast;
 int outmsgleft;
 volatile bool isMsgHanging;
-volatile bool isMsgSending;
+//volatile bool isMsgSending;
 
 #define MSG_INDEXINC_I() \
   msgdataindex = (msgdataindex + 1) % (BAMBOO_MSG_BUF_LENGTH)
@@ -418,38 +418,40 @@ INLINE void processlockrelease(int locktype,
                                bool redirect);
 
 // msg related functions
-INLINE void send_hanging_msg();
+INLINE void send_hanging_msg(bool isInterrupt);
 INLINE void send_msg_1(int targetcore,
-                       unsigned long n0);
+                       unsigned long n0,
+					   bool isInterrupt);
 INLINE void send_msg_2(int targetcore,
                        unsigned long n0,
-                       unsigned long n1);
+                       unsigned long n1,
+					   bool isInterrupt);
 INLINE void send_msg_3(int targetcore,
                        unsigned long n0,
                        unsigned long n1,
-                       unsigned long n2);
+                       unsigned long n2,
+					   bool isInterrupt);
 INLINE void send_msg_4(int targetcore,
                        unsigned long n0,
                        unsigned long n1,
                        unsigned long n2,
-                       unsigned long n3);
+                       unsigned long n3,
+					   bool isInterrupt);
 INLINE void send_msg_5(int targetcore,
                        unsigned long n0,
                        unsigned long n1,
                        unsigned long n2,
                        unsigned long n3,
-                       unsigned long n4);
+                       unsigned long n4,
+					   bool isInterrupt);
 INLINE void send_msg_6(int targetcore,
                        unsigned long n0,
                        unsigned long n1,
                        unsigned long n2,
                        unsigned long n3,
                        unsigned long n4,
-                       unsigned long n5);
-INLINE void send_msg_3_I(int targetcore,
-                         unsigned long n0,
[…]

### 2010-04-16 Robust/src/Runtime/multicoretask.c

@@ -100,7 +100,7 @@ void initruntimedata() {
   outmsglast = 0;
   outmsgleft = 0;
   isMsgHanging = false;
-  isMsgSending = false;
+  //isMsgSending = false;
 
   smemflag = true;
   bamboo_cur_msp = NULL;
@@ -241,10 +241,10 @@ bool checkObjQueue() {
     while(!lockflag) {
       BAMBOO_WAITING_FOR_LOCK(0);
 	  // check for outgoing sends
-	  if (isMsgHanging) {
+	  /*if (isMsgHanging) {
 		extern inline void send_hanging_msg(bool);
 		send_hanging_msg(true);
-	  } 
+	  } */
     }             // while(!lockflag)
     grount = lockresult;
 #ifdef DEBUG
@@ -403,8 +403,8 @@ void checkCoreStatus() {
 	  for(i = 1; i < NUMCORESACTIVE; ++i) {
 	    corestatus[i] = 1;
 	    // send status confirm msg to core i
-	    send_msg_1(i, STATUSCONFIRM);
-	  }                               // for(i = 1; i < NUMCORESACTIVE; ++i)
+	    send_msg_1(i, STATUSCONFIRM, false);
+	  }   // for(i = 1; i < NUMCORESACTIVE; ++i)
 	  return;
 	} else {
 	  // all the core status info are the latest
@@ -434,7 +434,7 @@ void checkCoreStatus() {
 #endif
 	  for(i = 1; i < NUMCORESACTIVE; ++i) {
 	    // send profile request msg to core i
-	    send_msg_2(i, PROFILEOUTPUT, totalexetime);
+	    send_msg_2(i, PROFILEOUTPUT, totalexetime, false);
 	  } // for(i = 1; i < NUMCORESACTIVE; ++i)
 	  // pour profiling data on startup core
 	  outputProfileData();
@@ -624,7 +624,7 @@ inline void run(void * arg) {
 #endif
 	      // send stall msg
 	      send_msg_4(STARTUPCORE, TRANSTALL, BAMBOO_NUM_OF_CORE,
-	                 self_numsendobjs, self_numreceiveobjs);
+	                 self_numsendobjs, self_numreceiveobjs, false);
 	      sendStall = true;
 	      isfirst = true;
 	      busystatus = false;
@@ -1572,7 +1572,10 @@ INLINE int checkMsgLength_I(int size) {
   default:
   {
     BAMBOO_DEBUGPRINT_REG(type);
[…]

### 2010-04-16 Robust/src/Runtime/DSTM/interface_recovery/dstm.h
grab locks on sockpool for all communications involving cache and prefetch

@@ -86,8 +86,8 @@
 //Prefetch tuning paramters
 //#define RETRYINTERVAL  20 //N (For Em3d, SOR, Moldyn benchmarks)
 //#define SHUTDOWNINTERVAL  3  //M
-#define RETRYINTERVAL  75 //N  (For MatrixMultiply, 2DFFT benchmarks)
-#define SHUTDOWNINTERVAL  1  //M
+#define RETRYINTERVAL  60 //N  (For MatrixMultiply, 2DFFT benchmarks)
+#define SHUTDOWNINTERVAL  10  //M
 #define NUM_TRY_TO_COMMIT 2
 #define MEM_ALLOC_THRESHOLD 20485760//20MB
 

### 2010-04-16 Robust/src/Runtime/DSTM/interface_recovery/dstmserver.c

@@ -1626,7 +1626,11 @@ int prefetchReq(int acceptfd) {
 	freeSockWithLock(transPResponseSocketPool, mid, sd);
       }
       mid=oidmid.mid;
-      sd = getSockWithLock(transPResponseSocketPool, mid);
+      //sd = getSockWithLock(transPResponseSocketPool, mid);
+      if((sd = getSockWithLock(transPResponseSocketPool, mid)) < 0) {
+        printf("%s() Socket Create Error at %s, %d\n", __func__, __FILE__, __LINE__);
+        return -1;
+      }
     }
     short offsetarry[numoffset];
     recv_data((int) acceptfd, offsetarry, numoffset*sizeof(short));

### 2010-04-16 Robust/src/Runtime/DSTM/interface_recovery/trans.c

@@ -463,8 +463,14 @@ void prefetch(int siteid, int ntuples, unsigned int *oids, unsigned short *endof
       /* Send  Prefetch Request */
       prefetchpile_t *ptr = pilehead;
       while(ptr != NULL) {
-        int sd = getSock2(transPrefetchSockPool, ptr->mid);
+        //int sd = getSock2(transPrefetchSockPool, ptr->mid);
+        int sd;
+        if((sd = getSockWithLock(transPrefetchSockPool, ptr->mid)) < 0) {
+          printf("%s() Socket Create Error at %s, %d\n", __func__, __FILE__, __LINE__);
+          return;
+        }
         sendPrefetchReq(ptr, sd);
+        freeSockWithLock(transPrefetchSockPool, ptr->mid, sd);
         ptr = ptr->next;
       }
       
@@ -1663,7 +1669,12 @@ void *getRemoteObj(unsigned int mnum, unsigned int oid) {
   objheader_t *h;
   void *objcopy = NULL;
 
-  int sd = getSock2(transReadSockPool, mnum);
+  //int sd = getSock2(transReadSockPool, mnum);
+  int sd;
+  if((sd = getSockWithLock(transReadSockPool, mnum)) < 0) {
+    printf("%s() Socket Create Error at %s, %d\n", __func__, __FILE__, __LINE__);
+    return NULL;
+  }
   char readrequest[sizeof(char)+sizeof(unsigned int)];
   readrequest[0] = READ_REQUEST;
   *((unsigned int *)(&readrequest[1])) = oid;
@@ -1700,6 +1711,7 @@ void *getRemoteObj(unsigned int mnum, unsigned int oid) {
   totalObjSize += size;
 #endif
 	}
+  freeSockWithLock(transReadSockPool, mnum, sd);
 	return objcopy;
 }
 
@@ -2840,6 +2852,7 @@ unsigned short getObjType(unsigned int oid) {
   objheader_t *objheader;
   unsigned short numoffset[] ={0};
   short fieldoffset[] ={};
+  int sd=0;
 
   if ((objheader = (objheader_t *) mhashSearch(oid)) == NULL) {
 #ifdef CACHE
@@ -2851,10 +2864,18 @@ unsigned short getObjType(unsigned int oid) {
     unsigned int machineID;
     static int flipBit = 0;
     machineID = (flipBit)?(getPrimaryMachine(mid)):(getBackupMachine(mid));
-    int sd = getSock2(transReadSockPool, machineID);
[…]

### 2010-04-16 Robust/src/Runtime/runtime.c
small change

@@ -350,9 +350,10 @@ void CALL01(___System______printString____L___String___,struct ___String___ * __
     short sc=((short *)(((char *)&chararray->___length___)+sizeof(int)))[i+offset];
     putchar(sc);
   }
-//#ifdef RECOVERYSTATS
+#ifdef RECOVERYSTATS
   fflush(stdout);
-//#endif
+  fflush(stdout);
+#endif
 }
 
 #ifdef D___RecoveryStat______printRecoveryStat____ 

### 2010-04-16 Robust/src/Benchmarks/Recovery/Game/java/RainForest.java
changes to Game benchmark

@@ -1,6 +1,6 @@
 #define ROW                 400   /* columns in the map */
 #define COLUMN              100   /* rows of in the map */
-#define ROUNDS              1000 /* Number of moves by each player */
+#define ROUNDS              2000 /* Number of moves by each player */
 #define PLAYERS             20    /* Number of Players when num Players != num of client machines */
 #define RATI0               0.5   /* Number of lumberjacks to number of planters */
 #define BLOCK               3     /* Area around the gamer to consider */

### 2010-04-16 Robust/src/Benchmarks/Recovery/Spider/recovery/Worker.java
print recovery stats

@@ -52,6 +52,7 @@ public class Worker extends Thread {
     }
     fi = System.currentTimeMillis();
     System.out.println("\n\nDone - Time Elapse : " + (double)((fi-st)/1000) +"\n\n");
+    RecoveryStat.printRecoveryStat();
     while(true) {
       sleep(100000);
     }

### 2010-04-16 Robust/src/Benchmarks/Recovery/MatrixMultiply/recovery/Worker.java
print stats in matrix multiply

@@ -57,7 +57,11 @@ public class Worker extends Thread {
       }
     }
     fi = System.currentTimeMillis();
-    System.out.println("\n\nDone - Time Elapse : " + (double)((fi-st)/1000) +"\n\n");
+    System.printString("\n\nDone - Time Elapse : " + (double)((fi-st)/1000) +"\n\n");
+    RecoveryStat.printRecoveryStat();
+    while(true) {
+      sleep(100000);
+    }
   }
   public static native void printRecoveryStat();
 }

### 2010-04-19 Robust/src/Benchmarks/Recovery/Spider/recovery/QueryTask.java
changes

@@ -27,6 +27,7 @@ public class QueryTask extends Task {
     int ldepth;
 
     atomic {
+      System.out.println("trans 2");
       max = this.maxDepth;
       maxSearch = this.maxSearchDepth;
       ldepth=this.depth;
@@ -39,6 +40,7 @@ public class QueryTask extends Task {
       String title;
       
       atomic {
+      System.out.println("trans 3");
 	hostname = new String(GlobalString.toLocalCharArray(getHostName()));
 	path = new String(GlobalString.toLocalCharArray(getPath()));
 	
@@ -65,6 +67,7 @@ public class QueryTask extends Task {
       
       if ((title = grabTitle(lq)) != null) {
 	atomic {
+      System.out.println("trans 4");
 	  //commits everything...either works or fails
 	  gTitle = global new GlobalString(title);
 	  processPage(lq);
@@ -74,6 +77,7 @@ public class QueryTask extends Task {
       s.close();
     } else {
       atomic {
+      System.out.println("trans 5");
 	dequeueTask();
       }
     }

### 2010-04-19 Robust/src/Benchmarks/Recovery/Spider/recovery/Spider.java

@@ -39,7 +39,10 @@ public class Spider {
       //set up workers
       ts=global new TaskSet(NUM_THREADS);
       for (i = 0; i < NUM_THREADS; i++) {
-	ts.threads[i] = global new Worker(ts,i);
+        ts.threads[i] = global new Worker(ts,i,(NUM_THREADS/2));
+      }
+      for (i = 0; i < NUM_THREADS/2; i++) {
+        ts.todo[i] = global new GlobalQueue();
       }
     }
 
@@ -50,7 +53,7 @@ public class Spider {
       DistributedHashMap results = global new DistributedHashMap(100, 100, 0.75f);
       DistributedLinkedList results_list = global new DistributedLinkedList();
       QueryTask firstquery = global new QueryTask(visitedList, maxDepth, maxSearchDepth, results, results_list, firstmachine, firstpage, 0);
-      ts.todo.push(firstquery);
+      ts.todo[0].push(firstquery);
     }
 
     System.printString("Finished to create Objects\n");

### 2010-04-19 Robust/src/Benchmarks/Recovery/Spider/recovery/Task.java

@@ -1,16 +1,19 @@
 public class Task {
   //Current worker thread
   Worker w;
+  int queueid;
   public Task() {}
   public void execute();
-  public void setWorker(Worker w) {
+  public void setWorker(Worker w, int queueid) {
     this.w = w;
+    this.queueid = queueid;
   }
   public void dequeueTask() {
     w.workingtask=null;
   }
   public void enqueueTask(Task t) {
-    w.tasks.todo.push(t);
+    //System.out.println("queueid= " + queueid);
+    w.tasks.todo[queueid].push(t);
   }
   public native void execution();
 }

### 2010-04-19 Robust/src/Benchmarks/Recovery/Spider/recovery/TaskSet.java

@@ -2,11 +2,11 @@ public class TaskSet {
   public TaskSet(int nt) {
     numthreads=nt;
     threads=global new Worker[nt];
-    todo=global new GlobalQueue();
+    todo=global new GlobalQueue[(nt/2)];
   }
 
   //Tasks to be executed
-  GlobalQueue todo;
+  GlobalQueue[] todo;
   //Vector of worker threads
   Worker threads[];
   int numthreads;

### 2010-04-19 Robust/src/Benchmarks/Recovery/Spider/recovery/Worker.java

@@ -1,13 +1,13 @@
 public class Worker extends Thread {
-  Object[] currentWorkList;
-  int mid;
+  int id;
   TaskSet tasks;
   Task workingtask;
+  int numQueue;
 
-  Worker(TaskSet tasks, int mid) {
+  Worker(TaskSet tasks, int id, int numQueue) {
     this.tasks = tasks;
-    this.currentWorkList = currentWorkList;
-    mid = mid;
+    this.id = id;
+    this.numQueue = 3; // Correct this 3 should be hash defined
   }
   
   public void run() {
@@ -17,29 +17,48 @@ public class Worker extends Thread {
     while(notdone) {
       Task t=null;
       atomic {
-        if (!tasks.todo.isEmpty()) {
+        System.out.println("Transacion 1");
+        int qindex = (id%numQueue);
+        //System.out.println("id= " + id + " numQueue= " + numQueue);
+        if (!tasks.todo[qindex].isEmpty()) {
           //grab segment from todo list
-          t=workingtask=(Task) tasks.todo.pop();
+          t=workingtask=(Task) tasks.todo[qindex].pop();
           if(t!=null)
-            t.setWorker(this);
+            t.setWorker(this, qindex);
         } else {
-          //steal work from dead threads
-          Worker[] threads=tasks.threads;
-	  boolean shouldexit=true;
-          for(int i=0;i<threads.length;i++) {
-            Worker w=(Worker)threads[i];
-	    if (w.workingtask!=null)
-	      shouldexit=false;
-            if (w.getStatus(i)==-1&&w.workingtask!=null) {
-              //steal work from this thread
-              t=workingtask=w.workingtask;
-              w.workingtask=null;
-	      t.setWorker(this);
-              break;
+          int newqindex = qindex;
+          boolean skipvisit = false;
+          for(int queuecount=1;queuecount < numQueue;queuecount++) {
+            newqindex = ((newqindex+1)%numQueue);
+            if (!tasks.todo[newqindex].isEmpty()) {
+              //grab segment from another todo list
+              t=workingtask=(Task) tasks.todo[newqindex].pop();
+              if(t!=null) {
+                t.setWorker(this, qindex);
+                skipvisit = true;
+                break;
+              }
             }
           }
-	  if (shouldexit)
-	    notdone=false;
+          if(!skipvisit) {
+            //steal work from dead threads
+            Worker[] threads=tasks.threads;
+            boolean shouldexit=true;
+            for(int i=0;i<threads.length;i++) {
[…]

### 2010-04-19 Robust/src/Analysis/Disjoint/DisjointAnalysis.java
improving debugging of call site contributions to initial contexts

@@ -541,10 +541,7 @@ public class DisjointAnalysis {
 
     pm = new PointerMethod();
 
-    if( state.DISJOINTDEBUGSCHEDULING ) {
-      fc2enclosing = new Hashtable<FlatCall, Descriptor>();
-    }
-
+    fc2enclosing = new Hashtable<FlatCall, Descriptor>();
   }
 
 
@@ -1185,13 +1182,12 @@ public class DisjointAnalysis {
         // and reschedule the callee for analysis
         addIHMcontribution( mdCallee, fc, heapForThisCall_cur );        
 
+        // map a FlatCall to its enclosing method/task descriptor 
+        // so we can write that info out later
+        fc2enclosing.put( fc, mdCaller );
+
         if( state.DISJOINTDEBUGSCHEDULING ) {
           System.out.println( "  context changed, scheduling callee: "+mdCallee );
-
-          // if we're debugging the scheduling system, map a FlatCall
-          // to its enclosing method/task descriptor so we can write
-          // that info out later
-          fc2enclosing.put( fc, mdCaller );
         }
 
         if( state.DISJOINTDVISITSTACKEESONTOP ) {
@@ -1354,7 +1350,7 @@ public class DisjointAnalysis {
                      true,   // write labels (variables)                
                      true,   // selectively hide intermediate temp vars 
                      true,   // prune unreachable heap regions          
-                     false,  // hide subset reachability states         
+                     true,  // hide subset reachability states         
                      true ); // hide edge taints                        
     }
   }
@@ -1372,11 +1368,11 @@ public class DisjointAnalysis {
         FlatCall   fc  = (FlatCall)   me2.getKey();
         ReachGraph rg  = (ReachGraph) me2.getValue();
                 
-        rg.writeGraph( "IHMPARTFOR"+d+"FROM"+fc,
+        rg.writeGraph( "IHMPARTFOR"+d+"FROM"+fc2enclosing.get( fc )+fc,
                        true,   // write labels (variables)
                        true,   // selectively hide intermediate temp vars
                        true,   // prune unreachable heap regions
-                       false,  // hide subset reachability states
+                       true,  // hide subset reachability states
                        true ); // hide edge taints
       }
     }
@@ -1394,7 +1390,7 @@ public class DisjointAnalysis {
                      true,   // write labels (variables)                
                      true,   // selectively hide intermediate temp vars 
                      true,   // prune unreachable heap regions          
-                     false,  // hide subset reachability states         
+                     true,  // hide subset reachability states         
[…]

### 2010-04-19 Robust/src/Analysis/Disjoint/ReachGraph.java
bug fix in that return value assignment edges were not being handled like other edges, so instead of doing them as a special case they are now integrated into the single callee-to-caller edge code

@@ -1614,17 +1614,18 @@ public class ReachGraph {
       RefEdge   reArg = (RefEdge)   me.getKey();
       Integer   index = (Integer)   me.getValue();
       
-      TempDescriptor arg = fmCallee.getParameter( index );
+      VariableNode   vnCaller  = (VariableNode) reArg.getSrc();
+      TempDescriptor argCaller = vnCaller.getTempDescriptor();
       
-      VariableNode vnCallee = 
-        rg.getVariableNodeFromTemp( arg );
+      TempDescriptor paramCallee = fmCallee.getParameter( index );      
+      VariableNode   vnCallee    = rg.getVariableNodeFromTemp( paramCallee );
       
       HeapRegionNode hrnDstCaller = reArg.getDst();
       HeapRegionNode hrnDstCallee = rg.id2hrn.get( hrnDstCaller.getID() );
       assert hrnDstCallee != null;
       
       ExistPred pred =
-        ExistPred.factory( arg,
+        ExistPred.factory( argCaller,
                            null, 
                            hrnDstCallee.getID(),
                            reArg.getType(),
@@ -1883,7 +1884,7 @@ public class ReachGraph {
 
 
     if( writeDebugDOTs ) {    
-      debugGraphPrefix = String.format( "call%02d", debugCallSiteVisitCounter );
+      debugGraphPrefix = String.format( "call%03d", debugCallSiteVisitCounter );
       rg.writeGraph( debugGraphPrefix+"calleeview", 
                      resolveMethodDebugDOTwriteLabels,    
                      resolveMethodDebugDOTselectTemps,    
@@ -1903,7 +1904,7 @@ public class ReachGraph {
   private static boolean resolveMethodDebugDOTwriteLabels     = true;
   private static boolean resolveMethodDebugDOTselectTemps     = true;
   private static boolean resolveMethodDebugDOTpruneGarbage    = true;
-  private static boolean resolveMethodDebugDOThideSubsetReach = false;
+  private static boolean resolveMethodDebugDOThideSubsetReach = true;
   private static boolean resolveMethodDebugDOThideEdgeTaints  = true;
 
   static String debugGraphPrefix;
@@ -1926,7 +1927,7 @@ public class ReachGraph {
                           debugCallSiteVisitCounter+
                           " to debug call site" );
 
-      debugGraphPrefix = String.format( "call%02d", 
+      debugGraphPrefix = String.format( "call%03d", 
                                         debugCallSiteVisitCounter );
       
[…]
